---
title: "Outcomes - EL"
author: "Sirig Gurung"
date: today
fontsize: 10pt
mainfont: Fira Sans
fontfamily: Fira Sans
monofont: Fira Code
code-line-numbers: true
df-print: kable
highlight-style: tango
number-sections: true
toc: false
lot: false
echo: true
warning: false
header-includes:
  - \usepackage{float}
  - \floatplacement{table}{H}
  - \floatplacement{figure}{H}
format: 
  pdf:
    fig-pos: 'H'
    tbl-pos: 'H'
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| results: hide

rm(list = ls())

pkgs <- c("tidyverse", "modelsummary", "here")

sapply(pkgs, require, character.only = TRUE)
rm(pkgs)

options(knitr.kable.NA = 0)
options(modelsummary_format_numeric_latex = "plain")
options(modelsummary_factory_default = 'kableExtra')
```

```{r}
#| label: Loading-deID-Data-DB
#| echo: false

box_directory <- path.expand("~/Box Sync/PPM/rctendline_june2025")


# Workfile -----
bl_workfile <- read.csv(here("data/out/bl/workfile-final.csv"))
pm_workfile_fu3 <- read.csv(here("data/out/fu3/workfile-final.csv"))
pm_workfile_fu4 <- read.csv(here("data/out/fu4/workfile-final.csv"))
pm_workfile_fu5 <- read.csv(here("data/out/fu5/workfile-final.csv"))

# Treatment DF ----
treat_df <-  bl_workfile |>
  select(hh_id, S, Z)

# PM ----
pm_el <- read.csv(here("data/out/el/Endline Prospective Migrant De-ID.csv")) |>
  filter(!is.na(pm_home)) |>
  distinct(hh_id, .keep_all = T)
# SHM ----
shm_el <- read.csv(here("data/out/el/Endline Secondary HH Member De-ID.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)
# woman ----
w_el <- read.csv(here("data/out/el/Endline Woman De-ID.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)
# HoH ----
hoh_bl <- readRDS(path.expand("~/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data/hoh/hoh_parent.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id) |>
  distinct(hh_id, .keep_all = T) |>
  left_join(treat_df, by = "hh_id") 
hoh_livestock_bl <- readRDS(path.expand("~/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data/hoh/hh_resource_livestock.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id)
hoh_livestockact_bl <- readRDS(path.expand("~/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data/hoh/hh_resource_livestockact.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id)

hoh_fu3 <- read.csv(here("data/out/fu3/Follow-up Round 3 Household Head De-ID.csv")) |>
  filter(resp_available == 1)
hoh_fu4 <- read.csv(path.expand("~/Box Sync/PPM/rctfollowups_sep2023/data/R4/out/Follow-up Round 4 Household Head.csv")) |>
  filter(!is.na(hoh_new_hh_mems)) |>
  distinct(hh_id, .keep_all = T)
hoh_fu5 <- read.csv(path.expand("~/Box Sync/PPM/rctfollowups_sep2023/data/R5/out/Follow-up Round 5 Household Head.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)
hoh_el <- read.csv(path.expand("~/Box Sync/PPM/rctendline_june2025/data/out/Endline Household Head.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)
# hoh_el <- read.csv(here("data/out/el/Endline Household Head De-ID.csv")) |>
#   filter(resp_available == 1) |>
#   distinct(hh_id, .keep_all = T)


# Woman
w_el <- read.csv(here("data/out/fu5/Follow-up Round 5 Woman De-ID.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)

```

```{r}
#| label: Create-Outcomes-Dataset

workfile <- bl_workfile |>
  mutate(S_Z = str_to_upper(str_c(S, "-", Z)),
         el_pm_comp = 1*(hh_id %in% pm_el$hh_id),
         el_shm_comp = 1*(hh_id %in% shm_el$hh_id),
         el_hoh_comp = 1*(hh_id %in% hoh_el$hh_id),
         el_w_comp = 1*(hh_id %in% w_el$hh_id)) |>
  select(hh_id, loc_id, com_id, S, Z, S_Z, ipw_s, ipw_z, 
         el_pm_comp, el_shm_comp, el_hoh_comp, el_w_comp,
         matches("^bl_")) |>
  arrange(hh_id)

workfile$S_Z <- factor(workfile$S_Z, 
                       levels = c("MC-PPM", "MC-UCT", "MC-C", "PC-C"))
```

# Functions to generate outcomes

## Additive indices

```{r}
#| label: Define-Additive-Index-Function
addIndex <- function(df_name, x, outcome_name, na = T) {
  # df_name: Dataset (string)
  # x: vector of variable names to sum over (string)
  # outcome_name: Name of outcome being generated  (string)
  # na: Include NAs or not? Feeds into the na.rm argument (boolean)
  df <- get(df_name) |>
    rowwise() |>
    mutate(!!outcome_name := 
             sum(c_across(all_of(x)), na.rm = T)) |>
    ungroup()
  assign(df_name, df, envir = .GlobalEnv)
}
```

## Summarize outcomes

```{r}
#| label: Summarize-Outcomes
x <- c("el_pm_know_mig_reqs", 
        "el_pm_has_travel_docs")
summ <- function(x) {
  sub <- workfile |>
    select(S_Z, all_of(x))

  datasummary(All(sub) ~ 
              S_Z * (N + Mean), 
            data = sub,
            output = "kableExtra") |> 
  kableExtra::kable_styling(font_size = 8)

}
```

## Check levels of variable 

```{r}
#| label: check-levels-of-var
checkLevels <- function(df, x) {
  df |>
    group_by(get(x)) |>
    summarize(n())
}
```

## Get Varnames from regex 

```{r}
#| label: get-varnames

getVarnames <- function(df, x) {
  colnames(select(df, matches(x)))
}

```

## Trim variables

```{r}
#| label: func-trim-variables
## Function to trim variables

trim <- function(df, var) {
  temp <- df |>
    mutate(!! paste0(var, "_tr") := ifelse(get(var) == 0, NA, get(var)))
  temp_tr <- temp
  
  u <- quantile(temp_tr[[paste0(var, "_tr")]], 0.95, na.rm = T) 
  l <- quantile(temp_tr[[paste0(var, "_tr")]], 0.05, na.rm = T) 
  
  temp <- temp |>
    mutate(!! paste0(var, "_tr") := case_when(get(var) > u & 
                                                get(var) != 0 ~ u,
                                              get(var) < l & 
                                                get(var) != 0 ~ l,
                                              .default = get(var)))
  return(temp)
}
```

# Generate outcomes

## Primary Outcomes

### PM

#### Manipulation Checks

```{r}
#| label: Gen-ManiCheck-Outcomes-PM

# Cleaning outcome components ----
pm_el <- pm_el |>
  mutate(pm_time_ecowas_correct = 1*(pm_time_ecowas == 3)) |>
  mutate_at(vars(pm_vax, pm_id),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Knowledge of regular migration (0-8) ----
addIndex("pm_el", 
         c("pm_docs_req_civ_3",
           "pm_docs_req_civ_4",
           "pm_time_ecowas_correct",
           "pm_docs_required_libya_2", 
           "pm_docs_required_libya_4", 
           "pm_docs_required_libya_6",
           "pm_vax_req_1", "pm_vax_req_2"), 
         "el_pm_know_mig_reqs")

# Possession of travel documents (0-2) ----
addIndex("pm_el",
         c("pm_id",
           "pm_vax"),
         "el_pm_has_travel_docs")
```

```{r}
#| label: Summ-ManiCheck-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_know_mig_reqs,
                   el_pm_has_travel_docs,
                   c("pm_docs_req_civ_3",
                     "pm_docs_req_civ_4",
                     "pm_time_ecowas_correct",
                     "pm_docs_required_libya_2", 
                     "pm_docs_required_libya_4", 
                     "pm_docs_required_libya_6",
                     "pm_vax_req_1", "pm_vax_req_2",
                     "pm_id",
                     "pm_vax")), 
            by = "hh_id") |>
  rename_at(vars(c("pm_docs_req_civ_3",
                     "pm_docs_req_civ_4",
                     "pm_time_ecowas_correct",
                     "pm_docs_required_libya_2", 
                     "pm_docs_required_libya_4", 
                     "pm_docs_required_libya_6",
                     "pm_vax_req_1", "pm_vax_req_2",
                     "pm_id",
                     "pm_vax")), 
            ~paste0("el_", .))

# Summarize outcomes generated ----
summ(c("el_pm_know_mig_reqs", 
       "el_pm_has_travel_docs"))

```


#### Migration Expectations

```{r}
#| label: Gen-FutureEarn-Outcomes-PM

# Expected migration earnings: near-term (if migrate) and 5-yr abroad.
# Mirrors bl_pm_mig_futureEarn / bl_pm_mig_earnAway_5y in genOutcomesBL so the
# variables stack across waves (suffix pm_mig_futureEarn / pm_mig_earnAway_5y).
#
# NOTE - measurement is NOT fully comparable to baseline, despite identical
# question text:
#  (1) Relevance condition: at baseline future_earn was gated on home == 1
#      (asked only of PMs currently at home); at endline pm_future_earn has no
#      relevance filter and is asked of all PM respondents. A missing baseline
#      value typically means "was away"; a missing endline value means genuine
#      non-response.
#  (2) Question order/framing: at baseline future_earn_away (5-yr abroad) sat in
#      a separate long-horizon block introduced by "think about your life five
#      years from now." At endline pm_future_earn_away (Q346) was moved to sit
#      immediately after pm_future_earn (Q345), under the near-term framing note
#      "...if you decided to travel to a neighboring country for work for at
#      least one month." The item text is unchanged but the priming context differs.
workfile <- pm_el |>
  transmute(
    hh_id,
    el_pm_mig_futureEarn  = pm_future_earn,      # Q345
    el_pm_mig_earnAway_5y = pm_future_earn_away  # Q346
  ) %>%
  left_join(workfile, ., by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_pm_mig_futureEarn",
       "el_pm_mig_earnAway_5y"))
```

#### Migration Concerns

```{r}
#| label: Gen-MigConcerns-Outcomes-PM

# Ungated concerns battery: asked of every consenting PM (no skip on migration
# interest or home/away status), framed as concerns weighed "as you considered
# whether to migrate." Each is a 1 = "very concerned" indicator, passed through
# 0/1. Covers family/community opposition (_fam, _comm) and being-needed-at-home
# (_workhome = household labor, _foodsec = household food) alongside the
# cost/danger/border barriers. Suffix kept identical to the raw column so the
# series stacks across waves on pm_mig_concerns_<x>. The conditional "who/why
# objected" follow-ups (gated on _fam/_comm == 1) are NOT cleaned here.
workfile <- pm_el |>
  transmute(
    hh_id,
    el_pm_mig_concerns_funds        = pm_mig_concerns_funds,
    el_pm_mig_concerns_cashdelay    = pm_mig_concerns_cashdelay,
    el_pm_mig_concerns_fam          = pm_mig_concerns_fam,
    el_pm_mig_concerns_comm         = pm_mig_concerns_comm,
    el_pm_mig_concerns_dangroute    = pm_mig_concerns_dangroute,
    el_pm_mig_concerns_dang         = pm_mig_concerns_dang,
    el_pm_mig_concerns_borderclosed = pm_mig_concerns_borderclosed,
    el_pm_mig_concerns_housingwork  = pm_mig_concerns_housingwork,
    el_pm_mig_concerns_foodsec      = pm_mig_concerns_foodsec,
    el_pm_mig_concerns_workhome     = pm_mig_concerns_workhome
  ) %>%
  left_join(workfile, ., by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_pm_mig_concerns_fam",
       "el_pm_mig_concerns_comm",
       "el_pm_mig_concerns_workhome",
       "el_pm_mig_concerns_foodsec",
       "el_pm_mig_concerns_funds",
       "el_pm_mig_concerns_cashdelay",
       "el_pm_mig_concerns_dangroute",
       "el_pm_mig_concerns_dang",
       "el_pm_mig_concerns_borderclosed",
       "el_pm_mig_concerns_housingwork"))
```


#### Migration

```{r}
#| label: Gen-Mig-Outcomes-PM

# Cleaning outcome components ----
pm_el <- pm_el |>
  mutate_at(vars(pm_mig_prep_contact, 
                 pm_mig_prep_savings, 
                 pm_mig_prep_legal),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Intention to Migrate (0-1) ----
pm_el <- pm_el |>
  mutate(el_pm_mig_intent = 1*(pm_mig_intent == 1 | pm_mig_intent_1 == 1))

# Preparation to migrate (0-3) ----
addIndex("pm_el",
         c("pm_mig_prep_contact", 
           "pm_mig_prep_savings", 
           "pm_mig_prep_legal"),
         "el_pm_mig_prep")

# Migration outcomes ----
pm_el <- pm_el |>
  mutate(pm_border_cross_ecowas = 1*(str_count(pm_countries_new, 
                                               "\\b(?:3|6|7|9|10|13|14|15|16|17|18|19)\\b") > 0),
         pm_border_cross = 1*(str_count(pm_countries_new, 
                                        "\\b(?!1\\b)\\d+\\b") > 0),
         pm_border_cross_nonec = 1*(str_count(pm_countries_new,
                                              "\\b(?:2|4|5|8|11|12|20|21)\\b") > 0),
         pm_dom_mig = case_when(pm_current_in_niger == 1 | pm_past_in_niger == 1 |
                                  pm_previous_in_niger_1 == 1 | pm_previous_in_niger_2 == 1 |
                                  pm_previous_in_niger_3 == 1 ~ 1,
                                .default = 0)) |>
  rowwise() |>
  mutate(pm_mig_any = pmax(pm_dom_mig, pm_border_cross, 
                           pm_border_cross_ecowas, pm_border_cross_nonec,
                           na.rm = T)) |>
  ungroup()

temp_df <- pm_el |>
  full_join(select(pm_workfile_fu5, hh_id, fu5_pm_mig_any,
                   fu5_pm_dom_mig, fu5_pm_border_cross, 
                   fu5_pm_border_cross_ecowas, fu5_pm_border_cross_nonec), by = "hh_id") |>
  rowwise() |>
  mutate(el_pm_mig_any = case_when(is.na(pm_mig_any) & is.na(fu5_pm_mig_any) ~ NA,
                                .default = pmax(pm_mig_any, fu5_pm_mig_any, na.rm = T)),
         el_pm_dom_mig = case_when(is.na(pm_dom_mig) & is.na(fu5_pm_dom_mig) ~ NA,
                                .default = pmax(pm_dom_mig, fu5_pm_dom_mig, na.rm = T)),
         el_pm_border_cross = case_when(is.na(pm_border_cross) & 
                                           is.na(fu5_pm_border_cross) ~ NA,
                                .default = pmax(pm_border_cross, 
                                                fu5_pm_border_cross, na.rm = T)),
         el_pm_border_cross_ecowas = case_when(is.na(pm_border_cross_ecowas) &
                                                  is.na(fu5_pm_border_cross_ecowas) ~ NA,
                                .default = pmax(pm_border_cross_ecowas, 
                                                fu5_pm_border_cross_ecowas, na.rm = T)),
         el_pm_border_cross_nonec = case_when(is.na(pm_border_cross_nonec) &
                                                  is.na(fu5_pm_border_cross_nonec) ~ NA,
                                .default = pmax(pm_border_cross_nonec, 
                                                fu5_pm_border_cross_nonec, na.rm = T))) |>
  ungroup() |>
  select(hh_id, el_pm_mig_any, el_pm_dom_mig, 
         el_pm_border_cross, el_pm_border_cross_ecowas,
         el_pm_border_cross_nonec)


# Counts and weeks from FU4 ----
ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)

return_country <- function(index, text) {
  items <- str_split(text, ",")[[1]]
  if (index > 0 & index <= length(items)) {
    return(items[index])
  } else {
    return(NA)
  }
}
  
  
mig_df <- pm_el |>
  select(hh_id, pm_locations_list, pm_countries,
         matches("pm_location_is_home_[0-9]|pm_location_act_index_[0-9]|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]")) |>
  pivot_longer(
    cols = matches("pm_location_is_home_[0-9]|pm_location_act_index_[0-9]|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)")

tot_loc_weeks <- mig_df |>
  group_by(hh_id) |>
  summarize(el_pm_total_weeks = sum(pm_location_weeks, na.rm = T))

mig_df$country <- map(1:nrow(mig_df),
    function(x){
      index <- mig_df$pm_location_act_index[x]
      country_list <- mig_df$pm_countries[x]
      as.numeric(return_country(index, country_list))
    }) |>
  unlist()

mig_df <- mig_df |>
  filter(pm_location_is_home == 0) |>
  mutate(country = ifelse(is.na(country), 1, country),
         dum = 1,
         ecowas = 1*(country %in% ecowas_codes),
         nonecowas = 1*(country %in% noecowas_codes),
         dom = 1*(country == 1),
         ecowas_weeks = ifelse(ecowas == 1, pm_location_weeks, 0),
         nonecowas_weeks = ifelse(nonecowas == 1, pm_location_weeks, 0),
         dom_weeks = ifelse(dom == 1, pm_location_weeks, 0)) |>
  group_by(hh_id) |>
  summarize(el_pm_mig_any_num = sum(dum, na.rm = T),
            el_pm_mig_any_weeks = sum(pm_location_weeks, na.rm = T),
            el_pm_dom_mig_num = sum(dom, na.rm = T),
            el_pm_dom_mig_weeks = sum(dom_weeks, na.rm = T),
            el_pm_border_cross_ecowas_num = sum(ecowas, na.rm = T),
            el_pm_border_cross_ecowas_weeks = sum(ecowas_weeks, na.rm = T),
            el_pm_border_cross_nonec_num = sum(nonecowas, na.rm = T),
            el_pm_border_cross_nonec_weeks = sum(nonecowas_weeks, na.rm = T))
  
mig_df <- mig_df |>
  right_join(select(pm_el, hh_id), by = "hh_id") |>
  mutate_at(vars(hh_id,
                 el_pm_mig_any_num, 
                 el_pm_dom_mig_num,
                 el_pm_border_cross_ecowas_num,
                 el_pm_border_cross_nonec_num,
                 el_pm_mig_any_weeks,
                 el_pm_dom_mig_weeks,
                 el_pm_border_cross_ecowas_weeks,
                 el_pm_border_cross_nonec_weeks),
            ~ifelse(is.na(.), 0, .)) 

## Adding up weeks and episodes to get cumulative measure ----
mig_df <- mig_df |>
  right_join(select(pm_workfile_fu5,
                    hh_id,
                    fu5_pm_mig_any_num, 
                    fu5_pm_dom_mig_num,
                    fu5_pm_border_cross_ecowas_num,
                    fu5_pm_border_cross_nonec_num,
                    fu5_pm_mig_any_weeks,
                    fu5_pm_dom_mig_weeks,
                    fu5_pm_border_cross_ecowas_weeks,
                    fu5_pm_border_cross_nonec_weeks,
                    fu5_pm_total_weeks), by = "hh_id") |>
  left_join(tot_loc_weeks, by = "hh_id") |>
  rowwise() |>
  mutate(el_pm_mig_any_num = sum(el_pm_mig_any_num, fu5_pm_mig_any_num, na.rm = T),
         el_pm_mig_any_weeks = sum(el_pm_mig_any_weeks, fu5_pm_mig_any_weeks, na.rm = T),
         el_pm_dom_mig_num = sum(el_pm_dom_mig_num, fu5_pm_dom_mig_num, na.rm = T),
         el_pm_dom_mig_weeks = sum(el_pm_dom_mig_weeks, fu5_pm_dom_mig_weeks, na.rm = T),
         el_pm_border_cross_ecowas_num = sum(el_pm_border_cross_ecowas_num, 
                                              fu5_pm_border_cross_ecowas_num, na.rm = T),
         el_pm_border_cross_ecowas_weeks = sum(el_pm_border_cross_ecowas_weeks, 
                                                fu5_pm_border_cross_ecowas_weeks, na.rm = T),
         el_pm_border_cross_nonec_num = sum(el_pm_border_cross_nonec_num, 
                                             fu5_pm_border_cross_nonec_num, na.rm = T),
         el_pm_border_cross_nonec_weeks = sum(el_pm_border_cross_nonec_weeks,
                                               fu5_pm_border_cross_nonec_weeks, na.rm = T),
         el_pm_total_weeks = sum(fu5_pm_total_weeks,
                                  el_pm_total_weeks, na.rm = T)) |>
  ungroup() |>
  mutate_at(vars(matches("el_")),
            ~ifelse(hh_id %in% pm_el$hh_id | !is.na(fu5_pm_mig_any_num), ., NA)) |>
  select(hh_id,
         el_pm_mig_any_num, 
         el_pm_dom_mig_num,
         el_pm_border_cross_ecowas_num,
         el_pm_border_cross_nonec_num,
         el_pm_mig_any_weeks,
         el_pm_dom_mig_weeks,
         el_pm_border_cross_ecowas_weeks,
         el_pm_border_cross_nonec_weeks,
         el_pm_total_weeks)

```


```{r}
#| label: Summ-Mig-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_mig_prep,
                   el_pm_mig_intent,
         c("pm_mig_prep_contact", 
           "pm_mig_prep_savings", 
           "pm_mig_prep_legal")), 
            by = "hh_id") |>
  left_join(mig_df, by = "hh_id") |>
  rename_at(vars(c("pm_mig_prep_contact", 
                   "pm_mig_prep_savings", 
                   "pm_mig_prep_legal")),
            ~paste0("el_", .)) |>
  left_join(temp_df, by = "hh_id")





# Summarize outcomes generated ----
summ(c("el_pm_mig_intent", 
       "el_pm_mig_prep",
       "el_pm_mig_prep_legal",
       "el_pm_mig_any", 
       "el_pm_dom_mig", 
       "el_pm_border_cross", 
       "el_pm_border_cross_ecowas",
       "el_pm_border_cross_nonec",
       "el_pm_mig_any_num", 
       "el_pm_dom_mig_num",
       "el_pm_border_cross_ecowas_num",
       "el_pm_border_cross_nonec_num",
       "el_pm_mig_any_weeks",
       "el_pm_dom_mig_weeks",
       "el_pm_border_cross_ecowas_weeks",
       "el_pm_border_cross_nonec_weeks",
       "el_pm_total_weeks"))

rm(temp_df)
```

#### Failed migration

```{r}
#| label: Gen-Failed-Mig-Outcomes-PM

# Cleaning outcome components ----
pm_fu4 <- pm_el |>
  mutate_at(vars(pm_failed_prep),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Failed migration ----
pm_el_temp <- pm_el |>
  mutate(pm_failed_dom_mig = case_when(1*(str_count(pm_failed_prep_country, 
                                               "\\b(?:1)\\b")) > 0 ~ 1,
                                          .default = 0),
         pm_failed_border_cross_ecowas = case_when(1*(str_count(pm_failed_prep_country, 
                                               "\\b(3|6|7|9|10|13|14|15|16|17|18|19)\\b")) 
                                     > 0 ~ 1,
                                          .default = 0),
         pm_failed_border_cross = case_when(pm_failed_prep_country == "0" |
                                                     pm_failed_prep_country == "" ~ 0,
                                                   1*(str_count(pm_failed_prep_country, 
                                                                "\\b(?!1\\b)\\d+\\b")) > 0 ~ 1,
                                                   .default = 0),
         pm_failed_mig_any = 1*(pm_failed_dom_mig == 1 | 
                                      pm_failed_border_cross == 1 |
                                      pm_failed_border_cross_ecowas == 1)) |>
  right_join(select(pm_workfile_fu3, 
                    matches("fu3_pm_failed_"), 
                    hh_id), 
             by = "hh_id") |>
  mutate(el_pm_failed_mig_any = case_when(is.na(pm_failed_mig_any) & 
                                             is.na(fu3_pm_failed_mig_any) ~ NA,
                                .default = pmax(pm_failed_mig_any, 
                                                fu3_pm_failed_mig_any, 
                                                na.rm = T)),
         el_pm_failed_dom_mig = case_when(is.na(pm_failed_dom_mig) & 
                                             is.na(fu3_pm_failed_dom_mig) ~ NA,
                                .default = pmax(pm_failed_dom_mig, 
                                                fu3_pm_failed_dom_mig, 
                                                na.rm = T)),
         el_pm_failed_border_cross = case_when(is.na(pm_failed_border_cross) & 
                                           is.na(fu3_pm_failed_border_cross) ~ NA,
                                .default = pmax(pm_failed_border_cross, 
                                                fu3_pm_failed_border_cross, 
                                                na.rm = T)),
         el_pm_failed_border_cross_ecowas = case_when(is.na(pm_failed_border_cross_ecowas) &
                                                  is.na(fu3_pm_failed_border_cross_ecowas) ~ NA,
                                .default = pmax(pm_failed_border_cross_ecowas, 
                                                fu3_pm_failed_border_cross_ecowas, 
                                                na.rm = T)))  |>
  select(hh_id, el_pm_failed_mig_any, el_pm_failed_border_cross,
         el_pm_failed_border_cross_ecowas, el_pm_failed_dom_mig, pm_failed_dom_mig)

```


```{r}
#| label: Summ-Failed-Mig-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el_temp, hh_id,
                   el_pm_failed_dom_mig,
                   el_pm_failed_border_cross,
                   el_pm_failed_border_cross_ecowas,
                   el_pm_failed_mig_any),
            by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_pm_failed_dom_mig",
       "el_pm_failed_border_cross",
       "el_pm_failed_border_cross_ecowas",
       "el_pm_failed_mig_any"))

rm(pm_el_temp)
```

#### Migrated or intends to migrate
```{r}
#| label: Gen-Intend-Mig-Outcomes-PM

# Cleaning outcome components ----
pm_el <- pm_el |>
  mutate_at(vars(el_pm_mig_intent),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Migration and intent ----
pm_el_temp <- pm_el |>
  mutate(pm_intent_dom_mig = case_when(1*(str_count(pm_mig_intent_country, 
                                               "\\b(?:1)\\b")) > 0 ~ 1,
                                          .default = 0),
         pm_intent_border_cross_ecowas = case_when(1*(str_count(pm_mig_intent_country, 
                                               "\\b(3|6|7|9|10|13|14|15|16|17|18|19)\\b")) 
                                     > 0 ~ 1,
                                          .default = 0),
         pm_intent_border_cross = case_when(pm_mig_intent_country == "0" |
                                                     pm_mig_intent_country == "" ~ 0,
                                                   1*(str_count(pm_mig_intent_country, 
                                                                "\\b(?!1\\b)\\d+\\b")) > 0 ~ 1,
                                                   .default = 0),
         pm_intent_mig_any = 1*(pm_intent_dom_mig == 1 | 
                                      pm_intent_border_cross == 1 |
                                      pm_intent_border_cross_ecowas == 1)) |>
  right_join(select(pm_workfile_fu5, 
                    matches("fu5_pm_intent_"), 
                    hh_id), 
             by = "hh_id") |>
  mutate(el_pm_intent_mig_any = case_when(is.na(pm_intent_mig_any) & 
                                             is.na(fu5_pm_intent_mig_any) ~ NA,
                                .default = pmax(pm_intent_mig_any, 
                                                fu5_pm_intent_mig_any, 
                                                na.rm = T)),
         el_pm_intent_dom_mig = case_when(is.na(pm_intent_dom_mig) & 
                                             is.na(fu5_pm_intent_dom_mig) ~ NA,
                                .default = pmax(pm_intent_dom_mig, 
                                                fu5_pm_intent_dom_mig, 
                                                na.rm = T)),
         el_pm_intent_border_cross = case_when(is.na(pm_intent_border_cross) & 
                                           is.na(fu5_pm_intent_border_cross) ~ NA,
                                .default = pmax(pm_intent_border_cross, 
                                                fu5_pm_intent_border_cross, 
                                                na.rm = T)),
         el_pm_intent_border_cross_ecowas = case_when(is.na(pm_intent_border_cross_ecowas) &
                                                  is.na(fu5_pm_intent_border_cross_ecowas) ~ NA,
                                .default = pmax(pm_intent_border_cross_ecowas, 
                                                fu5_pm_intent_border_cross_ecowas, 
                                                na.rm = T)))  |>
  select(hh_id, el_pm_intent_mig_any, el_pm_intent_border_cross,
         el_pm_intent_border_cross_ecowas, el_pm_intent_dom_mig, pm_intent_dom_mig)

```


```{r}
#| label: Summ-intend-Mig-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el_temp, hh_id,
                   el_pm_intent_dom_mig,
                   el_pm_intent_border_cross,
                   el_pm_intent_border_cross_ecowas,
                   el_pm_intent_mig_any),
            by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_pm_intent_dom_mig",
       "el_pm_intent_border_cross",
       "el_pm_intent_border_cross_ecowas",
       "el_pm_intent_mig_any"))
rm(pm_el_temp)
```



#### Economic Well-Being

```{r}
#| label: Gen-Econ-Outcomes-PM

# Cleaning outcome components ----
temp_loc_costs_df <- pm_el |>
  select(hh_id, matches("pm_food_cost_[0-9]+|pm_housing_cost_[0-9]+|pm_phone_cost_[0-9]+|pm_leisure_cost_[0-9]+|pm_transportation_cost_[0-9]+|pm_calc_total_income_[0-9]+|pm_calc_other_income_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_food_cost_[0-9]+|pm_housing_cost_[0-9]+|pm_phone_cost_[0-9]+|pm_leisure_cost_[0-9]+|pm_transportation_cost_[0-9]+|pm_calc_total_income_[0-9]+|pm_calc_other_income_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)") |>
  group_by(hh_id) |>
  summarize(el_pm_food_cost = sum(pm_food_cost, na.rm = T),
            el_pm_housing_cost = sum(pm_housing_cost, na.rm = T),
            el_pm_phone_cost = sum(pm_phone_cost, na.rm = T),
            el_pm_leisure_cost = sum(pm_leisure_cost, na.rm = T),
            el_pm_transportation_cost = sum(pm_transportation_cost, na.rm = T),
            el_pm_calc_total_income = sum(pm_calc_total_income, na.rm = T),
            el_pm_calc_other_income = sum(pm_calc_other_income, na.rm = T),
            tot_loc_weeks = sum(pm_location_weeks, na.rm = T))

# SG: this dataframe doesn't seem to get used but creates errors
# also this line is strange: el_pm_transportation_cost = sum(pm_leisure_cost)

# temp_inc_comps <- pm_el |>
#   select(hh_id, matches("pm_main_activity_benefit_house_[0-9]+|pm_main_activity_benefit_food_[0-9]+|pm_main_activity_benefit_phone_[0-9]+|pm_main_activity_benefit_other_[0-9]+|pm_main_activity_deduct_amt_[0-9]+|pm_calc_total_income_[0-9]+|pm_location_weeks_[0-9]+|pm_location_period_lab_[0-9]+")) |>
#   pivot_longer(
#     cols =matches("pm_main_activity_benefit_house_[0-9]+|pm_main_activity_benefit_food_[0-9]+|pm_main_activity_benefit_phone_[0-9]+|pm_main_activity_benefit_other_[0-9]+|pm_main_activity_deduct_amt_[0-9]+|pm_calc_total_income_[0-9]+|pm_location_weeks_[0-9]+|pm_location_period_lab_[0-9]+"),
#     names_to = c(".value", "loc_ind"),
#     names_pattern = "(.+)_([0-9]+)") |>
#   filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)") |>
#   group_by(hh_id) |>
#   summarize(el_pm_food_cost = sum(pm_main_activity_benefit_house, na.rm = T),
#             el_pm_housing_cost = sum(pm_main_activity_benefit_food, na.rm = T),
#             el_pm_phone_cost = sum(pm_main_activity_benefit_phone, na.rm = T),
#             el_pm_leisure_cost = sum(pm_main_activity_benefit_other, na.rm = T),
#             el_pm_transportation_cost = sum(pm_leisure_cost),
#             tot_loc_weeks = sum(pm_location_weeks, na.rm = T))
  
  
pm_el <- pm_el |>
  mutate(pm_total_loan_value = -pm_total_loan_value) |>
  mutate(pm_eat_protein = 7 - pm_eat_protein,
         pm_skip_meals_num = case_when(pm_skip_meals == 0 ~ 0,
                                       .default = pm_skip_meals_num),
         pm_emergency = 1*(pm_emerg_sell == 1 | pm_emerg_borrow == 1 | pm_emerg_spend == 1),
         pm_emergency_capital = (5-pm_emergency_capital)/4) |>
  left_join(temp_loc_costs_df, by = "hh_id")


rm(temp_loc_costs_df)

# Income (CFA) ----
addIndex("pm_el",
         c("el_pm_calc_total_income",
           "el_pm_calc_other_income"),
         "el_pm_inc")

pm_el <- pm_el |>
  mutate(el_pm_inc = el_pm_inc/tot_loc_weeks)

# Savings (CFA) ----
pm_el <- pm_el |>
  rowwise() |>
  mutate(el_pm_savings = sum(c_across(matches("^pm_savings_type_amt_[0-9]+$")), na.rm = T)) |>
  ungroup() |>
  mutate(el_pm_savings = ifelse(pm_separate_savings == 0, 0, el_pm_savings),
         el_pm_total_loan_value = -pm_total_loan_value)


addIndex("pm_el",
         c("el_pm_savings",
           "pm_total_loan_value"),
         "el_pm_net_savings")

# Consumption ----

addIndex("pm_el",
         c("el_pm_food_cost", "el_pm_housing_cost",
           "el_pm_leisure_cost", "el_pm_phone_cost",
           "el_pm_transportation_cost"),
         "el_pm_cons")

pm_el <- pm_el |>
  mutate(num_locations = str_count(pm_locations_list, ",") + 1,
         el_pm_cons = el_pm_cons/num_locations)

# Food Insecurity (0-14)----
addIndex("pm_el",
         c("pm_skip_meals_num",
           "pm_eat_protein"),
         "el_pm_foodsec")

## Reversing so it is food security
pm_el <- pm_el |>
  mutate(el_pm_foodsec = 14 - el_pm_foodsec)

# Economic Precarity (0-2) ----
## pm_emergency is a select multiple. Converting to indicator
## for PM faced emergency
addIndex("pm_el",
         c("pm_emergency_capital",
           "pm_emergency"),
         "el_pm_econprecar")

### Need to update share income due to changes in survey #### ----

# Income shared 
temp_loc_share_df <- pm_el |> 
  mutate_at(vars(matches("pm_share_income_[0-9]|pm_rec_income_[0-9]")), as.numeric) |>
  select(hh_id, matches("pm_location_is_home_[0-9]|pm_share_income_[0-9]$|pm_share_income_amt_[0-9]$|pm_rec_income_[0-9]$|pm_rec_income_amt_[0-9]$|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]")) |>
  pivot_longer(
    cols = matches("pm_location_is_home_[0-9]|pm_share_income_[0-9]+|pm_share_income_amt_[0-9]+|pm_rec_income_[0-9]+|pm_rec_income_amt_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)") |>
  mutate(pm_share_income_amt = ifelse(pm_share_income == 0, 0, pm_share_income_amt),
         pm_rec_income_amt = ifelse(pm_rec_income == 0, 0, pm_rec_income_amt),
         pm_share_income_amt = pm_share_income_amt/pm_location_weeks,
         pm_rec_income_amt = pm_rec_income_amt/pm_location_weeks) |>
  group_by(hh_id) |>
  summarize(el_pm_share_income = mean(pm_share_income_amt, na.rm = T),
            el_pm_rec_income = mean(pm_rec_income_amt, na.rm = T),
            tot_locs_weeks = sum(pm_location_weeks, na.rm = T)) |>
  mutate(el_pm_share_income = ifelse(is.na(el_pm_share_income),
                                      0, el_pm_share_income),
         el_pm_rec_income = ifelse(is.na(el_pm_rec_income),
                                    0, el_pm_rec_income))

pm_el <- pm_el |>
  left_join(temp_loc_share_df, by = "hh_id")

```

```{r}
#| label: Summ-Econ-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_inc,
                  # SG: variables below don't seem to exist
                  #  pm_payment_amt,
                  #  pm_house, 
                  #  pm_food, 
                  #  pm_phone_act, 
                  #  pm_other, 
                  #  pm_deduct, 
                  #  pm_calc_total_income,
                   el_pm_net_savings,
                   el_pm_savings,
                   el_pm_total_loan_value,
                   el_pm_cons,
                   el_pm_foodsec,
                   el_pm_econprecar,
                   el_pm_phone_cost, 
                   el_pm_leisure_cost,
                   el_pm_transportation_cost,
                   el_pm_food_cost,
                   el_pm_housing_cost,
                   el_pm_share_income,
                   el_pm_rec_income), 
            by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_pm_inc",
       "el_pm_net_savings",
       "el_pm_cons",
       "el_pm_foodsec",
       "el_pm_econprecar",
       "el_pm_share_income",
       "el_pm_rec_income"))
```


#### Physical Health and Saftey

```{r}
#| label: Gen-HealthSafety-Outcomes-PM


## All components are at the location level, taking max
## Could take sum but PMs travel to diff num. locations
temp_loc_harras_df <- pm_el |>
  select(hh_id, matches("pm_felt_unsafe_[0-9]+|pm_phys_attacked_[0-9]+|pm_theft_[0-9]+|pm_disc_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_felt_unsafe_[0-9]+|pm_phys_attacked_[0-9]+|pm_theft_[0-9]+|pm_disc_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)") |>
  group_by(hh_id) |>
  summarize(pm_felt_unsafe = max(pm_felt_unsafe, na.rm = T),
            pm_phys_attacked = max(pm_phys_attacked, na.rm = T),
            pm_theft = max(pm_theft, na.rm = T),
            pm_disc = max(pm_disc, na.rm = T)) |>
  mutate(across(c(pm_felt_unsafe, pm_phys_attacked, pm_theft, pm_disc),
                ~ifelse(is.infinite(.), NA, .)))

pm_el <- pm_el |>
  left_join(temp_loc_harras_df, by = "hh_id")
rm(temp_loc_harras_df)


# Absence of harassment and violence (0-8) ----

addIndex("pm_el",
         c("pm_felt_unsafe",
           "pm_phys_attacked", 
           "pm_theft", "pm_disc"),
         "el_pm_harrasment")  
  

# Physical health (1-4) ----
## pm_illness component is at the location level. Taking max
temp_ill_df <- pm_el |>
  select(hh_id, matches("pm_illness_[0-9]+|pm_location_period_lab_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_illness_[0-9]+|pm_location_period_lab_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "From follow up 5 (December 2024) to endline (June 2025)") |>
  filter(!is.na(pm_illness)) |>
  group_by(hh_id) |>
  summarize(pm_illness = max(pm_illness, na.rm = T))

pm_el <- pm_el |>
  left_join(temp_ill_df, by = "hh_id") |>
  # Scaling all components to (0-1)
  mutate(pm_sleep = pm_sleep/24,
         pm_physical_health = (pm_physical_health - 1)/4)

rm(temp_ill_df)

addIndex("pm_el",
         c("pm_illness_limit",
           "pm_sleep", 
           "pm_illness",
           "pm_physical_health"),
         "el_pm_physical_health")

```

```{r}
#| label: Summ-HealthSafety-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_physical_health,
                   el_pm_harrasment,
                   c("pm_illness_limit",
                     "pm_sleep", 
                     "pm_illness",
                     "pm_physical_health1" = "pm_physical_health",
                     "pm_felt_unsafe",
                     "pm_phys_attacked", 
                     "pm_theft", 
                     "pm_disc")), 
            by = "hh_id") |>
  rename_at(vars(c("pm_illness_limit",
                   "pm_sleep", 
                   "pm_illness",
                   "pm_physical_health1",
                   "pm_felt_unsafe",
                   "pm_phys_attacked", 
                   "pm_theft", 
                   "pm_disc")), 
            ~paste0("el_", .))

# Summarize outcomes generated ----
summ(c("el_pm_harrasment",
       "el_pm_physical_health"))
```


#### Mental Health

```{r}
#| label: Gen-MentHeatlh-Outcomes-PM

# Cleaning outcome components ----
pm_el <- pm_el |>
  mutate(rev_pm_self_esteem_4 = (5 - pm_self_esteem_4)/4,
         rev_pm_self_esteem_9 = (5 - pm_self_esteem_9)/4,
         pm_emotion1 = (pm_emotion1)/3,
         pm_emotion2 = (pm_emotion2)/3,
         rev_pm_emotion3 = (3 - pm_emotion3)/3,
         rev_pm_emotion4 = (3 - pm_emotion4)/3,
         rev_pm_emotion5 = (3 - pm_emotion5)/3,
         rev_pm_emotion6 = (3 - pm_emotion6)/3,
         rev_pm_emotion7 = (3 - pm_emotion7)/3,
         rev_pm_home_problems = (4 - pm_home_problems)/3,
         rev_pm_idleness = (4 - pm_idleness)/3,
         rev_pm_alcohol_consumption = (4 - pm_alcohol_consumption)/3,
         rev_pm_family_death = (4 - pm_family_death)/3,
         rev_pm_money_problems = (4 - pm_money_problems)/3,
         rev_pm_debt_owed = (4 - pm_debt_owed)/3,
         rev_pm_cant_find_work = (4 - pm_cant_find_work)/3,
         rev_pm_cant_educate_children = (4 - pm_cant_educate_children)/3,
         rev_pm_accidents_disasters = (4 - pm_accidents_disasters)/3,
         pm_ladder_scale = pm_ladder_scale/10
         ) 

# Emotion (0-9) ----
addIndex("pm_el",
         c("rev_pm_self_esteem_4",
           "rev_pm_self_esteem_9",
           "pm_emotion1",
           "pm_emotion2",
           "rev_pm_emotion3",
           "rev_pm_emotion4",
           "rev_pm_emotion5",
           "rev_pm_emotion6",
           "rev_pm_emotion7"),
         "el_pm_emotion")

# Stress: Family (0-4) ----
addIndex("pm_el",
         c("rev_pm_home_problems",
           "rev_pm_idleness",
           "rev_pm_alcohol_consumption",
           "rev_pm_family_death"),
         "el_pm_famstress")

# Stress: Economic (0-6) ----
addIndex("pm_el",
         c("rev_pm_money_problems",
           "rev_pm_debt_owed",
           "rev_pm_cant_find_work",
           "rev_pm_cant_educate_children",
           "rev_pm_accidents_disasters",
           "pm_ladder_scale"),
         "el_pm_econstress")
```


```{r}
#| label: Summ-MentHealth-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_econstress,
                   el_pm_famstress,
                   el_pm_emotion,
                   c("rev_pm_self_esteem_4",
                     "rev_pm_self_esteem_9",
                     "pm_emotion1",
                     "pm_emotion2",
                     "rev_pm_emotion3",
                     "rev_pm_emotion4",
                     "rev_pm_emotion5",
                     "rev_pm_emotion6",
                     "rev_pm_emotion7",
                     "rev_pm_home_problems",
                     "rev_pm_idleness",
                     "rev_pm_alcohol_consumption",
                     "rev_pm_family_death",
                     "rev_pm_money_problems",
                     "rev_pm_debt_owed",
                     "rev_pm_cant_find_work",
                     "rev_pm_cant_educate_children",
                     "rev_pm_accidents_disasters",
                     "pm_ladder_scale")),
            by = "hh_id") |>
  rename_at(vars("rev_pm_self_esteem_4",
                 "rev_pm_self_esteem_9",
                 "pm_emotion1",
                 "pm_emotion2",
                 "rev_pm_emotion3",
                 "rev_pm_emotion4",
                 "rev_pm_emotion5",
                 "rev_pm_emotion6",
                 "rev_pm_emotion7",
                 "rev_pm_home_problems",
                 "rev_pm_idleness",
                 "rev_pm_alcohol_consumption",
                 "rev_pm_family_death",
                 "rev_pm_money_problems",
                 "rev_pm_debt_owed",
                 "rev_pm_cant_find_work",
                 "rev_pm_cant_educate_children",
                 "rev_pm_accidents_disasters",
                 "pm_ladder_scale"), 
            ~paste0("el_pm_", gsub("pm_", "", .)))

# Summarize outcomes generated ----
summ(c("el_pm_emotion",
       "el_pm_famstress",
       "el_pm_econstress"))

```

#### Joint Decision-Making

```{r}
#| label: Gen-JointDecMake-Outcomes-PM

# Cleaning outcome components ---- 
pm_el <- pm_el |>
  mutate_at(vars(pm_daily_hh_expenses_couple,
                 pm_hh_purchases_couple,
                 pm_fam_plan_couple,
                 pm_migrate_couple,
                 pm_vote_couple,
                 pm_school_couple), ~(5-.)/4) |>
  mutate_at(vars(pm_fam_discuss_work, 
                 pm_fam_discuss_community, 
                 pm_fam_discuss_election, 
                 pm_fam_discuss_invest,
                 pm_discuss_women,
                 pm_fam_discuss_migrate),
            ~./3)

# Consults with spouse (0-7) ----
addIndex("pm_el",
         c("pm_daily_hh_expenses_couple",
           "pm_hh_purchases_couple",
           "pm_fam_plan_couple",
           "pm_migrate_couple",
           "pm_vote_couple",
           "pm_school_couple",
           "pm_discuss_women"),
         "el_pm_jointdec")

# Consults with family on issues other than migration (0-4) ----
addIndex("pm_el",
         c("pm_fam_discuss_work", 
           "pm_fam_discuss_community", 
           "pm_fam_discuss_election", 
           "pm_fam_discuss_invest"),
         "el_pm_consult_nonmig")

# Consults with family on migration ----
addIndex("pm_el",
         c("pm_fam_discuss_migrate",
           "pm_discuss_mig",
           "pm_discuss_responsibilities"),
         "el_pm_consult_mig")
```

```{r}
#| label: Summ-JointDecMake-Outcomes-PM
#| echo: False

# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_jointdec,
                   el_pm_consult_mig,
                   el_pm_consult_nonmig,
                   c("pm_daily_hh_expenses_couple",
                     "pm_hh_purchases_couple",
                     "pm_fam_plan_couple",
                     "pm_migrate_couple",
                     "pm_vote_couple",
                     "pm_school_couple",
                     "pm_discuss_women",
                     "pm_fam_discuss_work", 
                     "pm_fam_discuss_community", 
                     "pm_fam_discuss_election", 
                     "pm_fam_discuss_invest",
                     "pm_fam_discuss_migrate",
                     "pm_discuss_mig",
                     "pm_discuss_responsibilities")), 
            by = "hh_id") |>
  rename_at(vars(c("pm_daily_hh_expenses_couple",
                     "pm_hh_purchases_couple",
                     "pm_fam_plan_couple",
                     "pm_migrate_couple",
                     "pm_vote_couple",
                     "pm_school_couple",
                     "pm_discuss_women",
                     "pm_fam_discuss_work", 
                     "pm_fam_discuss_community", 
                     "pm_fam_discuss_election", 
                     "pm_fam_discuss_invest",
                     "pm_fam_discuss_migrate",
                     "pm_discuss_mig",
                     "pm_discuss_responsibilities")),
            ~paste0("el_", .))

# Summarize outcomes generated ----
summ(c("el_pm_jointdec",
       "el_pm_consult_mig",
       "el_pm_consult_nonmig"))
```


#### Attitudes and Values

```{r}
#| label: Gen-AttValues-Outcomes-PM

# Cleaning outcome components ----
pm_el <- pm_el |>
  mutate_at(vars(matches("pm_tol")), ~./10) |>
  mutate_at(vars(pm_marry_daughter_relig, 
                 pm_marry_daughter_eth,
                 pm_marry_son_relig,
                 pm_marry_son_eth), ~1*(. == 1)) |>
  mutate(rev_pm_prob_other_ethnicity = (4-pm_prob_other_ethnicity)/3)  |>
  mutate_at(vars(pm_neglects_children,
                 pm_argues,
                 pm_refuses_pray,
                 pm_burns_food),
            ~ 1-.)

# Tolerance (0-9) ----
addIndex("pm_el",
         c("pm_tol_relig",
           "pm_tol_eth",
           "pm_tol_mig",
           "pm_tol_muslim",
           "rev_pm_prob_other_ethnicity",
           "pm_marry_daughter_eth",
           "pm_marry_daughter_relig", 
           "pm_marry_son_relig",
           "pm_marry_son_eth"),
         "el_pm_tolerance")

# IPV attitudes (0-4) ----
addIndex("pm_el",
         c("pm_neglects_children",
           "pm_argues",
           "pm_refuses_pray",
           "pm_burns_food"),
         "el_pm_attitudes_ipv")

# Democracy index (0-3) ----
pm_el <- pm_el |>
  mutate(pm_rev_governance_opinion = 1L*(pm_governance_opinion == 1),
         pm_rule_law = (pm_rule_law-1)/3,
         pm_violence_justified = (pm_violence_justified-1)/3,
         pm_rev_society_opinion = (3-pm_society_opinion)/2)

addIndex("pm_el",
         c("pm_rev_governance_opinion",
           "pm_rule_law",
           "pm_violence_justified",
           "pm_rev_society_opinion"),
         "el_pm_democracy")

# Cosmopolitan index (0-2) ----
pm_el <- pm_el |>
  mutate(pm_constrain_customs = 1L*(pm_constrain_customs == 1),
         pm_free_move = (4 - pm_free_move)/3)

addIndex("pm_el",
         c("pm_constrain_customs",
           "pm_free_move"),
         "el_pm_cosmopolitan")

pm_el <- pm_el |>
  rename_at(vars(pm_rev_governance_opinion,
                 pm_rule_law,
                 pm_violence_justified,
                 pm_rev_society_opinion,
                 pm_surplus,
                 pm_constrain_customs,
                 pm_free_move),
            ~paste0("el_", .))

```

```{r}
#| label: Summ-AttValues-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_tolerance,
                   el_pm_attitudes_ipv,
                   c("pm_tol_relig",
                     "pm_tol_eth",
                     "pm_tol_mig",
                     "pm_tol_muslim",
                     "rev_pm_prob_other_ethnicity",
                     "pm_marry_daughter_eth",
                     "pm_marry_daughter_relig", 
                     "pm_marry_son_relig",
                     "pm_marry_son_eth",
                     "pm_neglects_children",
                     "pm_argues",
                     "pm_refuses_pray",
                     "pm_burns_food"),
                     el_pm_rev_governance_opinion,
                     el_pm_rule_law,
                     el_pm_violence_justified,
                     el_pm_surplus,
                     el_pm_rev_society_opinion,
                     el_pm_constrain_customs,
                     el_pm_free_move,
                   el_pm_cosmopolitan,
                   el_pm_democracy), 
            by = "hh_id") |>
  rename_at(vars("pm_tol_relig",
                 "pm_tol_eth",
                 "pm_tol_mig",
                 "pm_tol_muslim",
                 "rev_pm_prob_other_ethnicity",
                 "pm_marry_daughter_eth",
                 "pm_marry_daughter_relig", 
                 "pm_marry_son_relig",
                 "pm_marry_son_eth",
                 "pm_neglects_children",
                 "pm_argues",
                 "pm_refuses_pray",
                 "pm_burns_food"),
           ~paste0("el_pm_", gsub("pm_", "", .)))

# Summarize outcomes generated ----
summ(c("el_pm_tolerance", 
       "el_pm_attitudes_ipv"))
       

```

### SHM

#### Migration Expectations

```{r}
#| label: Gen-FutureEarn-Outcomes-SHM

# Secondary HH member's expectation of the PM's migration earnings: near-term
# (Q103) and 5-yr abroad (Q104). Same items/units as the PM report, but a second
# respondent reporting about the PM ("expect them to earn"), so kept as distinct
# shm_ panel columns (suffix shm_mig_futureEarn / shm_mig_earnAway_5y).
# The baseline non-comparability caveats noted for the PM items above do not
# bind here: at baseline the SHM future_earn was ungated (no home == 1 filter),
# matching the endline structure.
workfile <- shm_el |>
  transmute(
    hh_id,
    el_shm_mig_futureEarn  = shm_future_earn,      # Q103
    el_shm_mig_earnAway_5y = shm_future_earn_away  # Q104
  ) %>%
  left_join(workfile, ., by = "hh_id")

# Summarize outcomes generated ----
summ(c("el_shm_mig_futureEarn",
       "el_shm_mig_earnAway_5y"))
```

#### Mental Health
```{r}
#| label: Gen-MentHeatlh-Outcomes-SHM

# Cleaning outcome components ----
shm_el <- shm_el |>
  mutate(rev_shm_self_esteem_4 = (5 - shm_self_esteem_4)/4,
         rev_shm_self_esteem_9 = (5 - shm_self_esteem_9)/4,
         shm_emotion1 = (shm_emotion1)/3,
         shm_emotion2 = (shm_emotion2)/3,
         rev_shm_emotion3 = (3 - shm_emotion3)/3,
         rev_shm_emotion4 = (3 - shm_emotion4)/3,
         rev_shm_emotion5 = (3 - shm_emotion5)/3,
         rev_shm_emotion6 = (3 - shm_emotion6)/3,
         rev_shm_emotion7 = (3 - shm_emotion7)/3,
         rev_shm_home_problems = (4 - shm_home_problems)/3,
         rev_shm_idleness = (4 - shm_idleness)/3,
         rev_shm_alcohol_consumption = (4 - shm_alcohol_consumption)/3,
         rev_shm_family_death = (4 - shm_family_death)/3,
         rev_shm_money_problems = (4 - shm_money_problems)/3,
         rev_shm_debt_owed = (4 - shm_debt_owed)/3,
         rev_shm_cant_find_work = (4 - shm_cant_find_work)/3,
         rev_shm_cant_educate_children = (4 - shm_cant_educate_children)/3,
         rev_shm_accidents_disasters = (4 - shm_accidents_disasters)/3,
         shm_ladder_scale = shm_ladder_scale/10) 

# Emotion (0-9) ----
addIndex("shm_el",
         c("rev_shm_self_esteem_4",
           "rev_shm_self_esteem_9",
           "shm_emotion1",
           "shm_emotion2",
           "rev_shm_emotion3",
           "rev_shm_emotion4",
           "rev_shm_emotion5",
           "rev_shm_emotion6",
           "rev_shm_emotion7"),
         "el_shm_emotion")

# Stress: Family (0-4) ----
addIndex("shm_el",
         c("rev_shm_home_problems",
           "rev_shm_idleness",
           "rev_shm_alcohol_consumption",
           "rev_shm_family_death"),
         "el_shm_famstress")

# Stress: Economic (0-6) ----
addIndex("shm_el",
         c("rev_shm_money_problems",
           "rev_shm_debt_owed",
           "rev_shm_cant_find_work",
           "rev_shm_cant_educate_children",
           "rev_shm_accidents_disasters",
           "shm_ladder_scale"),
         "el_shm_econstress")
```

```{r}
#| label: Summ-MentHeatlh-Outcomes-SHM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(shm_el, hh_id,
                   el_shm_econstress,
                   el_shm_famstress,
                   el_shm_emotion,
                   c("rev_shm_self_esteem_4",
                     "rev_shm_self_esteem_9",
                     "shm_emotion1",
                     "shm_emotion2",
                     "rev_shm_emotion3",
                     "rev_shm_emotion4",
                     "rev_shm_emotion5",
                     "rev_shm_emotion6",
                     "rev_shm_emotion7",
                     "rev_shm_home_problems",
                     "rev_shm_idleness",
                     "rev_shm_alcohol_consumption",
                     "rev_shm_family_death",
                     "rev_shm_money_problems",
                     "rev_shm_debt_owed",
                     "rev_shm_cant_find_work",
                     "rev_shm_cant_educate_children",
                     "rev_shm_accidents_disasters",
                     "shm_ladder_scale")), 
            by = "hh_id") |>
  rename_at(vars(c("rev_shm_self_esteem_4",
                     "rev_shm_self_esteem_9",
                     "shm_emotion1",
                     "shm_emotion2",
                     "rev_shm_emotion3",
                     "rev_shm_emotion4",
                     "rev_shm_emotion5",
                     "rev_shm_emotion6",
                     "rev_shm_emotion7",
                     "rev_shm_home_problems",
                     "rev_shm_idleness",
                     "rev_shm_alcohol_consumption",
                     "rev_shm_family_death",
                     "rev_shm_money_problems",
                     "rev_shm_debt_owed",
                     "rev_shm_cant_find_work",
                     "rev_shm_cant_educate_children",
                     "rev_shm_accidents_disasters",
                     "shm_ladder_scale")),
            ~paste0("el_shm_", gsub("shm_", "", .)))

# Summarize outcomes generated ----
summ(c("el_shm_emotion",
       "el_shm_famstress",
       "el_shm_econstress"))

```


#### Joint Decision-Making

```{r}
#| label: Gen-JointDecMake-Outcomes-SHM

# Cleaning outcome components ----
shm_el <- shm_el |>
  mutate_at(vars(shm_daily_hh_expenses_couple,
                 shm_hh_purchases_couple,
                 shm_fam_plan_couple,
                 shm_migrate_couple,
                 shm_vote_couple,
                 shm_school_couple), ~(5-.)/4) |>
  mutate_at(vars(shm_fam_discuss_work, 
                 shm_fam_discuss_community, 
                 shm_fam_discuss_election, 
                 shm_fam_discuss_invest,
                 shm_discuss_women,
                 shm_fam_discuss_migrate),
            ~./3)

# Consults with spouse (0-7) ----
addIndex("shm_el",
         c("shm_daily_hh_expenses_couple",
           "shm_hh_purchases_couple",
           "shm_fam_plan_couple",
           "shm_migrate_couple",
           "shm_vote_couple",
           "shm_school_couple",
           "shm_discuss_women"),
         "el_shm_jointdec")

# Consults with family on issues other than migration (0-4) ----
addIndex("shm_el",
         c("shm_fam_discuss_work", 
           "shm_fam_discuss_community", 
           "shm_fam_discuss_election", 
           "shm_fam_discuss_invest"),
         "el_shm_consult_nonmig")

# Consults with family on migration ----
addIndex("shm_el",
         c("shm_fam_discuss_migrate",
           "shm_discuss_mig",
           "shm_discuss_responsibilities"),
         "el_shm_consult_mig")
```


```{r}
#| label: Summ-JointDecMake-Outcomes-SHM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(shm_el, hh_id,
                   el_shm_jointdec,
                   el_shm_consult_nonmig,
                   el_shm_consult_mig,
                   c("shm_daily_hh_expenses_couple",
                     "shm_hh_purchases_couple",
                     "shm_fam_plan_couple",
                     "shm_migrate_couple",
                     "shm_vote_couple",
                     "shm_school_couple",
                     "shm_discuss_women",
                     "shm_fam_discuss_work", 
                     "shm_fam_discuss_community", 
                     "shm_fam_discuss_election", 
                     "shm_fam_discuss_invest",
                     "shm_fam_discuss_migrate",
                     "shm_discuss_mig",
                     "shm_discuss_responsibilities")),
            by = "hh_id") |>
  rename_at(vars(c("shm_daily_hh_expenses_couple",
                     "shm_hh_purchases_couple",
                     "shm_fam_plan_couple",
                     "shm_migrate_couple",
                     "shm_vote_couple",
                     "shm_school_couple",
                     "shm_discuss_women",
                     "shm_fam_discuss_work", 
                     "shm_fam_discuss_community", 
                     "shm_fam_discuss_election", 
                     "shm_fam_discuss_invest",
                     "shm_fam_discuss_migrate",
                     "shm_discuss_mig",
                     "shm_discuss_responsibilities")),
            ~paste0("el_", .))

# Summarize outcomes generated ----
summ(c("el_shm_jointdec",
       "el_shm_consult_mig",
       "el_shm_consult_nonmig"))
```

### HoH

#### HH Size 

```{r}
#| label: Gen-Size-HH

# HH size ----
hh_size <- hoh_el |>
  select(hh_id, matches("hoh_roster_age_[0-9]+")) |>
  pivot_longer(cols = matches("hoh_roster_age_[0-9]+"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(!is.na(hoh_roster_age)) |>
  mutate(above18 = 1*(hoh_roster_age >= 18),
         below18 = 1*(hoh_roster_age < 18),
         below15 = 1*(hoh_roster_age < 15),
         above15 = 1*(hoh_roster_age >= 15),
         dum = 1) |>
  group_by(hh_id) |>
  summarize(el_hh_members = sum(dum, na.rm = T),
            el_hh_members_above18 = sum(above18, na.rm = T),
            el_hh_members_below18 = sum(below18, na.rm = T),
            el_hh_members_above15 = sum(above15, na.rm = T),
            el_hh_members_below15 = sum(below15, na.rm = T))

```

```{r}
#| label: Summ--Size-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(hh_size, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_hh_members",
       "el_hh_members_above18",
       "el_hh_members_below18",
       "el_hh_members_above15",
       "el_hh_members_below15"))


```

#### Migration outcomes

```{r}
#| label: Gen-Mig-Outcomes-HH

ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)

## Number of member migrating (ECOWAS, non-ECOWAS, Domestically) ----

### Function to get 

hh_mig <- function(df) {
  ## Getting PM names to remove from calculation ----
  pm_names <- df |>
    select(pm_name, hh_id) |>
    mutate(pm_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", pm_name)),
           dum_pm = 1) 
  
  ## MErging PM names to roster names, generating dummy for PM ----
  roster_names <- df |>
    select(hh_id, matches("hoh_roster_name_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_name_[0-9]+"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_roster_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", hoh_roster_name))) |>
    left_join(pm_names, by = c("hh_id", "hoh_roster_name" = "pm_name")) |>
    mutate(dum_pm = ifelse(is.na(dum_pm), 0, 1))
  
  
  # Member demographic info ----
  members_df <- df |>
    select(hh_id, matches("hoh_roster_age_[0-9]|hoh_roster_sex_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_age_[0-9]|hoh_roster_sex_[0-9]"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    filter(!is.na(hoh_roster_age))
  
  df |>
    select(hh_id, matches("hoh_dest_country_[0-9]")) |>
    mutate_at(vars(matches("hoh_dest_country_")), as.numeric) |>
    pivot_longer(cols = matches("hoh_dest_country_[0-9]+"),
      names_to = c(".value", "loc_ind", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)_([0-9]+)") |>
    left_join(roster_names, by = c("hh_id", "mem_ind")) |>
    left_join(members_df, by = c("hh_id", "mem_ind")) |>
    mutate_at(vars(mem_ind, loc_ind), as.numeric) |>
    filter(!is.na(hoh_dest_country) & hoh_dest_country != 0 & dum_pm == 0) |>
    mutate(dum_ec = 1*(loc_ind %in% ecowas_codes),
           dum_noec = 1*(loc_ind %in% noecowas_codes),
           dum_niger = 1*(loc_ind == 1),
           dum_ec_work = 1*(loc_ind %in% ecowas_codes & 
                            hoh_roster_age %in% 18:40 &
                            hoh_roster_sex == "Male"),
           dum_noec_work = 1*(loc_ind %in% noecowas_codes & 
                              hoh_roster_age %in% 18:40 &
                              hoh_roster_sex == "Male"),
           dum_niger_work = 1*(loc_ind == 1 & 
                               hoh_roster_age %in% 18:40 &
                               hoh_roster_sex == "Male"))  |>
  ungroup() |>
  rowwise() |>
  mutate(dum_any = pmax(dum_ec, dum_noec, dum_niger),
         dum_any_work = pmax(dum_ec_work, dum_noec_work, dum_niger_work)) |>
  ungroup()
}

mig_df_fu3 <- hh_mig(hoh_fu3) |>
  mutate(survey_wave = "fu3")

mig_df_fu4 <- hh_mig(hoh_fu4) |>
  mutate(survey_wave = "fu4")

# SG: this breaks for the same reason as genOutcomesFU5
mig_df_fu5 <- hh_mig(hoh_fu5) |>
  mutate(survey_wave = "fu4")

mig_df <- hh_mig(hoh_el) |>
  mutate(survey_wave = "fu5") |>
  bind_rows(mig_df_fu3) |>
  bind_rows(mig_df_fu4) |>
  bind_rows(mig_df_fu5) |>
  group_by(hh_id, hoh_roster_name) |>
  summarize(dum_ec = max(dum_ec, na.rm = T),
            dum_noec = max(dum_noec, na.rm = T),
            dum_niger = max(dum_niger, na.rm = T),
            dum_any = max(dum_any, na.rm = T),
            dum_ec_work = max(dum_ec_work, na.rm = T),
            dum_noec_work = max(dum_noec_work, na.rm = T),
            dum_niger_work = max(dum_niger_work, na.rm = T),
            dum_any_work = max(dum_any_work, na.rm = T)) |>
  ungroup() |>
  arrange(hh_id, hoh_roster_name) |>
  group_by(hh_id) |>
  summarize(el_hh_border_cross_ecowas = max(dum_ec),
            el_hh_border_cross_nonec = max(dum_noec),
            el_hh_dom_mig = max(dum_niger),
            el_hh_mig_any = max(dum_any),
            el_hh_border_cross_ecowas_work = max(dum_ec_work),
            el_hh_border_cross_nonec_work = max(dum_noec_work),
            el_hh_dom_mig_work = max(dum_niger_work),
            el_hh_mig_any_work = max(dum_any_work),
            el_hh_border_cross_ecowas_num = sum(dum_ec),
            el_hh_border_cross_nonec_num = sum(dum_noec),
            el_hh_dom_mig_num = sum(dum_niger),
            el_hh_mig_any_num = sum(dum_any),
            el_hh_border_cross_ecowas_work_num = sum(dum_ec_work),
            el_hh_border_cross_nonec_work_num = sum(dum_noec_work),
            el_hh_dom_mig_work_num = sum(dum_niger_work),
            el_hh_mig_any_work_num = sum(dum_any_work)) |>
  ungroup() |>
  full_join(select(hoh_el, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu5, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu4, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu3, hh_id), by = "hh_id") |>
  mutate_at(vars(matches("el_hh_")),
            ~ifelse(is.na(.), 0, .)) |>
  arrange(hh_id) 

```

```{r}
#| label: Summ-Mig-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(mig_df, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_hh_mig_any",
       "el_hh_dom_mig",
       "el_hh_border_cross_ecowas", 
       "el_hh_border_cross_nonec",
       "el_hh_mig_any_work",
       "el_hh_dom_mig_work",
       "el_hh_border_cross_ecowas_work", 
       "el_hh_border_cross_nonec_work",
       "el_hh_mig_any_num",
       "el_hh_dom_mig_num",
       "el_hh_border_cross_ecowas_num", 
       "el_hh_border_cross_nonec_num",
       "el_hh_mig_any_work_num",
       "el_hh_dom_mig_work_num",
       "el_hh_border_cross_ecowas_work_num", 
       "el_hh_border_cross_nonec_work_num"))

```


#### Failed Migration

```{r}
#| label: Gen-Failed-Mig-Outcomes-HH

ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)

## Number of member failed migration (ECOWAS, non-ECOWAS, Domestically) ----

### Function to get 
hh_failed_mig <- function(df) {
  ## Getting PM names to remove from calculation ----
  pm_names <- df |>
    select(pm_name, hh_id) |>
    mutate(pm_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", pm_name)),
           dum_pm = 1) 
  
  ## MErging PM names to roster names, generating dummy for PM ----
  roster_names <- df |>
    select(hh_id, matches("hoh_roster_name_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_name_[0-9]+"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_roster_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", hoh_roster_name))) |>
    left_join(pm_names, by = c("hh_id", "hoh_roster_name" = "pm_name")) |>
    mutate(dum_pm = ifelse(is.na(dum_pm), 0, 1))
  
  df |>
    select(hh_id, matches("hoh_failed_country_index_[0-9]+_[0-9]+")) |>
    pivot_longer(cols = matches("hoh_failed_country_index_[0-9]+"),
      names_to = c(".value", "mem_ind", "loc"),
      names_pattern = "(.+)_([0-9]+)_([0-9]+)") |>
    left_join(roster_names, by = c("hh_id", "mem_ind")) |>
    filter(dum_pm == 0 & hoh_failed_country_index != "") |>
    mutate(dum_failed_ec = 1*(hoh_failed_country_index %in% ecowas_codes),
           dum_failed_noec = 1*(hoh_failed_country_index %in% noecowas_codes),
           dum_failed_niger = 1*(hoh_failed_country_index == 1))  |>
  ungroup() |>
  rowwise() |>
  mutate(dum_failed_any = pmax(dum_failed_ec, dum_failed_noec, dum_failed_niger)) |>
  ungroup()
}

mig_df_fu3 <- hh_failed_mig(hoh_fu3) |>
  mutate(survey_wave = "fu3")

mig_df_fu4 <- hh_failed_mig(hoh_fu4) |>
  mutate(survey_wave = "fu4")

mig_df_fu5 <- hh_failed_mig(hoh_fu5) |>
  mutate(survey_wave = "fu5") |>
  mutate(mem_ind = as.character(mem_ind))

mig_df <- hh_failed_mig(hoh_el) |>
  mutate(survey_wave = "fu5") |>
  bind_rows(mig_df_fu3) |>
  bind_rows(mig_df_fu4) |>
  bind_rows(mig_df_fu5) |>
  group_by(hh_id, hoh_roster_name) |>
  summarize(dum_failed_ec = max(dum_failed_ec, na.rm = T),
            dum_failed_noec = max(dum_failed_noec, na.rm = T),
            dum_failed_niger = max(dum_failed_niger, na.rm = T),
            dum_failed_any = max(dum_failed_any, na.rm = T)) |>
  ungroup() |>
  arrange(hh_id, hoh_roster_name) |>
  group_by(hh_id) |>
  summarize(el_hh_failed_border_cross_ecowas = max(dum_failed_ec),
            el_hh_failed_border_cross_nonec = max(dum_failed_noec),
            el_hh_failed_dom_mig = max(dum_failed_niger),
            el_hh_failed_mig_any = max(dum_failed_any)) |>
  ungroup() |>
  full_join(select(hoh_el, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu5, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu4, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu3, hh_id), by = "hh_id") |>
  mutate_at(vars(matches("el_hh_")),
            ~ifelse(is.na(.), 0, .)) |>
  arrange(hh_id) 

```

```{r}
#| label: Summ-Failed-Mig-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(mig_df, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_hh_failed_mig_any",
       "el_hh_failed_dom_mig",
       "el_hh_failed_border_cross_ecowas", 
       "el_hh_failed_border_cross_nonec"))
```

#### Economic Well-Being

```{r}
#| label: Gen-Econ-Outcomes-HH

# Cleaning outcome components ----
hoh_el <- hoh_el |>
  mutate(hoh_remit_send_niger_amt = -hoh_remit_send_niger_amt,
         hoh_goods_send_niger_amt = -hoh_goods_send_niger_amt,
         hoh_livestock_expend = -hoh_livestock_expend,
         hoh_hire_livestock_total = -(hoh_hire_livestock_days*hoh_hire_livestock_wage),
         hoh_borrow_total = -hoh_borrow_total,
         hoh_adult_protein = case_when(hoh_adult_protein < 7 ~ 
                                         hoh_adult_protein,
                                   .default = 7),
         hoh_child_protein = case_when(hoh_child_protein < 7 ~ 
                                         hoh_child_protein,
                                   .default = 7),
         livestock_paid = hoh_paid_livestock_wage * 12 *
           hoh_paid_livestock_days) |>
         # hoh_total_income = hoh_total_income,
         # hoh_rent_land_amt = - hoh_rent_land_amt) |>
  mutate_at(vars(hoh_purchase_clothing, 
                 hoh_purchase_sheep, 
                 hoh_purchase_goat, 
                 hoh_purchase_poultry,
                 c(getVarnames(hoh_el, "emerg_sell_[1-9]"),
                   getVarnames(hoh_el, "emerg_borrow_[1-9]"),
                   getVarnames(hoh_el, "emerg_consume_[1-9]"),
                   getVarnames(hoh_el, "emerg_spend_[1-9]"))),
            ~case_when(. < 0 ~ NA,
                       .default = .)) |>
  mutate_at(vars(hoh_adults_skip_meal_num, 
                 hoh_adults_skip_days_num,
                 hoh_adult_protein,
                 hoh_child_skip_days_num,
                 hoh_child_skip_meals_num,
                 hoh_child_protein), ~./7) |>
  # mutate_at(vars(matches("hoh_monthly_consumption_amt_"),
  #                matches("hoh_weekly_consumption_amt_"),
  #                hoh_savings_total,
  #                hoh_borrow_total,
  #                hoh_earn_rent,
  #                hoh_income_gifts,
  #                hoh_earn_interest,
  #                hoh_biz_income,
  #                ), ~./hhmembers) |>
  mutate(across(starts_with("hoh_crop_quantity_"), 
              ~ . * get(sub("crop_quantity", "price_sold", cur_column())), 
              .names = "A_{.col %>% str_extract('[0-9]+')}")) 


temp_monthconscat_df <- hoh_el |>
  select(hh_id, 
         matches("hoh_monthly_consumption_amt_[0-9]"),
         matches("hoh_item_[0-9]")) |>
  pivot_longer(
    cols = matches("hoh_monthly_consumption_amt_[0-9]|hoh_item_[0-9]"),
    names_to = c(".value", "item_number"),
    names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_item = case_when(hoh_item %in% 
                            c("Education (children, excluding school fees)", 
                              "Education (enfants, hors frais de scolarité)",	
                              "Tarbiya (yara, ban da kuɗin makaranta)") ~ "el_hh_monthcons_edu_child",
                          hoh_item %in% 
                            c("Education (adults, including vocational training)",
                              "Éducation (adultes, y compris la formation professionnelle)",	
                              "Ilimi (manya, gami da koyar da sana'a") ~ "el_hh_monthcons_edu_adult",
                          hoh_item %in% 
                            c("Healthcare",	"Soins de santé", "Kiwon lafiya") ~ "el_hh_monthcons_health",
                          hoh_item %in% c("Ceremonies", "Cérémonies", "bukukuwa") ~ "el_hh_monthcons_ceremony",
                          hoh_item %in% c("Clothes + shoes", "Vêtements + chaussures", 
                                           "Tufafi + takalma") ~ "el_hh_monthcons_clothes",
                          .default = NA)) |>
  filter(hoh_item != "") |>
  select(-item_number) |>
  pivot_wider(names_from = "hoh_item", values_from = "hoh_monthly_consumption_amt") |>
  mutate_at(vars(matches("el_hoh_monthcons")), ~case_when(is.na(.) ~ 0, .default = .))


temp_weekconscat_df <- hoh_el |>
  select(hh_id, 
         matches("hoh_weekly_consumption_amt_[0-9]"),
         matches("hoh_item_week_[0-9]")) |>
  pivot_longer(
    cols = matches("hoh_weekly_consumption_amt_[0-9]|hoh_item_week_[0-9]"),
    names_to = c(".value", "item_number"),
    names_pattern = "(.+)_([0-9]+)") |>
  mutate(hoh_item_week = case_when(hoh_item_week %in% 
                            c("Food (for household members)",	
                              "Nourriture (pour les membres du ménage)",
                              "Abinci (ga mutanen gida)") ~ "el_hh_weekcons_food",
                          hoh_item_week %in% 
                            c("Mobile phone credit + charging", 
                              "Crédit mobile + recharge", 
                              "Kuɗin /kiredin kira a salula + caji") ~ "el_hh_weekcons_phone",
                          hoh_item_week %in% 
                            c("Fuel for home/ cooking (i.e. lighting, electricity, firewood)",
                              "Combustible pour la maison/la cuisine (c.-à-d. éclairage, électricité, bois de chauffage)",	
                              "Makamashi na gidan don / dafa abinci ( haske gida , wutar lantarki, itacen jin wuta)") ~ "el_hh_weekcons_homefuel",
                          hoh_item_week %in% c("Fuel for vehicles",
                                      "Carburant pour véhicules",
                                      "Man fetur/isansi na mota") ~ "el_hh_weekcons_vehiclefuel",
                          hoh_item_week %in% c("Transportation fare (taxi, moto taxi)",
                                      "Frais de transport (taxi, moto taxi)",
                                      "Kuɗin (taxi, kabu- kabu )") ~ "el_hh_weekcons_transport",
                          hoh_item_week %in% c("Water (to drink)",
                                      "Eau (à boire)",
                                      "Ruwa (don sha)") ~ "el_hh_weekcons_water",
                          .default = NA)) |>
  filter(hoh_item_week != "") |>
  select(-item_number) |>
  pivot_wider(names_from = "hoh_item_week", values_from = "hoh_weekly_consumption_amt") |>
  mutate_at(vars(matches("el_hh_weekcons")), ~case_when(is.na(.) ~ 0, .default = .))


### Disabled in EL
# # Ag income (CFA) ) ----
# temp_df <- hoh_el |> 
#   select(hh_id, matches("hoh_qty_consume_[0-9]+|hoh_price_consume_[0-9]+|hoh_qty_left_[0-9]+|hoh_price_left_[0-9]+")) |>
#   pivot_longer(
#     cols = matches("hoh_qty_consume_[0-9]+|hoh_price_consume_[0-9]+|hoh_qty_left_[0-9]+|hoh_price_left_[0-9]+"),
#     names_to = c(".value", "crop_ind"),
#     names_pattern = "(.+)_([0-9]+)") |>
#   mutate(crop_cons_income = hoh_qty_consume * hoh_price_consume,
#          crop_left_income = hoh_qty_left * hoh_price_left) |>
#          # crop_inc = crop_left_income) |>
#   rowwise() |>
#   mutate(crop_inc = sum(crop_left_income, crop_cons_income, na.rm = T)) |>
#   ungroup() |>
#   group_by(hh_id) |>
#   summarize(crop_inc_hh = sum(crop_inc, na.rm = T))

# hoh_el <- left_join(hoh_el, temp_df, by = "hh_id")  |>
#   # mutate(crop_inc_pc = crop_inc_hh/hhmembers) |>
#   mutate_at(vars(c("hoh_total_income",
#            "crop_inc_hh", "hoh_rent_land_amt")), ~ifelse(is.na(.), 0, .))
# 
# addIndex("hoh_el",
#          c("hoh_total_income",
#            "crop_inc_hh", "hoh_rent_land_amt"),
#          "el_hh_ag_inc")

# rm(temp_df)

# Livestock income (CFA) ----

temp_df2 <- hoh_el |>
  select(hh_id, matches("hoh_livestock_value_[0-9]+")) |>
  pivot_longer(
    cols = matches("hoh_livestock_value_[0-9]+"),
    names_to = c(".value", "_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
    group_by(hh_id) |>
    summarize(C = sum(hoh_livestock_value, na.rm = T))

temp_df <- hoh_el |> 
  select(hh_id, matches("hoh_livestock_sold_[0-9]+|hoh_livestock_sold_val_[0-9]+|hoh_livestock_consumed_[0-9]+|hoh_livestock_consumed_val_[0-9]+")) |>
  pivot_longer(
    cols = matches("hoh_livestock_sold_[0-9]+|hoh_livestock_sold_val_[0-9]+|hoh_livestock_consumed_[0-9]+|hoh_livestock_consumed_val_[0-9]+"),
    names_to = c(".value", "livestock_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  rowwise() |>
  mutate(livestock_inc = hoh_livestock_sold_val) |>
  ungroup() |>
  group_by(hh_id) |>
  summarize(livestock_inc_hh = sum(livestock_inc, na.rm = T)) |>
  left_join(temp_df2, by = "hh_id")

hoh_el <- left_join(hoh_el, temp_df, by = "hh_id") |>
  # mutate(livestock_inc_pc = livestock_inc_hh/hhmembers) |>
  mutate_at(vars(c("livestock_paid",
           "livestock_inc_hh", "hoh_livestock_expend",
           "hoh_hire_livestock_total", "C")), ~ifelse(is.na(.), 0, .))

addIndex("hoh_el",
         c("livestock_paid",
           "livestock_inc_hh", 
           "hoh_livestock_expend",
           "hoh_hire_livestock_total",
           "C"),
         "el_hh_livestock_inc")

rm(temp_df)

# Other income (CFA) ----
temp_df <- hoh_el |>
  select(hh_id, matches("hoh_member_other_weeks_[0-9]+|hoh_member_other_amt_[0-9]+")) |>
  pivot_longer(
    cols = matches("hoh_member_other_weeks_[0-9]+|hoh_member_other_amt_[0-9]+"),
    names_to = c(".value", "mem_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
    mutate(mem_other_inc = hoh_member_other_amt * hoh_member_other_weeks) |>
    group_by(hh_id) |>
    summarize(other_inc_hh = sum(mem_other_inc, na.rm = T))
    
  
hoh_el <- left_join(hoh_el, temp_df, by = "hh_id") |>
  # mutate(other_inc_pc = other_inc_hh/hhmembers) |>
  mutate_at(vars(c("hoh_earn_rent",
           "other_inc_hh", "hoh_income_gifts",
           "hoh_earn_interest")), ~ifelse(is.na(.), 0, .))
  
addIndex("hoh_el",
         c("other_inc_hh", 
           "hoh_earn_rent",
           "hoh_income_gifts",
           "hoh_earn_interest"),
         "el_hh_other_inc")
rm(temp_df)

# Business income (CFA) ----
hoh_el <- hoh_el |>
  mutate(el_hh_biz_inc = ifelse(hoh_own_biz == 1, hoh_biz_income, 0))


# Remittances (CFA) ---- 
## pm_names to identify PMs from roster 
pm_names <- hoh_bl |> 
  select(hh_id, pm_name) |>
  mutate(pm_name_str = stringi::stri_trans_general(tolower(gsub(" ", "", sub(" \\(age: [0-9]+\\)", "", pm_name))), "Latin-ASCII"))
  
#Amount contributed to HH common pot by PM
contribute_df <- hoh_el |>
  select(hh_id, matches("hoh_member_contribute_[0-9]+|hoh_member_act_name_[0-9]+")) |>
  pivot_longer(cols = matches("hoh_member_contribute_[0-9]+|hoh_member_act_name_[0-9]+"),
               names_to = c(".value", "member"),
               names_pattern = "(.+)_([0-9]+)") |>
  select(hh_id, hoh_member_act_name, hoh_member_contribute) |>
  mutate(member_act_name_str = stringi::stri_trans_general(tolower(gsub(" ", "", sub(" \\(age: [0-9]+\\)", "", hoh_member_act_name))), "Latin-ASCII")) |>
  left_join(pm_names, by = c("hh_id", "member_act_name_str" = "pm_name_str")) |>
  filter(!is.na(pm_name)) |>
  distinct(hh_id, member_act_name_str, .keep_all = T) |>
  select(hh_id, 
         el_hh_pm_contribute = hoh_member_contribute)

addIndex("hoh_el",
         c("hoh_remit_rec_niger_amt",
           "hoh_goods_rec_niger_amt",
           "hoh_remit_send_niger_amt",
           "hoh_goods_send_niger_amt"),
         "el_hh_remit")

# Savings (CFA) ----
addIndex("hoh_el",
         c("hoh_savings_total",
           "hoh_borrow_total"),
         "el_hh_savings")


# Monthly expenditures (CFA) ----
addIndex("hoh_el",
         c("hoh_monthly_consumption_amt_1",
           "hoh_monthly_consumption_amt_2",
           "hoh_monthly_consumption_amt_3",
           "hoh_monthly_consumption_amt_4",
           "hoh_monthly_consumption_amt_5"),
         "el_hh_monthly_cons")

# Weekly expenditures (CFA) ----
addIndex("hoh_el",
         c("hoh_weekly_consumption_amt_1",
           "hoh_weekly_consumption_amt_2",
           "hoh_weekly_consumption_amt_3",
           "hoh_weekly_consumption_amt_4",
           "hoh_weekly_consumption_amt_5",
           "hoh_weekly_consumption_amt_6"),
         "el_hh_weekly_cons")

# Ramadan Expenditures (CFA) ----
addIndex("hoh_el",
         c("hoh_purchase_clothing", 
           "hoh_purchase_sheep", 
           "hoh_purchase_goat", 
           "hoh_purchase_poultry"),
         "el_hh_fest_cons")

# Adult food security (0-3) ----
addIndex("hoh_el",
         c("hoh_adults_skip_meal_num", 
           "hoh_adults_skip_days_num",
           "hoh_adult_protein"), 
         "el_hh_adult_foodsec")


# Child food security (0-3) ----
addIndex("hoh_el",
         c("hoh_child_skip_meals_num", 
           "hoh_child_skip_days_num",
           "hoh_child_protein"), 
         "el_hh_child_foodsec")

## Reversing so it is food security
hoh_el <- hoh_el |>
  mutate(el_hh_adult_foodsec = 3 - el_hh_adult_foodsec,
         el_hh_child_foodsec = 3 - el_hh_child_foodsec)


# Economic Precarity (events) ----
addIndex("hoh_el",
         c(getVarnames(hoh_el, "emerg_sell_[1-9]"),
           getVarnames(hoh_el, "emerg_borrow_[1-9]"),
           getVarnames(hoh_el, "emerg_consume_[1-9]"),
           getVarnames(hoh_el, "emerg_spend_[1-9]")),
         "el_hh_emerg_event")

# Economic Precarity (cost in CFA) ----
addIndex("hoh_el",
         c(getVarnames(hoh_el, "emerg_sell_amt_[1-9]"),
           getVarnames(hoh_el, "emerg_borrow_amt_[1-9]"),
           getVarnames(hoh_el, "emerg_spend_amt_[1-9]")),
         "el_hh_emerg_cost")
```


```{r}
#| label: Summ-Econ-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(hoh_el, hh_id,
                   # el_hh_ag_inc,
                   # el_hh_total_income = hoh_total_income,
                   # el_hh_crop_prices = crop_inc_hh, 
                   # el_hh_rent_land_amt = hoh_rent_land_amt,
                   el_hh_livestock_inc,
                   el_hh_livestock_paid = livestock_paid,
                   el_hh_livestock_value = livestock_inc_hh, 
                   el_hh_livestock_expend = hoh_livestock_expend,
                   el_hh_hire_livestock_total = hoh_hire_livestock_total,
                   el_hh_livestock_holdings = C,
                   el_hh_other_inc,
                   el_hh_biz_inc,
                   el_hh_remit,
                   el_hh_savings,
                   el_hh_savings_total = hoh_savings_total,
                   el_hh_borrow_total = hoh_borrow_total,
                   el_hh_monthly_cons,
                   el_hh_weekly_cons,
                   el_hh_fest_cons,
                   el_hh_adult_foodsec,
                   el_hh_child_foodsec,
                   el_hh_emerg_event,
                   el_hh_emerg_cost), 
            by = "hh_id") |>
  left_join(temp_monthconscat_df, by = "hh_id") |>
  left_join(temp_weekconscat_df, by = "hh_id") |>
  mutate_at(vars(matches("el_hh_weekcons|el_hh_monthcons")), 
            ~case_when(el_hoh_comp == 1 & is.na(.) ~ 0,
                       .default = .))  |>
  left_join(contribute_df, by = "hh_id")


# Summarize outcomes generated ----
summ(c(
  # "el_hh_ag_inc",
       "el_hh_livestock_inc",
       "el_hh_other_inc", 
       "el_hh_biz_inc", 
       "el_hh_remit",
       "el_hh_pm_contribute",
       "el_hh_savings",
       "el_hh_monthly_cons",
       "el_hh_weekly_cons",
       "el_hh_fest_cons",
       "el_hh_adult_foodsec",
       "el_hh_child_foodsec",
       "el_hh_emerg_event",
       "el_hh_emerg_cost"))
```

#### Investments

```{r}
#| label: Gen-Inv-Outcomes-HH

# Cleaning outcome components ----
temp_df1 <- hoh_el |>
  select(hh_id, matches("hoh_livestock_bought_val_[0-9]+")) |>
  pivot_longer(cols = matches("hoh_livestock_bought_val_[0-9]+"),
               names_to = c(".value", "_ind"),
               names_pattern = "(.+)_([0-9]+)") |>
    group_by(hh_id) |>
    summarize(hoh_livestock_bought_amt = sum(hoh_livestock_bought_val, na.rm = T))
  
# Num school age members and asset counts
temp_school_assets_df <- hoh_el |>
  mutate_at(vars(matches("hoh_roster_age_[0-9]+")), 
            ~case_when(. %in% 4:27 ~ 1,
                       .default = 0)) |>
  select(hh_id, 
         matches("hoh_roster_age_[0-9]+"), 
         matches("hoh_durable_asset_[0-9]+"),
         matches("hoh_school_cost_[0-9]+")) |>
  pivot_longer(
    cols = matches("hoh_roster_age_[0-9]+|hoh_durable_asset_[0-9]+|hoh_school_cost_[0-9]+"),
    names_to = c(".value", "id"),
    names_pattern = "(.+)_([0-9]+)") |>
  group_by(hh_id) |>
  summarize(B = sum(hoh_durable_asset, na.rm = T),
            N_schoolage = sum(hoh_roster_age, na.rm = T),
            cost_school = sum(hoh_school_cost, na.rm = T))
  
# Select business assets. Merge in all data
temp_df <- hoh_el |>
  mutate(A = 1*(hoh_durable_asset_10 == 1) + 1*(hoh_durable_asset_11 == 1) + 
           1*(hoh_durable_asset_12 == 1)) |> 
  left_join(temp_school_assets_df, by = "hh_id") |>
  mutate_at(vars(B, N_schoolage, cost_school), ~ifelse(is.na(.), 0, .))



# Business investment (livestock purchase, business/land improvement) ----
hoh_el <- left_join(temp_df, temp_df1, by = "hh_id") 

rm(temp_df, temp_df1, temp_df2)

# Business investment (livestock purchase, business/land improvement) ----
## Getting BL values for normalization ----
## Getting BL values for normalization ----
# temp_livestock_price_df <-  hoh_livestock_bl |>
#   mutate(price = livestock_value/livestock_own) |>
#   mutate(livestock_id =   case_when(
#     livestock_name %in% c("Chickens", "Poulets", "Kaji") ~ 1,
#     livestock_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
#     livestock_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
#     livestock_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
#     livestock_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
#     livestock_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
#     livestock_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
#     livestock_name %in% c("None", "Aucun", "Babu") ~ 0,
#     TRUE ~ NA_real_  # In case of any unexpected value
#   )) |>
#   group_by(livestock_id) |>
#   summarize(med_price = median(price, na.rm = T))
# 
# temp_livestock_bought_df <- hoh_livestockact_bl |>
#   mutate(livestock_id =   case_when(
#     livestock_act_name %in% c("Chickens", "Poulets", "Kaji") ~ 1,
#     livestock_act_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
#     livestock_act_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
#     livestock_act_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
#     livestock_act_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
#     livestock_act_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
#     livestock_act_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
#     livestock_act_name %in% c("None", "Aucun", "Babu") ~ 0,
#     TRUE ~ NA_real_  # In case of any unexpected value
#   )) |> 
#   left_join(temp_livestock_price_df, by = "livestock_id") |>
#   mutate(livestock_bought_amt = med_price*livestock_bought) |>
#   group_by(hh_id) |>
#   summarize(D = sum(livestock_bought_amt, na.rm = T)) |>
#   mutate(bl_hoh_livestock_bought_amt = as.numeric(D))
# 
# bl_data_temp <- hoh_bl |>
#   left_join(temp_livestock_bought_df, by = "hh_id") |>
#   mutate(A = 1*(durable_asset_10 == 1) + 1*(durable_asset_11 == 1) + 
#            1*(durable_asset_12 == 1),
#          bl_hoh_livestock_bought_amt = ifelse(is.na(bl_hoh_livestock_bought_amt), 0, bl_hoh_livestock_bought_amt),
#          land_purchased = ifelse(land_access_amt == 0, 0 , land_purchased),
#          improve_business = ifelse(own_biz == 0, 0, improve_business)) |>
#   select(c("bl_hoh_livestock_bought_amt",
#            "improve_business",
#            "improve_land"),
#          bl_hoh_land_purchased = land_purchased,
#          bl_A = A) |>
#   rename_at(vars(all_of(c("improve_business",
#                           "improve_land"))),
#             ~paste0("bl_hoh_",  .)) |>
#   trim("bl_hoh_livestock_bought_amt") |>
#   trim("bl_hoh_land_purchased") |>
#   select(-bl_hoh_land_purchased, 
#          -bl_hoh_livestock_bought_amt)
# 
# bl_means <- bl_data_temp |>
#   summarize_all(~mean(., na.rm = T)) |>
#   rename_all(~paste0(., "_mean"))
# 
# bl_sd <- bl_data_temp |>
#   summarize_all(~sd(., na.rm = T)) |>
#   rename_all(~paste0(., "_sd"))
# 
# bl_stats <- do.call("rbind", replicate(
#   nrow(hoh_el), bind_cols(bl_means, bl_sd), simplify = FALSE))
# 
# # Normalized data by BL value
# norm_temp_inv_df <- hoh_el |>
#   mutate(hoh_improve_business = ifelse(hoh_own_biz == 0, 0, hoh_improve_business),
#          hoh_land_purchased = ifelse(hoh_land_access_amt == 0, 0, hoh_land_purchased)) |>
#   trim("hoh_livestock_bought_amt") |>
#   trim("hoh_land_purchased") |>
#   select(hh_id, c("hoh_livestock_bought_amt_tr", "A", "hoh_improve_business", 
#                   "hoh_improve_land", "hoh_land_purchased_tr")) |>
#   cbind(bl_stats) |>
#   mutate(across(c("hoh_livestock_bought_amt_tr", "A", "hoh_improve_business", 
#                   "hoh_improve_land", "hoh_land_purchased_tr"),
#                 ~ (. - get(paste0("bl_", cur_column(), "_mean"))) / 
#                   get(paste0("bl_", cur_column(), "_sd")),
#     .names = "{.col}_std")) |>
#   filter(!is.na(hoh_livestock_bought_amt_tr) & 
#            !is.na(hoh_land_purchased_tr)) |>
#   select(hh_id, matches("_std"))
# 
# # Get PC1 loading
# std_vars_inv <- select(norm_temp_inv_df, ends_with("_std"))
# pca_result_inv <- prcomp(std_vars_inv, center = FALSE, scale. = FALSE)
# pc1_loadings_inv <- pca_result_inv$rotation[, 1]
# 
# # Weight each standardized value by the PCA loadings and add for PC1 by observation
# pca_df_inv <- norm_temp_inv_df |>
#   mutate(el_hh_biz_inv = as.matrix(std_vars_inv) %*% pc1_loadings_inv) |>
#   select(hh_id, el_hh_biz_inv)


#### hoh_land_purchased, hoh_own_hectares use from FU5, disabled in EL
temp_inv_df <- hoh_el |>
  mutate(hoh_improve_business = ifelse(hoh_own_biz == 0, 0, hoh_improve_business)) |>
         # hoh_land_purchased = ifelse(hoh_land_access_amt == 0, 0, hoh_land_purchased)) |>
  trim("hoh_livestock_bought_amt")
  # trim("hoh_land_purchased")

stat_vars <- temp_inv_df |> 
  filter(S == "mc" & Z == "c") |>
  summarize(
    # mean_hoh_land_purchased_tr = mean(hoh_land_purchased_tr, na.rm = T),
            # sd_hoh_land_purchased_tr = sd(hoh_land_purchased_tr, na.rm = T),
            mean_hoh_livestock_bought_amt_tr = mean(hoh_livestock_bought_amt_tr, na.rm = T),
            sd_hoh_livestock_bought_amt_tr = sd(hoh_livestock_bought_amt_tr, na.rm = T),
            mean_A = mean(A, na.rm = T),
            sd_A = sd(A, na.rm = T),
            mean_hoh_improve_land = mean(hoh_improve_land, na.rm = T),
            sd_hoh_improve_land = sd(hoh_improve_land, na.rm = T),
            mean_hoh_improve_business = mean(hoh_improve_business, na.rm = T),
            sd_hoh_improve_business = sd(hoh_improve_business, na.rm = T)) 

stat_vars <- do.call("rbind", replicate(nrow(temp_inv_df), 
                                      stat_vars, simplify = FALSE))

temp_inv_df <- temp_inv_df |>
  cbind(stat_vars)

std_vars_inv <- temp_inv_df |>
  mutate(across(c(
    # "hoh_land_purchased_tr", 
    "A", "hoh_improve_business", 
                  "hoh_improve_land", "hoh_livestock_bought_amt_tr"),
                ~ (. - get(paste0("mean_", cur_column()))) / 
                  get(paste0("sd_", cur_column())),
    .names = "{.col}_std")) |>
  select(matches("_std"))


pca_result_inv <- prcomp(std_vars_inv, center = F, scale. = F)
temp_inv_df$el_hh_biz_inv <- pca_result_inv$x[, 1]

pca_df_inv <- temp_inv_df |>
  select(hh_id, el_hh_biz_inv)


# Education (number of children enrolled) ----
temp_enroll_df <- hoh_el |> 
  select(hh_id, matches("hoh_attending_school")) |>
  pivot_longer(
    cols = matches("hoh_attending_school"),
    names_to = c(".value", "id"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(!is.na(hoh_attending_school)) |>
  group_by(hh_id) |>
  summarize(el_hh_enroll_num = sum(hoh_attending_school))

hoh_el <- left_join(hoh_el, temp_enroll_df, by = "hh_id") |>
  mutate(el_hh_enroll_num = ifelse(is.na(el_hh_enroll_num), 0, el_hh_enroll_num))
# Education (cost per child) ---- 
hoh_el <- hoh_el |>
  mutate(el_hh_enroll_cost = cost_school)


# Assets (durable goods, livestock, home, land) ----
## Getting BL values for normalization ----
# temp_livestock_assets <- hoh_livestock_bl |>
#   group_by(hh_id) |>
#   summarize(bl_C = sum(livestock_value, na.rm = T)) |>
#   right_join(select(hoh_bl, hh_id), by = "hh_id") |>
#   mutate(bl_C = ifelse(is.na(bl_C), 0, bl_C))
# 
# temp_durable_assets <- hoh_bl |>
#   select(hh_id, matches("durable_asset_[0-9]")) |>
#   pivot_longer(cols = matches("durable_asset_[0-9]"),
#                names_to = c(".value", "asset"),
#                names_pattern = "(.+)_([0-9]+)") |>
#   group_by(hh_id) |>
#   summarize(bl_B = sum(durable_asset, na.rm = T))
# 
# 
# bl_data_temp <- hoh_bl |> 
#   mutate(home_value = ifelse(own_home == 0, 0, home_value),
#          improve_home_amt = ifelse(improve_add_rooms == 0 &
#                                      improve_floors == 0 & 
#                                      improve_walls == 0& 
#                                      improve_roof == 0 &
#                                      improve_o == 0, 0, 
#                                    improve_home_amt)) |>
#   left_join(temp_livestock_assets, by = "hh_id") |>
#   left_join(temp_durable_assets, by = "hh_id") |>
#   trim("bl_C") |>
#   trim("home_value") |>
#   trim("improve_home_amt") |>
#   trim("own_hectares") |>
#   select(c("bl_B",
#            "bl_C_tr",
#            "improve_add_rooms",
#            "improve_floors",
#            "improve_walls",
#            "improve_roof",
#            "home_value_tr",
#            "improve_home_amt_tr",
#            "own_hectares_tr")) |>
#   rename_at(vars(all_of(c("improve_add_rooms",
#                         "improve_floors",
#                         "improve_walls",
#                         "improve_roof",
#                         "home_value_tr",
#                         "improve_home_amt_tr",
#                         "own_hectares_tr"))),
#             ~paste0("bl_hoh_",  .))
# 
# bl_means <- bl_data_temp |>
#   summarize_all(~mean(., na.rm = T)) |>
#   rename_all(~paste0(., "_mean"))
# 
# bl_sd <- bl_data_temp |>
#   summarize_all(~sd(., na.rm = T)) |>
#   rename_all(~paste0(., "_sd"))
# 
# bl_stats <- do.call("rbind", replicate(
#   nrow(hoh_el), bind_cols(bl_means, bl_sd), simplify = FALSE))
# 
# ## Normalizing, Calculating PCA of normalized values ----
# 
# # Normalized data by BL value
# temp_df <- hoh_el |>
#   # left_join(select(temp_df, hh_id, B, C), by = "hh_id") |>
#   mutate(hoh_home_value = ifelse(hoh_own_home == 0 | is.na(hoh_own_home), 0, hoh_home_value),
#          hoh_home_value = ifelse(is.na(hoh_home_value), 0, hoh_home_value),
#          hoh_improve_home_amt = ifelse(hoh_improve_add_rooms == 0 &
#                                        hoh_improve_floors == 0 & 
#                                        hoh_improve_walls == 0& 
#                                        hoh_improve_roof == 0 &
#                                        hoh_improve_o == 0, 0, hoh_improve_home_amt)) |>
#   trim("C") |>
#   trim("hoh_home_value") |>
#   trim("hoh_improve_home_amt") |>
#   trim("hoh_own_hectares") |>
#   select(hh_id, c("B",
#            "C_tr",
#            "hoh_improve_add_rooms",
#            "hoh_improve_floors",
#            "hoh_improve_walls",
#            "hoh_improve_roof",
#            "hoh_home_value_tr",
#            "hoh_improve_home_amt_tr",
#            "hoh_own_hectares_tr")) |>
#   cbind(bl_stats) |>
#   mutate(across(c(B,
#                   C_tr,
#                   hoh_improve_add_rooms,
#                   hoh_improve_floors,
#                   hoh_improve_walls,
#                   hoh_improve_roof,
#                   hoh_home_value_tr,
#                   hoh_improve_home_amt_tr,
#                   hoh_own_hectares_tr),
#                 ~ (. - get(paste0("bl_", cur_column(), "_mean"))) / 
#                   get(paste0("bl_", cur_column(), "_sd")),
#     .names = "{.col}_std")) |>
#   filter(!is.na(C_tr) &
#            !is.na(hoh_home_value_tr) & 
#            !is.na(hoh_improve_home_amt_tr) & 
#            !is.na(hoh_own_hectares_tr)) |>
#   select(hh_id, matches("_std")) 
# 
# # Get PC1 loading
# std_vars <- select(temp_df, ends_with("_std"))
# pca_result <- prcomp(std_vars, center = FALSE, scale. = FALSE)
# pc1_loadings <- pca_result$rotation[, 1]
# 
# # Weight each standardized value by the PCA loadings and add for PC1 by observation
# pca_df <- temp_df |>
#   mutate(el_hh_assets = as.matrix(std_vars) %*% pc1_loadings) |>
#   select(hh_id, el_hh_assets)



norm_temp_df <- hoh_el |>
  mutate(hoh_home_value = ifelse(hoh_own_home == 0 | is.na(hoh_own_home), 0, hoh_home_value),
         hoh_home_value = ifelse(is.na(hoh_home_value), 0, hoh_home_value),
         hoh_improve_home_amt = ifelse(hoh_improve_add_rooms == 0 &
                                       hoh_improve_floors == 0 & 
                                       hoh_improve_walls == 0& 
                                       hoh_improve_roof == 0 &
                                       hoh_improve_o == 0, 0, hoh_improve_home_amt)) |>
  trim("C") |>
  trim("hoh_home_value") |>
  trim("hoh_improve_home_amt") 
  # trim("hoh_own_hectares")


stat_vars <- norm_temp_df |> 
  filter(S == "mc" & Z == "c") |>
  summarize(mean_B = mean(B, na.rm = T),
            sd_B = sd(B, na.rm = T),
            mean_C_tr = mean(C_tr, na.rm = T),
            sd_C_tr = sd(C_tr, na.rm = T),
            mean_hoh_improve_add_rooms = mean(hoh_improve_add_rooms, na.rm = T),
            sd_hoh_improve_add_rooms = sd(hoh_improve_add_rooms, na.rm = T),
            mean_hoh_improve_floors = mean(hoh_improve_floors, na.rm = T),
            sd_hoh_improve_floors = sd(hoh_improve_floors, na.rm = T),
            mean_hoh_improve_walls = mean(hoh_improve_walls, na.rm = T),
            sd_hoh_improve_walls = sd(hoh_improve_walls, na.rm = T),
            mean_hoh_improve_roof = mean(hoh_improve_roof, na.rm = T),
            sd_hoh_improve_roof = sd(hoh_improve_roof, na.rm = T),
            mean_hoh_home_value_tr = mean(hoh_home_value_tr, na.rm = T),
            sd_hoh_home_value_tr = sd(hoh_home_value_tr, na.rm = T),
            mean_hoh_improve_home_amt_tr = mean(hoh_improve_home_amt_tr, na.rm = T),
            sd_hoh_improve_home_amt_tr = sd(hoh_improve_home_amt_tr, na.rm = T))
            # mean_hoh_own_hectares_tr = mean(hoh_own_hectares_tr, na.rm = T),
            # sd_hoh_own_hectares_tr = sd(hoh_own_hectares_tr, na.rm = T)) 


stat_vars <- do.call("rbind", replicate(nrow(norm_temp_df), 
                                      stat_vars, simplify = FALSE))

norm_temp_df <- norm_temp_df |>
  select(hh_id, c("B", 
                  "hoh_improve_add_rooms",
                  "hoh_improve_floors",
                  "hoh_improve_walls",
                  "hoh_improve_roof",
                  "hoh_home_value_tr",
                  "hoh_improve_home_amt_tr")) |>
                  # "hoh_own_hectares_tr")) |>
  cbind(stat_vars)
  
std_vars <- norm_temp_df |>
  mutate(across(c("B",
                  "hoh_improve_add_rooms",
                  "hoh_improve_floors",
                  "hoh_improve_walls",
                  "hoh_improve_roof",
                  "hoh_home_value_tr",
                  "hoh_improve_home_amt_tr"),
                  # "hoh_own_hectares_tr"),
                ~ (. - get(paste0("mean_", cur_column()))) / 
                  get(paste0("sd_", cur_column())),
    .names = "{.col}_std")) |>
  select(matches("_std"))


pca_result <- prcomp(std_vars, center = F, scale. = F)
norm_temp_df$el_hh_assets <- pca_result$x[, 1]

pca_df <- norm_temp_df |>
  select(hh_id, el_hh_assets)

```


```{r}
#| label: Summ-Inv-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(hoh_el, hh_id, 
                   el_hh_enroll_num,
                   el_hh_enroll_cost), by = "hh_id") |>
  left_join(pca_df_inv, by = "hh_id") |>
  left_join(pca_df, by = "hh_id")  |>
  mutate_at(c("el_hh_assets", 
              "el_hh_biz_inv"), ~(scale(.) %>% as.vector))

# Summarize outcomes generated ----
summ(c("el_hh_biz_inv",
       "el_hh_enroll_cost",
       "el_hh_enroll_num",
       "el_hh_assets"))
```


## Secondary Outcomes

### PM

#### Family Structure

```{r}
#| label: Summ-Fam-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_marital_status = pm_married), 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_pm_marital_status"))
```

#### Investment

```{r}
#| label: Gen-Inv-Outcomes-PM

# Investments in training cost (CFA) ----
addIndex("pm_el",
         c("pm_lang_train_cost",
           "pm_voc_train_cost"),
         "el_pm_inv_cost")
```

```{r}
#| label: Summ-Inv-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_el, hh_id,
                   el_pm_inv_cost), 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_pm_inv_cost"))
```


### SHM

#### Attitudes and Values

```{r}
#| label: Gen-AttValues-Outcomes-SHM

# Cleaning outcome components ----
shm_el <- shm_el |>
  mutate_at(vars(matches("shm_tol")), ~./10) |>
  mutate_at(vars(shm_marry_daughter_relig, 
                 shm_marry_daughter_eth,
                 shm_marry_son_relig,
                 shm_marry_son_eth), ~1*(. == 1)) |>
  mutate(rev_shm_prob_other_ethnicity = (4-shm_prob_other_ethnicity)/3)

# Tolerance (0-9) ----
addIndex("shm_el",
         c("shm_tol_relig",
           "shm_tol_eth",
           "shm_tol_mig",
           "shm_tol_muslim",
           "rev_shm_prob_other_ethnicity",
           "shm_marry_daughter_eth",
           "shm_marry_daughter_relig", 
           "shm_marry_son_relig",
           "shm_marry_son_eth"),
         "el_shm_tolerance")
```

```{r}
#| label: Summ-AttValues-Outcomes-SHM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(shm_el, hh_id,
                   el_shm_tolerance,
                   c("shm_tol_relig",
                     "shm_tol_eth",
                     "shm_tol_mig",
                     "shm_tol_muslim",
                     "rev_shm_prob_other_ethnicity",
                     "shm_marry_daughter_eth",
                     "shm_marry_daughter_relig", 
                     "shm_marry_son_relig",
                     "shm_marry_son_eth")), 
            by = "hh_id") |>
  rename_at(vars(c("shm_tol_relig",
                     "shm_tol_eth",
                     "shm_tol_mig",
                     "shm_tol_muslim",
                     "rev_shm_prob_other_ethnicity",
                     "shm_marry_daughter_eth",
                     "shm_marry_daughter_relig", 
                     "shm_marry_son_relig",
                     "shm_marry_son_eth")),
            ~paste0("el_shm_", gsub("shm_", "", .)))

# Summarize outcomes generated ----
summ(c("el_shm_tolerance"))

```


#### Manipulation Checks

```{r}
#| label: Gen-ManiCheck-Outcomes-SHM

# Cleaning outcome components ----
shm_el <- shm_el |>
  mutate(shm_time_ecowas_correct = 1*(shm_time_ecowas == 3)) 

# Knowledge of regular migration (0-8) ----
addIndex("shm_el", 
         c("shm_docs_required_civ_3",
           "shm_docs_required_civ_3",
           "shm_time_ecowas_correct",
           "shm_docs_required_libya_2", 
           "shm_docs_required_libya_4", 
           "shm_docs_required_libya_6",
           "shm_vax_req_1", "shm_vax_req_2"), 
         "el_shm_know_mig_reqs")

# Cleaning outcome components ----
shm_el <- shm_el |>
  mutate_at(vars(shm_mig_prep_contact, 
                 shm_mig_prep_savings, 
                 shm_mig_prep_legal),
            ~case_when(. < 0 ~ NA,
                       .default = .))


# Preparation to migrate (0-3) ----
addIndex("shm_el",
         c("shm_mig_prep_contact", 
           "shm_mig_prep_savings", 
           "shm_mig_prep_legal"),
         "el_shm_mig_prep")

```


```{r}
#| label: Summ-ManiCheck-Outcomes-SHM
#| echo: False

# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(shm_el, hh_id,
                   el_shm_know_mig_reqs,
                   el_shm_mig_prep,
                   c("shm_docs_required_civ_3",
               "shm_docs_required_civ_3",
               "shm_time_ecowas_correct",
               "shm_docs_required_libya_2", 
               "shm_docs_required_libya_4", 
               "shm_docs_required_libya_6",
               "shm_vax_req_1", "shm_vax_req_2",
               "shm_mig_prep_contact", 
                "shm_mig_prep_savings", 
                "shm_mig_prep_legal")), 
            by = "hh_id") |>
  rename_at(vars(c("shm_docs_required_civ_3",
               "shm_docs_required_civ_3",
               "shm_time_ecowas_correct",
               "shm_docs_required_libya_2", 
               "shm_docs_required_libya_4", 
               "shm_docs_required_libya_6",
               "shm_vax_req_1", "shm_vax_req_2",
               "shm_mig_prep_contact", 
           "shm_mig_prep_savings", 
           "shm_mig_prep_legal")),
            ~paste0("el_", .))

# Summarize outcomes generated ----
summ(c("el_shm_know_mig_reqs"))
```

### HoH

#### Time-use

```{r}
#| label: Gen-TimeUse-Outcomes-HoH

# Converting roster module to long format ----

# getting names, age and sex from HH roster module
# roster_age <- hoh_el_id |>
#   select(hh_id, matches("hoh_roster_age_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "age",
#                names_pattern = "hoh_roster_age_([0-9]+)$")
# 
# roster_sex <- hoh_el_id |>
#   select(hh_id, matches("hoh_roster_sex_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "sex",
#                names_pattern = "hoh_roster_sex_([0-9]+)$")
# 
# roster_names <- hoh_el_id |>
#   select(hh_id, matches("hoh_roster_name_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "name",
#                names_pattern = "hoh_roster_name_([0-9]+)$")


# Getting paid_ag and names for hoh_hh_paid module ----
# roster_paid_ag_names <- hoh_el_id |>
#   select(hh_id, matches("hoh_paid_name_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "name",
#                names_pattern = "hoh_paid_name_([0-9]+)$") 

# roster_paid_ag <- hoh_el |>
#   select(hh_id, matches("hoh_paid_ag_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "paid_ag",
#                names_pattern = "hoh_paid_ag_([0-9]+)$")

# Getting ag_days_member and names for hoh_hh_labor module ----
# roster_days_member <- hoh_el |>
#   select(hh_id, matches("hoh_ag_days_member_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "ag_days_member",
#                names_pattern = "hoh_ag_days_member_([0-9]+)$") 
# 
# roster_days_member_name <- hoh_el |>
#   select(hh_id, matches("hoh_labor_name_[0-9]+$")) |>
#   pivot_longer(!hh_id, names_to = "index",
#                values_to = "name",
#                names_pattern = "hoh_labor_name_([0-9]+)$") 

# Merging the data to separate dataset for each module ----
# full_roster_paid_ag <- left_join(roster_paid_ag_names, 
#                                  roster_paid_ag, 
#                          by = c("hh_id", "index"))  |>
#   select(-index)

# full_roster_days_member <- left_join(roster_days_member, 
#                                      roster_days_member_name, 
#                                      by = c("hh_id", "index")) |>
#   select(-index)

# Generating a time use dataset by merging across modules ----
# full_roster_timeuse <- full_join(full_roster_paid_ag, 
#                                  full_roster_days_member,
#                                  by = c("hh_id", "name")) |>
#   rowwise() |>
#   mutate(X = sum(paid_ag, ag_days_member, na.rm = T)) |>
#   ungroup() |>
#   filter(name != "")
# 
# # Full roster dataset ----
# full_roster <- left_join(roster_names, roster_age, 
#                          by = c("hh_id", "index")) |>
#   left_join(roster_sex, by = c("hh_id", "index")) |>
#   mutate(dum_child = case_when(is.na(age) ~ NA,
#                                age %in% 7:13 ~ 1, 
#                                .default = 0),
#          dum_elderly = case_when(is.na(age) ~ NA,
#                                age > 59 ~ 1, 
#                                .default = 0),
#          dum_woman = case_when(is.na(age) ~ NA,
#                                age %in% 14:59 & sex == "Female" ~ 1, 
#                                .default = 0))

# Final dataset with outcomes ----
## Cannot merge on index since the time use modules are only enumerated
## for members above 7. Indices are not consistent between those modules
## and the roster module. Using HH ID and names to merge for now
# temp_df <- left_join(full_roster, full_roster_timeuse, 
#                      by = c("hh_id", "name")) |> 
#   mutate(X = ifelse(is.na(X), 0, X),
#          child_timeuse = X*dum_child,
#          elderly_timeuse = X*dum_elderly,
#          woman_timeuse = X*dum_woman) |> 
#   group_by(hh_id) |>
#   summarize(el_hh_childtimeuse = mean(child_timeuse, na.rm = T),
#             el_hh_eldertimeuse = mean(elderly_timeuse, na.rm = T),
#             el_hh_womantimeuse = mean(woman_timeuse, na.rm = T)) |>
#   select(hh_id, matches("el_hh")) |>
#   mutate_at(vars(matches("el_hh")), ~case_when(is.na(.) ~ 0, .default = .))
```

```{r}
#| label: Summ-TimeUse-Outcomes-HoH
#| echo: False

# # Merge in outcomes to workfile ----
# workfile <- workfile |> 
#   left_join(distinct(temp_df, hh_id, .keep_all = T), 
#             by = "hh_id")
# 
# # Summarize outcomes generated ----
# summ(c("el_hh_childtimeuse",
#        "el_hh_eldertimeuse",
#        "el_hh_womantimeuse"))
# 
# rm(temp_df)

```

### Woman



#### Mental Health

```{r}
#| label: Gen-MentHeatlh-Outcomes-W

# Cleaning outcome components ----
w_el <- w_el |>
  mutate(rev_w_self_esteem_4 = (5 - w_self_esteem_4)/4,
         rev_w_self_esteem_9 = (5 - w_self_esteem_9)/4,
         w_emotion1 = (w_emotion1)/3,
         w_emotion2 = (w_emotion2)/3,
         rev_w_emotion3 = (3 - w_emotion3)/3,
         rev_w_emotion4 = (3 - w_emotion4)/3,
         rev_w_emotion5 = (3 - w_emotion5)/3,
         rev_w_emotion6 = (3 - w_emotion6)/3,
         rev_w_emotion7 = (3 - w_emotion7)/3,
         rev_w_home_problems = (4 - w_home_problems)/3,
         rev_w_idleness = (4 - w_idleness)/3,
         rev_w_alcohol_consumption = (4 - w_alcohol_consumption)/3,
         rev_w_family_death = (4 - w_family_death)/3,
         rev_w_money_problems = (4 - w_money_problems)/3,
         rev_w_debt_owed = (4 - w_debt_owed)/3,
         rev_w_cant_find_work = (4 - w_cant_find_work)/3,
         rev_w_cant_educate_children = (4 - w_cant_educate_children)/3,
         rev_w_accidents_disasters = (4 - w_accidents_disasters)/3,
         pm_ladder_scale = w_ladder_scale/10
         ) 

# Emotion (0-9) ----
addIndex("w_el",
         c("rev_w_self_esteem_4",
           "rev_w_self_esteem_9",
           "w_emotion1",
           "w_emotion2",
           "rev_w_emotion3",
           "rev_w_emotion4",
           "rev_w_emotion5",
           "rev_w_emotion6",
           "rev_w_emotion7"),
         "el_w_emotion")

# Stress: Family (0-4) ----
addIndex("w_el",
         c("rev_w_home_problems",
           "rev_w_idleness",
           "rev_w_alcohol_consumption",
           "rev_w_family_death"),
         "el_w_famstress")

# Stress: Economic (0-6) ----
addIndex("w_el",
         c("rev_w_money_problems",
           "rev_w_debt_owed",
           "rev_w_cant_find_work",
           "rev_w_cant_educate_children",
           "rev_w_accidents_disasters",
           "w_ladder_scale"),
         "el_w_econstress")
```

```{r}
#| label: Summ-MentHealth-Outcomes-W
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(w_el, hh_id,
                   el_w_econstress,
                   el_w_famstress,
                   el_w_emotion,
                   c("rev_w_self_esteem_4",
                     "rev_w_self_esteem_9",
                     "w_emotion1",
                     "w_emotion2",
                     "rev_w_emotion3",
                     "rev_w_emotion4",
                     "rev_w_emotion5",
                     "rev_w_emotion6",
                     "rev_w_emotion7",
                     "rev_w_home_problems",
                     "rev_w_idleness",
                     "rev_w_alcohol_consumption",
                     "rev_w_family_death",
                     "rev_w_money_problems",
                     "rev_w_debt_owed",
                     "rev_w_cant_find_work",
                     "rev_w_cant_educate_children",
                     "rev_w_accidents_disasters",
                     "w_ladder_scale")),
            by = "hh_id") |>
  rename_at(vars("rev_w_self_esteem_4",
                 "rev_w_self_esteem_9",
                 "w_emotion1",
                 "w_emotion2",
                 "rev_w_emotion3",
                 "rev_w_emotion4",
                 "rev_w_emotion5",
                 "rev_w_emotion6",
                 "rev_w_emotion7",
                 "rev_w_home_problems",
                 "rev_w_idleness",
                 "rev_w_alcohol_consumption",
                 "rev_w_family_death",
                 "rev_w_money_problems",
                 "rev_w_debt_owed",
                 "rev_w_cant_find_work",
                 "rev_w_cant_educate_children",
                 "rev_w_accidents_disasters",
                 "w_ladder_scale"), 
            ~paste0("el_w_", gsub("w_", "", .)))

# Summarize outcomes generated ----
summ(c("el_w_emotion",
       "el_w_famstress",
       "el_w_econstress"))
```


#### Joint Decision-making

```{r}
#| label: Gen-JointDecMake-Outcomes-W

# w_el <- read.csv(here("data/out/fu5/Follow-up Round 5 Woman De-ID.csv")) |>
#   filter(resp_available == 1) |>
#   distinct(hh_id, .keep_all = T)
# 
# workfile <- read.csv(here("data/out/fu5/workfile-final.csv"))
# 
# workfile <- workfile |>
#   select(-c("el_w_domabuse",
#             "el_w_trust_spouse",
#             "el_w_save_acc",
#             "el_w_savings_amt",
#            "el_w_humiliate",
#            "el_w_threaten",
#            "el_w_push_shake",
#            "el_w_slap_twist",
#            "el_w_punch",
#            "el_w_kick",
#            "el_w_strangle_burn",
#            "el_w_threaten_weapon",
#            "el_w_attack_weapon",
#            "el_w_sexual_assault",
#            "el_w_prevent_work",
#            "el_w_prevent_visit",
#            "el_w_accuse_unfaithful",
#            "el_w_not_permit_friends",
#            "el_w_limit_fam_contact",
#            "el_w_jointdec",
#            "el_w_daily_hh_expenses_couple",
#            "el_w_hh_purchases_couple",
#            "el_w_fam_plan_couple",
#            "el_w_migrate_couple",
#            "el_w_vote_couple",
#            "el_w_school_couple",
#            "el_w_discuss_women",
#            "el_w_consult_nonmig",
#            "el_w_discuss_work", 
#            "el_w_discuss_community", 
#            "el_w_discuss_election",  
#            "el_w_discuss_invest",
#            "el_w_affection",
#            "el_w_affectionate",
#            "el_w_respectful",
#            "el_w_gender_attitudes",
#            "el_w_neglects_children",
#        "el_w_argues",
#        "el_w_refuses_pray",
#        "el_w_burns_food",
#        "el_w_male_education_priority",
#        "el_w_equal_rights_inheritance",
#        "el_w_woman_reject_marriage",
#        "el_w_equal_rights_divorce",
#        "el_w_polygamy"))

# Cleaning outcome components ----
w_el <- read.csv(here("data/out/el/Endline Woman De-ID.csv")) |>
  filter(resp_available == 1) |>
  distinct(hh_id, .keep_all = T)
w_el <- w_el |>
  mutate_at(vars(w_accuse_unfaithful,
                 w_not_permit_friends,
                 w_limit_fam_contact),
            ~case_when(. < 0 ~ NA,
                       .default = .)) |>
  mutate_at(vars(w_daily_hh_expenses_couple,
                 w_hh_purchases_couple,
                 w_fam_plan_couple,
                 w_migrate_couple,
                 w_vote_couple,
                 w_school_couple,
                 w_male_education_priority), ~(5-.)/4) |>
  mutate_at(vars(w_equal_rights_inheritance, 
                 w_woman_reject_marriage,
                 w_equal_rights_divorce, 
                 w_polygamy), ~(.-1)/4) |>
  mutate_at(vars(w_discuss_work, 
                 w_discuss_community, 
                 w_discuss_election, 
                 w_discuss_invest,
                 w_discuss_women,
                 w_affectionate,
                 w_respectful),
            ~./3) |>
  mutate_at(vars(w_daily_hh_expenses_couple,
                 w_hh_purchases_couple,
                 w_fam_plan_couple,
                 w_migrate_couple,
                 w_vote_couple,
                 w_school_couple,
                 w_discuss_women,
                 w_prevent_work,
                 w_prevent_visit),
            ~ifelse(w_married == 0, NA, .)) |>
  mutate_at(vars(w_neglects_children,
                 w_argues,
                 w_refuses_pray,
                 w_burns_food),
            ~ 1-.) |>
  mutate(w_allowance_freedom = ifelse(w_allowance_freedom < 0, NA, w_allowance_freedom)) |>
  rename("el_w_allowance_husband" = "w_allowance_husband",
         "el_w_allowance_freedom" = "w_allowance_freedom")

# Domestic Abuse (0-10) ----
addIndex("w_el",
         c("w_humiliate",
           "w_threaten",
           "w_push_shake",
           "w_slap_twist",
           "w_punch",
           "w_kick",
           "w_strangle_burn",
           "w_threaten_weapon",
           "w_attack_weapon",
           "w_sexual_assault"),
         "el_w_domabuse")

# Trust between Spouses (0-5) ---- 
## Last three components only asked to married women. Outcome
## generated for married women only
addIndex("w_el",
         c("w_prevent_work",
           "w_prevent_visit",
           "w_accuse_unfaithful",
           "w_not_permit_friends",
           "w_limit_fam_contact"),
         "el_w_trust_spouse")

# Create index with 
# w_neglects_children
# w_argues
# w_refuses_pray
# w_burns_food

# Consults with spouse (0-7) ----
addIndex("w_el",
         c("w_daily_hh_expenses_couple",
           "w_hh_purchases_couple",
           "w_fam_plan_couple",
           "w_migrate_couple",
           "w_vote_couple",
           "w_school_couple",
           "w_discuss_women"),
         "el_w_jointdec")

# Consults with family on issues other than migration (0-4) ----
addIndex("w_el",
         c("w_discuss_work", 
           "w_discuss_community", 
           "w_discuss_election", 
           "w_discuss_invest"),
         "el_w_consult_nonmig")


# Affectionate/Respectful (0-2) ----
addIndex("w_el",
         c("w_affectionate",
           "w_respectful"),
         "el_w_affection")

# IPV attitudes (0-4) ----
addIndex("w_el",
         c("w_neglects_children",
           "w_argues",
           "w_refuses_pray",
           "w_burns_food"),
         "el_w_attitudes_ipv")

# Attitudes around gender equaltiy (0-5) ----
addIndex("w_el",
         c("w_male_education_priority",
           "w_equal_rights_inheritance",
           "w_woman_reject_marriage",
           "w_equal_rights_divorce",
           "w_polygamy"),
         "el_w_gender_eq")


w_el <- w_el |>
  mutate(el_w_trust_spouse = ifelse(w_married == 1, el_w_trust_spouse, 
                                     NA),
         el_w_domabuse = ifelse(w_married == 0, NA, 
                                     el_w_domabuse),
         el_w_jointdec = ifelse((!is.na(w_daily_hh_expenses_couple) | 
                                  !is.na(w_hh_purchases_couple) | 
                                  !is.na(w_fam_plan_couple) | 
                                  !is.na(w_migrate_couple) | 
                                  !is.na(w_vote_couple) |
                                  !is.na(w_school_couple) | 
                                  !is.na(w_discuss_women)) & 
                                       w_married == 1, el_w_jointdec, NA),
         el_w_affection = ifelse((!is.na(w_affectionate) | 
                                  !is.na(w_respectful)) & 
                                       w_married == 1, el_w_affection, NA),
         el_w_consult_nonmig = ifelse(w_married == 1, el_w_consult_nonmig, NA))


# Savings account ----
w_el <- w_el |>
  mutate(el_w_save_acc = 1*(w_separate_savings != 0))

# Savings ----
addIndex("w_el", 
         getVarnames(w_el, "savings_type_amt"),
         "el_w_savings_amt")

```

```{r}
#| label: Summ-JointDecMake-Outcomes-W
#| echo: False

# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(w_el, hh_id,
                   el_w_domabuse,
                   el_w_humiliate = w_humiliate,
                   el_w_threaten = w_threaten,
                   el_w_push_shake = w_push_shake,
                   el_w_slap_twist = w_slap_twist,
                   el_w_punch = w_punch,
                   el_w_kick = w_kick,
                   el_w_strangle_burn = w_strangle_burn,
                   el_w_threaten_weapon = w_threaten_weapon,
                   el_w_attack_weapon = w_attack_weapon,
                   el_w_sexual_assault = w_sexual_assault,
                   el_w_trust_spouse,
                   el_w_prevent_work = w_prevent_work,
                   el_w_prevent_visit = w_prevent_visit,
                   el_w_accuse_unfaithful = w_accuse_unfaithful,
                   el_w_not_permit_friends = w_not_permit_friends,
                   el_w_limit_fam_contact = w_limit_fam_contact,
                   el_w_save_acc,
                   el_w_savings_amt,
                   el_w_jointdec,
                   el_w_daily_hh_expenses_couple = w_daily_hh_expenses_couple,
                   el_w_hh_purchases_couple = w_hh_purchases_couple,
                   el_w_fam_plan_couple = w_fam_plan_couple,
                   el_w_migrate_couple = w_migrate_couple,
                   el_w_vote_couple = w_vote_couple,
                   el_w_school_couple = w_school_couple,
                   el_w_discuss_women = w_discuss_women,
                   el_w_consult_nonmig,
                   el_w_discuss_work = w_discuss_work, 
                   el_w_discuss_community = w_discuss_community, 
                   el_w_discuss_election = w_discuss_election,  
                   el_w_discuss_invest = w_discuss_invest,
                   el_w_affection,
                   el_w_affectionate = w_affectionate,
                   el_w_respectful = w_respectful,
                   el_w_attitudes_ipv,
                   el_w_neglects_children = w_neglects_children,
                   el_w_argues = w_argues,
                   el_w_refuses_pray = w_refuses_pray,
                   el_w_burns_food = w_burns_food,
                   el_w_gender_eq,
                   el_w_male_education_priority = w_male_education_priority,
                   el_w_equal_rights_inheritance = w_equal_rights_inheritance,
                   el_w_woman_reject_marriage = w_woman_reject_marriage,
                   el_w_equal_rights_divorce = w_equal_rights_divorce,
                   el_w_polygamy = w_polygamy,
                   el_w_allowance_husband,
                   el_w_allowance_freedom), 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("el_w_domabuse",
       "el_w_trust_spouse",
       "el_w_jointdec",
       "el_w_consult_nonmig",
       "el_w_affection",
       "el_w_save_acc",
       "el_w_savings_amt",
       "el_w_gender_eq",
       "el_w_attitudes_ipv"))
```

# Saving Final Workfile

```{r}

workfile |>
  write.csv(here("data/out/el/workfile-final.csv"),
            na = '',
            row.names = F) 

            
```
