---
title: "Outcomes - FU4"
author: "Sirig Gurung"
date: today
fontsize: 10pt
mainfont: Fira Sans
fontfamily: Fira Sans
monofont: Fira Code
code-line-numbers: true
df-print: kable
highlight-style: tango
number-sections: true
toc: false
lot: false
echo: true
warning: false
header-includes:
  - \usepackage{float}
  - \floatplacement{table}{H}
  - \floatplacement{figure}{H}
format: 
  pdf:
    fig-pos: 'H'
    tbl-pos: 'H'
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| results: hide

rm(list = ls())

pkgs <- c("tidyverse", "modelsummary", "here")

sapply(pkgs, require, character.only = TRUE)
rm(pkgs)

options(knitr.kable.NA = 0)
options(modelsummary_format_numeric_latex = "plain")
```

```{r}
#| label: Loading-deID-Data-DB
#| echo: false


box_directory <- "/Users/siriggurung/Box Sync/PPM/rctfollowups_sep2023"


# Workfile -----
bl_workfile <- read.csv(here("data/out/bl/workfile-final.csv"))
pm_workfile_fu3 <- read.csv(here("data/out/fu3/workfile-final.csv"))

# Treatment DF ----
treat_df <-  bl_workfile |>
  select(hh_id, S, Z)

# PM ----
pm_fu4 <- read.csv(here("data/out/fu4/Follow-up Round 4 Prospective Migrant De-ID.csv")) |>
  filter(!is.na(pm_home)) |>
  distinct(hh_id, .keep_all = T)
# SHM ----
shm_fu4 <- read.csv(here("data/out/fu4/Follow-up Round 4 Secondary HH Member De-ID.csv")) |>
  filter(!is.na(shm_home)) |>
  distinct(hh_id, .keep_all = T)
# HoH ----
hoh_bl <- readRDS(paste0("/Users/siriggurung/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data", "/hoh/hoh_parent.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id) |>
  distinct(hh_id, .keep_all = T) |>
  left_join(treat_df, by = "hh_id")
hoh_livestock_bl <- readRDS(paste0("/Users/siriggurung/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data", "/hoh/hh_resource_livestock.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id)
hoh_livestockact_bl <- readRDS(paste0("/Users/siriggurung/Box Sync/PPM/rctbaseline_may2023/inprog_sirig/data", "/hoh/hh_resource_livestockact.rds")) |>
  filter(hh_id %in% pm_workfile_fu3$hh_id)

hoh_fu4 <- read.csv(paste0(box_directory, "/data/R4/out/Follow-up Round 4 Household Head.csv")) |>
  filter(!is.na(hoh_new_hh_mems)) |>
  distinct(hh_id, .keep_all = T)

```

```{r}
#| label: Create-Outcomes-Dataset

workfile <- bl_workfile |>
  mutate(S_Z = str_to_upper(str_c(S, "-", Z)),
         fu4_pm_comp = 1*(hh_id %in% pm_fu4$hh_id),
         fu4_shm_comp = 1*(hh_id %in% shm_fu4$hh_id),
         fu4_hoh_comp = 1*(hh_id %in% hoh_fu4$hh_id)) |>
  select(hh_id, loc_id, com_id, S, Z, S_Z, ipw_s, ipw_z, 
         fu4_pm_comp, fu4_shm_comp, fu4_hoh_comp,
         matches("^bl_")) |>
  arrange(hh_id)

workfile$S_Z <- factor(workfile$S_Z, 
                       levels = c("MC-PPM", "MC-UCT", "MC-C", "PC-C"))
```

# Functions to generate outcomes

## Additive indices

```{r}
#| label: Define-Additive-Index-Function
addIndex <- function(df_name, x, outcome_name, na = T) {
  # df_name: Dataset (string)
  # x: vector of variable names to sum over (string)
  # outcome_name: Name of outcome being generated  (string)
  # na: Include NAs or not? Feeds into the na.rm argument (boolean)
  df <- get(df_name) |>
    rowwise() |>
    mutate(!!outcome_name := 
             sum(c_across(all_of(x)), na.rm = T)) |>
    ungroup()
  assign(df_name, df, envir = .GlobalEnv)
}
```

## Summarize outcomes

```{r}
#| label: Summarize-Outcomes

summ <- function(x) {
  sub <- workfile |>
  select(S_Z, all_of(x))

datasummary(All(sub) ~ 
              S_Z * (N + Mean), 
            data = sub,
            output = "kableExtra") |> 
  kableExtra::kable_styling(font_size = 8)
}
```

## Check levels of variable 

```{r}
#| label: check-levels-of-var
checkLevels <- function(df, x) {
  df |>
    group_by(get(x)) |>
    summarize(n())
}
```

## Get Varnames from regex 

```{r}
#| label: get-varnames

getVarnames <- function(df, x) {
  colnames(select(df, matches(x)))
}

```

## Trim variables

```{r}
#| label: func-trim-variables
## Function to trim variables

trim <- function(df, var) {
  temp <- df |>
    mutate(!! paste0(var, "_tr") := ifelse(get(var) == 0, NA, get(var)))
  temp_tr <- temp
  
  u <- quantile(temp_tr[[paste0(var, "_tr")]], 0.95, na.rm = T) 
  l <- quantile(temp_tr[[paste0(var, "_tr")]], 0.05, na.rm = T) 
  
  temp <- temp |>
    mutate(!! paste0(var, "_tr") := case_when(get(var) > u & 
                                                get(var) != 0 ~ u,
                                              get(var) < l & 
                                                get(var) != 0 ~ l,
                                              .default = get(var)))
  return(temp)
}
```

# Generate outcomes

## Primary Outcomes

### PM


#### Migration

```{r}
#| label: Gen-Mig-Outcomes-PM

# Cleaning outcome components ----
pm_fu4 <- pm_fu4 |>
  mutate_at(vars(pm_mig_prep_contact, 
                 pm_mig_prep_savings, 
                 pm_mig_prep_legal),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Intention to Migrate (0-1) ----
pm_fu4 <- pm_fu4 |>
  mutate(fu4_pm_mig_intent = 1*(pm_mig_intent == 1 | pm_mig_intent_1 == 1))

# Preparation to migrate (0-3) ----
addIndex("pm_fu4",
         c("pm_mig_prep_contact", 
           "pm_mig_prep_savings", 
           "pm_mig_prep_legal"),
         "fu4_pm_mig_prep")

# Migration outcomes ----

pm_fu4 <- pm_fu4 |>
  mutate(pm_countries_new = case_when(grepl("^,", pm_countries_new) ~ 
                                        paste0("1", pm_countries_new),
                                      .default = pm_countries_new),
         pm_border_cross_ecowas = 1*(str_count(pm_countries_new, 
                                               "\\b(?:3|6|7|9|10|13|14|15|16|17|18|19)\\b") > 0),
         pm_border_cross = 1*(str_count(pm_countries_new, 
                                        "\\b(?!1\\b)\\d+\\b") > 0),
         pm_dom_mig = case_when(pm_current_in_niger == 1 | pm_past_in_niger == 1 |
                                  pm_previous_in_niger_1 == 1 | pm_previous_in_niger_2 == 1 |
                                  pm_previous_in_niger_3 == 1 ~ 1,
                                .default = 0),
         pm_border_cross_nonec = 1*(str_count(pm_countries_new,
                                              "\\b(?:2|4|5|8|11|12|20|21)\\b") > 0)) |>
  rowwise() |>
  mutate(pm_mig_any = pmax(pm_dom_mig, pm_border_cross,
                           pm_border_cross_ecowas, na.rm = T)) |>
  ungroup()

temp_df <- pm_fu4 |>
  right_join(select(pm_workfile_fu3, hh_id, fu3_pm_mig_any,
                   fu3_pm_dom_mig, fu3_pm_border_cross, 
                   fu3_pm_border_cross_ecowas, 
                   fu3_pm_border_cross_nonec), by = "hh_id") |>
  rowwise() |>
  mutate(fu4_pm_mig_any = case_when(is.na(pm_mig_any) & is.na(fu3_pm_mig_any) ~ NA,
                                .default = pmax(pm_mig_any, fu3_pm_mig_any, na.rm = T)),
         fu4_pm_dom_mig = case_when(is.na(pm_dom_mig) & is.na(fu3_pm_dom_mig) ~ NA,
                                .default = pmax(pm_dom_mig, fu3_pm_dom_mig, na.rm = T)),
         fu4_pm_border_cross = case_when(is.na(pm_border_cross) & 
                                           is.na(fu3_pm_border_cross) ~ NA,
                                .default = pmax(pm_border_cross, 
                                                fu3_pm_border_cross, na.rm = T)),
         fu4_pm_border_cross_ecowas = case_when(is.na(pm_border_cross_ecowas) &
                                                  is.na(fu3_pm_border_cross_ecowas) ~ NA,
                                .default = pmax(pm_border_cross_ecowas, 
                                                fu3_pm_border_cross_ecowas, na.rm = T)),
         fu4_pm_border_cross_nonec = case_when(is.na(pm_border_cross_nonec) &
                                                  is.na(fu3_pm_border_cross_nonec) ~ NA,
                                .default = pmax(pm_border_cross_nonec, 
                                                fu3_pm_border_cross_nonec, na.rm = T))) |>
  ungroup() |>
  select(hh_id, fu4_pm_mig_any, fu4_pm_dom_mig, 
         fu4_pm_border_cross, fu4_pm_border_cross_ecowas, 
         fu4_pm_border_cross_nonec)


# Counts and weeks from FU4 ----
ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)

return_country <- function(index, text) {
  items <- str_split(text, ",")[[1]]
  if (index > 0 & index <= length(items)) {
    return(items[index])
  } else {
    return(NA)
  }
}
  
  
mig_df <- pm_fu4 |>
  select(hh_id, pm_locations_list, pm_countries,
         matches("pm_location_is_home_[0-9]|pm_location_act_index_[0-9]|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]")) |>
  pivot_longer(
    cols = matches("pm_location_is_home_[0-9]|pm_location_act_index_[0-9]|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)")|>
  filter(pm_location_period_lab == "from our most recent survey in person to now")
  

tot_loc_weeks <- mig_df |>
  group_by(hh_id) |>
  summarize(fu4_pm_total_weeks = sum(pm_location_weeks, na.rm = T))

mig_df$country <- map(1:nrow(mig_df),
    function(x){
      index <- mig_df$pm_location_act_index[x]
      country_list <- mig_df$pm_countries[x]
      as.numeric(return_country(index, country_list))
    }) |>
  unlist()

mig_df <- mig_df |>
  filter(pm_location_is_home == 0) |>
  mutate(country = ifelse(is.na(country), 1, country),
         dum = 1,
         ecowas = 1*(country %in% ecowas_codes),
         nonecowas = 1*(country %in% noecowas_codes),
         dom = 1*(country == 1),
         ecowas_weeks = ifelse(ecowas == 1, pm_location_weeks, 0),
         nonecowas_weeks = ifelse(nonecowas == 1, pm_location_weeks, 0),
         dom_weeks = ifelse(dom == 1, pm_location_weeks, 0)) |>
  group_by(hh_id) |>
  summarize(fu4_pm_mig_any_num = sum(dum, na.rm = T),
            fu4_pm_mig_any_weeks = sum(pm_location_weeks, na.rm = T),
            fu4_pm_dom_mig_num = sum(dom, na.rm = T),
            fu4_pm_dom_mig_weeks = sum(dom_weeks, na.rm = T),
            fu4_pm_border_cross_ecowas_num = sum(ecowas, na.rm = T),
            fu4_pm_border_cross_ecowas_weeks = sum(ecowas_weeks, na.rm = T),
            fu4_pm_border_cross_nonec_num = sum(nonecowas, na.rm = T),
            fu4_pm_border_cross_nonec_weeks = sum(nonecowas_weeks, na.rm = T))
  
mig_df <- mig_df |>
  right_join(select(pm_fu4, hh_id), by = "hh_id") |>
  mutate_at(vars(hh_id,
                 fu4_pm_mig_any_num, 
                 fu4_pm_dom_mig_num,
                 fu4_pm_border_cross_ecowas_num,
                 fu4_pm_border_cross_nonec_num,
                 fu4_pm_mig_any_weeks,
                 fu4_pm_dom_mig_weeks,
                 fu4_pm_border_cross_ecowas_weeks,
                 fu4_pm_border_cross_nonec_weeks),
            ~ifelse(is.na(.), 0, .)) 

## Adding up weeks and episodes to get cumulative measure ----
mig_df <- mig_df |>
  right_join(select(pm_workfile_fu3,
                    hh_id,
                    fu3_pm_mig_any_num, 
                    fu3_pm_dom_mig_num,
                    fu3_pm_border_cross_ecowas_num,
                    fu3_pm_border_cross_nonec_num,
                    fu3_pm_mig_any_weeks,
                    fu3_pm_dom_mig_weeks,
                    fu3_pm_border_cross_ecowas_weeks,
                    fu3_pm_border_cross_nonec_weeks,
                    fu3_pm_total_weeks), by = "hh_id") |>
  left_join(tot_loc_weeks, by = "hh_id") |>
  rowwise() |>
  mutate(fu4_pm_mig_any_num = sum(fu3_pm_mig_any_num, fu4_pm_mig_any_num, na.rm = T),
         fu4_pm_mig_any_weeks = sum(fu3_pm_mig_any_weeks, fu4_pm_mig_any_weeks, na.rm = T),
         fu4_pm_dom_mig_num = sum(fu3_pm_dom_mig_num, fu4_pm_dom_mig_num, na.rm = T),
         fu4_pm_dom_mig_weeks = sum(fu3_pm_dom_mig_weeks, fu4_pm_dom_mig_weeks, na.rm = T),
         fu4_pm_border_cross_ecowas_num = sum(fu3_pm_border_cross_ecowas_num, 
                                              fu4_pm_border_cross_ecowas_num, na.rm = T),
         fu4_pm_border_cross_ecowas_weeks = sum(fu3_pm_border_cross_ecowas_weeks, 
                                                fu4_pm_border_cross_ecowas_weeks, na.rm = T),
         fu4_pm_border_cross_nonec_num = sum(fu3_pm_border_cross_nonec_num, 
                                             fu4_pm_border_cross_nonec_num, na.rm = T),
         fu4_pm_border_cross_nonec_weeks = sum(fu3_pm_border_cross_nonec_weeks,
                                               fu4_pm_border_cross_nonec_weeks, na.rm = T),
         fu4_pm_total_weeks = sum(fu3_pm_total_weeks,
                                  fu4_pm_total_weeks, na.rm = T)) |>
  ungroup() |>
  mutate_at(vars(matches("fu4_")),
            ~ifelse(hh_id %in% pm_fu4$hh_id | !is.na(fu3_pm_mig_any_num), ., NA)) |>
  select(hh_id,
         fu4_pm_mig_any_num, 
         fu4_pm_dom_mig_num,
         fu4_pm_border_cross_ecowas_num,
         fu4_pm_border_cross_nonec_num,
         fu4_pm_mig_any_weeks,
         fu4_pm_dom_mig_weeks,
         fu4_pm_border_cross_ecowas_weeks,
         fu4_pm_border_cross_nonec_weeks,
         fu4_pm_total_weeks)


```


```{r}
#| label: Summ-Mig-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_mig_prep,
                   fu4_pm_mig_intent,
         c("pm_mig_prep_contact", 
           "pm_mig_prep_savings", 
           "pm_mig_prep_legal")), 
            by = "hh_id") |>
  left_join(mig_df, by = "hh_id") |>
  rename_at(vars(c("pm_mig_prep_contact", 
                   "pm_mig_prep_savings", 
                   "pm_mig_prep_legal")),
            ~paste0("fu4_", .)) |>
  left_join(temp_df, by = "hh_id")

# Summarize outcomes generated ----
summ(c("fu4_pm_mig_intent", 
       "fu4_pm_mig_prep",
       "fu4_pm_mig_any", 
       "fu4_pm_dom_mig", 
       "fu4_pm_border_cross", 
       "fu4_pm_border_cross_ecowas", 
       "fu4_pm_border_cross_nonec",
       "fu4_pm_mig_any_num", 
       "fu4_pm_dom_mig_num",
       "fu4_pm_border_cross_ecowas_num",
       "fu4_pm_border_cross_nonec_num",
       "fu4_pm_mig_any_weeks",
       "fu4_pm_dom_mig_weeks",
       "fu4_pm_border_cross_ecowas_weeks",
       "fu4_pm_border_cross_nonec_weeks",
       "fu4_pm_total_weeks"))

```


#### Migrated or intends to migrate

```{r}
#| label: Gen-Intend-Mig-Outcomes-PM

# Cleaning outcome components ----
pm_fu4 <- pm_fu4 |>
  mutate_at(vars(fu4_pm_mig_intent),
            ~case_when(. < 0 ~ NA,
                       .default = .))

# Migration and intent ----
pm_fu4_temp <- pm_fu4 |>
  mutate(pm_intent_dom_mig = case_when(1*(str_count(pm_mig_intent_country, 
                                               "\\b(?:1)\\b")) > 0 ~ 1,
                                          .default = 0),
         pm_intent_border_cross_ecowas = case_when(1*(str_count(pm_mig_intent_country, 
                                               "\\b(3|6|7|9|10|13|14|15|16|17|18|19)\\b")) 
                                     > 0 ~ 1,
                                          .default = 0),
         pm_intent_border_cross = case_when(pm_mig_intent_country == "0" |
                                                     pm_mig_intent_country == "" ~ 0,
                                                   1*(str_count(pm_mig_intent_country, 
                                                                "\\b(?!1\\b)\\d+\\b")) > 0 ~ 1,
                                                   .default = 0),
         pm_intent_mig_any = 1*(pm_intent_dom_mig == 1 | 
                                      pm_intent_border_cross == 1 |
                                      pm_intent_border_cross_ecowas == 1)) |>
  right_join(select(pm_workfile_fu3, 
                    matches("fu3_pm_intent_"), 
                    hh_id), 
             by = "hh_id") |>
  mutate(fu4_pm_intent_mig_any = case_when(is.na(pm_intent_mig_any) & 
                                             is.na(fu3_pm_intent_mig_any) ~ NA,
                                .default = pmax(pm_intent_mig_any, 
                                                fu3_pm_intent_mig_any, 
                                                na.rm = T)),
         fu4_pm_intent_dom_mig = case_when(is.na(pm_intent_dom_mig) & 
                                             is.na(fu3_pm_intent_dom_mig) ~ NA,
                                .default = pmax(pm_intent_dom_mig, 
                                                fu3_pm_intent_dom_mig, 
                                                na.rm = T)),
         fu4_pm_intent_border_cross = case_when(is.na(pm_intent_border_cross) & 
                                           is.na(fu3_pm_intent_border_cross) ~ NA,
                                .default = pmax(pm_intent_border_cross, 
                                                fu3_pm_intent_border_cross, 
                                                na.rm = T)),
         fu4_pm_intent_border_cross_ecowas = case_when(is.na(pm_intent_border_cross_ecowas) &
                                                  is.na(fu3_pm_intent_border_cross_ecowas) ~ NA,
                                .default = pmax(pm_intent_border_cross_ecowas, 
                                                fu3_pm_intent_border_cross_ecowas, 
                                                na.rm = T)))  |>
  select(hh_id, fu4_pm_intent_mig_any, 
         fu4_pm_intent_border_cross,
         fu4_pm_intent_border_cross_ecowas, 
         fu4_pm_intent_dom_mig)

```


```{r}
#| label: Summ-intend-Mig-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4_temp, hh_id,
                   fu4_pm_intent_dom_mig,
                   fu4_pm_intent_border_cross,
                   fu4_pm_intent_border_cross_ecowas,
                   fu4_pm_intent_mig_any),
            by = "hh_id")

# Summarize outcomes generated ----
summ(c("fu4_pm_intent_dom_mig",
       "fu4_pm_intent_border_cross",
       "fu4_pm_intent_border_cross_ecowas",
       "fu4_pm_intent_mig_any"))
rm(pm_fu4_temp)
```

#### Economic Well-Being

```{r}
#| label: Gen-Econ-Outcomes-PM

# Cleaning outcome components ----
temp_loc_costs_df <- pm_fu4 |>
  select(hh_id, matches("pm_food_cost_[0-9]+|pm_housing_cost_[0-9]+|pm_phone_cost_[0-9]+|pm_leisure_cost_[0-9]+|pm_transportation_cost_[0-9]+|pm_calc_total_income_[0-9]+|pm_calc_other_income_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_food_cost_[0-9]+|pm_housing_cost_[0-9]+|pm_phone_cost_[0-9]+|pm_leisure_cost_[0-9]+|pm_transportation_cost_[0-9]+|pm_calc_total_income_[0-9]+|pm_calc_other_income_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "from our most recent survey in person to now") |>
  group_by(hh_id) |>
  summarize(fu4_pm_food_cost = sum(pm_food_cost, na.rm = T),
            fu4_pm_housing_cost = sum(pm_housing_cost, na.rm = T),
            fu4_pm_phone_cost = sum(pm_phone_cost, na.rm = T),
            fu4_pm_leisure_cost = sum(pm_leisure_cost, na.rm = T),
            fu4_pm_transportation_cost = sum(pm_transportation_cost, na.rm = T),
            fu4_pm_calc_total_income = sum(pm_calc_total_income, na.rm = T),
            fu4_pm_calc_other_income = sum(pm_calc_other_income, na.rm = T),
            tot_loc_weeks = sum(pm_location_weeks, na.rm = T))
  
pm_fu4 <- pm_fu4 |>
  mutate(pm_total_loan_value = -pm_total_loan_value) |>
  mutate(pm_eat_protein = 7 - pm_eat_protein,
         pm_skip_meals_num = case_when(pm_skip_meals == 0 ~ 0,
                                       .default = pm_skip_meals_num),
         pm_emergency = 1*(pm_emerg_sell == 1 | pm_emerg_borrow == 1 | pm_emerg_spend == 1),
         pm_emergency_capital = (5-pm_emergency_capital)/4) |>
  left_join(temp_loc_costs_df, by = "hh_id")


rm(temp_loc_costs_df)

# Income (CFA) ----
addIndex("pm_fu4",
         c("fu4_pm_calc_total_income",
           "fu4_pm_calc_other_income"),
         "fu4_pm_inc")

pm_fu4 <- pm_fu4 |>
  mutate(fu4_pm_inc = fu4_pm_inc/tot_loc_weeks)

# Savings (CFA) ----

pm_fu4 <- pm_fu4 |>
  rowwise() |>
  mutate(fu4_pm_savings = sum(c_across(matches("^pm_savings_type_amt_[0-9]+$")), na.rm = T)) |>
  ungroup()


addIndex("pm_fu4",
         c("fu4_pm_savings",
           "pm_total_loan_value"),
         "fu4_pm_net_savings")


pm_fu4 <- pm_fu4 |>
  mutate(fu4_pm_savings = ifelse(pm_separate_savings == 0, 0, fu4_pm_savings),
         fu4_pm_total_loan_value = -pm_total_loan_value)

# Consumption ----

addIndex("pm_fu4",
         c("fu4_pm_food_cost", "fu4_pm_housing_cost",
           "fu4_pm_leisure_cost", "fu4_pm_phone_cost",
           "fu4_pm_transportation_cost"),
         "fu4_pm_cons")

pm_fu4 <- pm_fu4 |>
  mutate(num_locations = str_count(pm_locations_list, ",") + 1,
         fu4_pm_cons = fu4_pm_cons/num_locations)


# Food Insecurity (0-14)----
addIndex("pm_fu4",
         c("pm_skip_meals_num",
           "pm_eat_protein"),
         "fu4_pm_foodsec")

## Reversing so it is food security
pm_fu4 <- pm_fu4 |>
  mutate(fu4_pm_foodsec = 14 - fu4_pm_foodsec)

# Economic Precarity ----
## pm_emergency is a select multiple. Converting to indicator
## for PM faced emergency
addIndex("pm_fu4",
         c("pm_emergency_capital",
           "pm_emergency"),
         "fu4_pm_econprecar")


# Income shared 
temp_loc_share_df <- pm_fu4 |> 
  select(hh_id, matches("pm_location_is_home_[0-9]|pm_share_income_[0-9]+|pm_share_income_amt_[0-9]+|pm_rec_income_[0-9]+|pm_rec_income_amt_[0-9]+|pm_location_weeks_[0-9]|pm_location_period_lab_[0-9]")) |>
  pivot_longer(
    cols = matches("pm_location_is_home_[0-9]|pm_share_income_[0-9]+|pm_share_income_amt_[0-9]+|pm_rec_income_[0-9]+|pm_rec_income_amt_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "from our most recent survey in person to now") |>
  mutate(pm_share_income_amt = case_when(pm_share_income == 0 ~ 0,
                                          .default = pm_share_income_amt),
         pm_share_income_amt = pm_share_income_amt/pm_location_weeks) |>
  group_by(hh_id) |>
  summarize(fu4_pm_share_income = mean(pm_share_income_amt, na.rm = T),
            tot_locs_weeks = sum(pm_location_weeks, na.rm = T)) |>
  mutate(fu4_pm_share_income = ifelse(is.na(fu4_pm_share_income), 0, fu4_pm_share_income))


pm_fu4 <- pm_fu4 |>
  left_join(temp_loc_share_df, by = "hh_id")
```

```{r}
#| label: Summ-Econ-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----

workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_inc,
                   fu4_pm_net_savings,
                   fu4_pm_savings,
                   fu4_pm_total_loan_value,
                   fu4_pm_cons,
                   fu4_pm_foodsec,
                   fu4_pm_econprecar,
                   fu4_pm_phone_cost, 
                   fu4_pm_leisure_cost,
                   fu4_pm_transportation_cost,
                   fu4_pm_food_cost,
                   fu4_pm_housing_cost,
                   fu4_pm_share_income), 
            by = "hh_id")

# Summarize outcomes generated ----
summ(c("fu4_pm_inc",
       "fu4_pm_net_savings",
       "fu4_pm_savings",
       "fu4_pm_total_loan_value",
       "fu4_pm_cons",
       "fu4_pm_foodsec",
       "fu4_pm_econprecar",
       "fu4_pm_share_income"))

```


#### Physical Health and Saftey

```{r}
#| label: Gen-HealthSafety-Outcomes-PM


## All components are at the location level, taking max
## Could take sum but PMs travel to diff num. locations
temp_loc_harras_df <- pm_fu4 |>
  select(hh_id, matches("pm_felt_unsafe_[0-9]+|pm_phys_attacked_[0-9]+|pm_theft_[0-9]+|pm_disc_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_felt_unsafe_[0-9]+|pm_phys_attacked_[0-9]+|pm_theft_[0-9]+|pm_disc_[0-9]+|pm_location_period_lab_[0-9]+|pm_location_weeks_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "from our most recent survey in person to now") |>
  group_by(hh_id) |>
  summarize(pm_felt_unsafe = max(pm_felt_unsafe, na.rm = T),
            pm_phys_attacked = max(pm_phys_attacked, na.rm = T),
            pm_theft = max(pm_theft, na.rm = T),
            pm_disc = max(pm_disc, na.rm = T)) |>
  mutate(across(c(pm_felt_unsafe, pm_phys_attacked, pm_theft, pm_disc),
                ~ifelse(is.infinite(.), NA, .)))

pm_fu4 <- pm_fu4 |>
  left_join(temp_loc_harras_df, by = "hh_id")
rm(temp_loc_harras_df)


# Absence of harassment and violence (0-8) ----

addIndex("pm_fu4",
         c("pm_felt_unsafe",
           "pm_phys_attacked", 
           "pm_theft", "pm_disc"),
         "fu4_pm_harrasment")  
  

# Physical health (1-4) ----
## pm_illness component is at the location level. Taking max
temp_ill_df <- pm_fu4 |>
  select(hh_id, matches("pm_illness_[0-9]+|pm_location_period_lab_[0-9]+")) |>
  pivot_longer(
    cols = matches("pm_illness_[0-9]+|pm_location_period_lab_[0-9]+"),
    names_to = c(".value", "loc_ind"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(pm_location_period_lab == "from our most recent survey in person to now") |>
  filter(!is.na(pm_illness)) |>
  group_by(hh_id) |>
  summarize(pm_illness = max(pm_illness, na.rm = T))

pm_fu4 <- pm_fu4 |>
  left_join(temp_ill_df, by = "hh_id") |>
  # Scaling all components to (0-1)
  mutate(pm_sleep = pm_sleep/24,
         pm_physical_health = (pm_physical_health - 1)/4)

rm(temp_ill_df)

addIndex("pm_fu4",
         c("pm_illness_limit",
           "pm_sleep", 
           "pm_illness",
           "pm_physical_health"),
         "fu4_pm_physical_health")

```

```{r}
#| label: Summ-HealthSafety-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_physical_health,
                   fu4_pm_harrasment,
                   c("pm_illness_limit",
                     "pm_sleep", 
                     "pm_illness",
                     "pm_physical_health1" = "pm_physical_health",
                     "pm_felt_unsafe",
                     "pm_phys_attacked", 
                     "pm_theft", 
                     "pm_disc")), 
            by = "hh_id") |>
  rename_at(vars(c("pm_illness_limit",
                   "pm_sleep", 
                   "pm_illness",
                   "pm_physical_health1",
                   "pm_felt_unsafe",
                   "pm_phys_attacked", 
                   "pm_theft", 
                   "pm_disc")), 
            ~paste0("fu4_", .))

# Summarize outcomes generated ----
summ(c("fu4_pm_harrasment",
       "fu4_pm_physical_health"))
```

#### Mental Health

```{r}
#| label: Gen-MentHeatlh-Outcomes-PM

# Cleaning outcome components ----
pm_fu4 <- pm_fu4 |>
  mutate(rev_pm_self_esteem_4 = (5 - pm_self_esteem_4)/4,
         rev_pm_self_esteem_9 = (5 - pm_self_esteem_9)/4,
         pm_emotion1 = (pm_emotion1)/3,
         pm_emotion2 = (pm_emotion2)/3,
         rev_pm_emotion3 = (3 - pm_emotion3)/3,
         rev_pm_emotion4 = (3 - pm_emotion4)/3,
         rev_pm_emotion5 = (3 - pm_emotion5)/3,
         rev_pm_emotion6 = (3 - pm_emotion6)/3,
         rev_pm_emotion7 = (3 - pm_emotion7)/3,
         rev_pm_home_problems = (4 - pm_home_problems)/3,
         rev_pm_idleness = (4 - pm_idleness)/3,
         rev_pm_alcohol_consumption = (4 - pm_alcohol_consumption)/3,
         rev_pm_family_death = (4 - pm_family_death)/3,
         rev_pm_money_problems = (4 - pm_money_problems)/3,
         rev_pm_debt_owed = (4 - pm_debt_owed)/3,
         rev_pm_cant_find_work = (4 - pm_cant_find_work)/3,
         rev_pm_cant_educate_children = (4 - pm_cant_educate_children)/3,
         rev_pm_accidents_disasters = (4 - pm_accidents_disasters)/3,
         pm_ladder_scale = pm_ladder_scale/10
         ) 

# Emotion (0-9) ----
addIndex("pm_fu4",
         c("rev_pm_self_esteem_4",
           "rev_pm_self_esteem_9",
           "pm_emotion1",
           "pm_emotion2",
           "rev_pm_emotion3",
           "rev_pm_emotion4",
           "rev_pm_emotion5",
           "rev_pm_emotion6",
           "rev_pm_emotion7"),
         "fu4_pm_emotion")

# Stress: Family (0-4) ----
addIndex("pm_fu4",
         c("rev_pm_home_problems",
           "rev_pm_idleness",
           "rev_pm_alcohol_consumption",
           "rev_pm_family_death"),
         "fu4_pm_famstress")

# Stress: Economic (0-6) ----
addIndex("pm_fu4",
         c("rev_pm_money_problems",
           "rev_pm_debt_owed",
           "rev_pm_cant_find_work",
           "rev_pm_cant_educate_children",
           "rev_pm_accidents_disasters",
           "pm_ladder_scale"),
         "fu4_pm_econstress")
```


```{r}
#| label: Summ-MentHealth-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_econstress,
                   fu4_pm_famstress,
                   fu4_pm_emotion,
                   c("rev_pm_self_esteem_4",
                     "rev_pm_self_esteem_9",
                     "pm_emotion1",
                     "pm_emotion2",
                     "rev_pm_emotion3",
                     "rev_pm_emotion4",
                     "rev_pm_emotion5",
                     "rev_pm_emotion6",
                     "rev_pm_emotion7",
                     "rev_pm_home_problems",
                     "rev_pm_idleness",
                     "rev_pm_alcohol_consumption",
                     "rev_pm_family_death",
                     "rev_pm_money_problems",
                     "rev_pm_debt_owed",
                     "rev_pm_cant_find_work",
                     "rev_pm_cant_educate_children",
                     "rev_pm_accidents_disasters",
                     "pm_ladder_scale")),
            by = "hh_id") |>
  rename_at(vars("rev_pm_self_esteem_4",
                 "rev_pm_self_esteem_9",
                 "pm_emotion1",
                 "pm_emotion2",
                 "rev_pm_emotion3",
                 "rev_pm_emotion4",
                 "rev_pm_emotion5",
                 "rev_pm_emotion6",
                 "rev_pm_emotion7",
                 "rev_pm_home_problems",
                 "rev_pm_idleness",
                 "rev_pm_alcohol_consumption",
                 "rev_pm_family_death",
                 "rev_pm_money_problems",
                 "rev_pm_debt_owed",
                 "rev_pm_cant_find_work",
                 "rev_pm_cant_educate_children",
                 "rev_pm_accidents_disasters",
                 "pm_ladder_scale"), 
            ~paste0("fu4_pm_", gsub("pm_", "", .)))

# Summarize outcomes generated ----
summ(c("fu4_pm_emotion",
       "fu4_pm_famstress",
       "fu4_pm_econstress"))

```


### SHM

#### Mental Health
```{r}
#| label: Gen-MentHeatlh-Outcomes-SHM

# Cleaning outcome components ----
shm_fu4 <- shm_fu4 |>
  mutate(rev_shm_self_esteem_4 = (5 - shm_self_esteem_4)/4,
         rev_shm_self_esteem_9 = (5 - shm_self_esteem_9)/4,
         shm_emotion1 = (shm_emotion1)/3,
         shm_emotion2 = (shm_emotion2)/3,
         rev_shm_emotion3 = (3 - shm_emotion3)/3,
         rev_shm_emotion4 = (3 - shm_emotion4)/3,
         rev_shm_emotion5 = (3 - shm_emotion5)/3,
         rev_shm_emotion6 = (3 - shm_emotion6)/3,
         rev_shm_emotion7 = (3 - shm_emotion7)/3,
         rev_shm_home_problems = (4 - shm_home_problems)/3,
         rev_shm_idleness = (4 - shm_idleness)/3,
         rev_shm_alcohol_consumption = (4 - shm_alcohol_consumption)/3,
         rev_shm_family_death = (4 - shm_family_death)/3,
         rev_shm_money_problems = (4 - shm_money_problems)/3,
         rev_shm_debt_owed = (4 - shm_debt_owed)/3,
         rev_shm_cant_find_work = (4 - shm_cant_find_work)/3,
         rev_shm_cant_educate_children = (4 - shm_cant_educate_children)/3,
         rev_shm_accidents_disasters = (4 - shm_accidents_disasters)/3,
         shm_ladder_scale = shm_ladder_scale/10) 

# Emotion (0-9) ----
addIndex("shm_fu4",
         c("rev_shm_self_esteem_4",
           "rev_shm_self_esteem_9",
           "shm_emotion1",
           "shm_emotion2",
           "rev_shm_emotion3",
           "rev_shm_emotion4",
           "rev_shm_emotion5",
           "rev_shm_emotion6",
           "rev_shm_emotion7"),
         "fu4_shm_emotion")

# Stress: Family (0-4) ----
addIndex("shm_fu4",
         c("rev_shm_home_problems",
           "rev_shm_idleness",
           "rev_shm_alcohol_consumption",
           "rev_shm_family_death"),
         "fu4_shm_famstress")

# Stress: Economic (0-6) ----
addIndex("shm_fu4",
         c("rev_shm_money_problems",
           "rev_shm_debt_owed",
           "rev_shm_cant_find_work",
           "rev_shm_cant_educate_children",
           "rev_shm_accidents_disasters",
           "shm_ladder_scale"),
         "fu4_shm_econstress")
```

```{r}
#| label: Summ-MentHeatlh-Outcomes-SHM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(shm_fu4, hh_id,
                   fu4_shm_econstress,
                   fu4_shm_famstress,
                   fu4_shm_emotion,
                   c("rev_shm_self_esteem_4",
                     "rev_shm_self_esteem_9",
                     "shm_emotion1",
                     "shm_emotion2",
                     "rev_shm_emotion3",
                     "rev_shm_emotion4",
                     "rev_shm_emotion5",
                     "rev_shm_emotion6",
                     "rev_shm_emotion7",
                     "rev_shm_home_problems",
                     "rev_shm_idleness",
                     "rev_shm_alcohol_consumption",
                     "rev_shm_family_death",
                     "rev_shm_money_problems",
                     "rev_shm_debt_owed",
                     "rev_shm_cant_find_work",
                     "rev_shm_cant_educate_children",
                     "rev_shm_accidents_disasters",
                     "shm_ladder_scale")), 
            by = "hh_id") |>
  rename_at(vars(c("rev_shm_self_esteem_4",
                     "rev_shm_self_esteem_9",
                     "shm_emotion1",
                     "shm_emotion2",
                     "rev_shm_emotion3",
                     "rev_shm_emotion4",
                     "rev_shm_emotion5",
                     "rev_shm_emotion6",
                     "rev_shm_emotion7",
                     "rev_shm_home_problems",
                     "rev_shm_idleness",
                     "rev_shm_alcohol_consumption",
                     "rev_shm_family_death",
                     "rev_shm_money_problems",
                     "rev_shm_debt_owed",
                     "rev_shm_cant_find_work",
                     "rev_shm_cant_educate_children",
                     "rev_shm_accidents_disasters",
                     "shm_ladder_scale")),
            ~paste0("fu4_shm_", gsub("shm_", "", .)))

# Summarize outcomes generated ----
summ(c("fu4_shm_emotion",
       "fu4_shm_famstress",
       "fu4_shm_econstress"))

```


### HoH

#### HH Size 

```{r}
#| label: Gen-Size-HH

# HH size ----
hh_size <- hoh_fu4 |>
  select(hh_id, matches("hoh_roster_age_[0-9]+")) |>
  pivot_longer(cols = matches("hoh_roster_age_[0-9]+"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(!is.na(hoh_roster_age)) |>
  mutate(above18 = 1*(hoh_roster_age >= 18),
         below18 = 1*(hoh_roster_age < 18),
         below15 = 1*(hoh_roster_age < 15),
         above15 = 1*(hoh_roster_age >= 15),
         between1815 = 1*(hoh_roster_age >= 18 & 
                            hoh_roster_age <= 40),
         dum = 1) |>
  group_by(hh_id) |>
  summarize(fu4_hh_members = sum(dum, na.rm = T),
            fu4_hh_members_above18 = sum(above18, na.rm = T),
            fu4_hh_members_below18 = sum(below18, na.rm = T),
            fu4_hh_members_above15 = sum(above15, na.rm = T),
            fu4_hh_members_below15 = sum(below15, na.rm = T),
            fu4_hh_members_1840 = sum(between1815, na.rm = T))

```

```{r}
#| label: Summ--Size-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(hh_size, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("fu4_hh_members",
       "fu4_hh_members_above18",
       "fu4_hh_members_below18",
       "fu4_hh_members_above15",
       "fu4_hh_members_below15",
       "fu4_hh_members_1840"))
```

#### Migration outcomes

```{r}
#| label: Gen-Mig-Outcomes-HH

ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)


hoh_fu3 <- read.csv(here("data/out/fu3/Follow-up Round 3 Household Head De-ID.csv")) |>
  filter(resp_available == 1)

## Number of member migrating (ECOWAS, non-ECOWAS, Domestically) ----

### Function to get 
hh_mig <- function(df) {
  ## Getting PM names to remove from calculation ----
  pm_names <- df |>
    select(pm_name, hh_id) |>
    mutate(pm_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", pm_name)),
           dum_pm = 1) 
  
  ## MErging PM names to roster names, generating dummy for PM ----
  roster_names <- df |>
    select(hh_id, matches("hoh_roster_name_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_name_[0-9]+"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_roster_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", hoh_roster_name))) |>
    left_join(pm_names, by = c("hh_id", "hoh_roster_name" = "pm_name")) |>
    mutate(dum_pm = ifelse(is.na(dum_pm), 0, 1))
  
  
  # Member demographic info ----
  members_df <- df |>
    select(hh_id, matches("hoh_roster_age_[0-9]|hoh_roster_sex_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_age_[0-9]|hoh_roster_sex_[0-9]"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    filter(!is.na(hoh_roster_age))
  
  df |>
    select(hh_id, matches("hoh_dest_country_[0-9]")) |>
    mutate_at(vars(matches("hoh_dest_country_")), as.numeric) |>
    pivot_longer(cols = matches("hoh_dest_country_[0-9]+"),
      names_to = c(".value", "loc_ind", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)_([0-9]+)") |>
    left_join(roster_names, by = c("hh_id", "mem_ind")) |>
    left_join(members_df, by = c("hh_id", "mem_ind")) |>
    mutate_at(vars(mem_ind, loc_ind), as.numeric) |>
    filter(!is.na(hoh_dest_country) & hoh_dest_country != 0 & dum_pm == 0) |>
    mutate(dum_ec = 1*(loc_ind %in% ecowas_codes),
           dum_noec = 1*(loc_ind %in% noecowas_codes),
           dum_niger = 1*(loc_ind == 1),
           dum_ec_work = 1*(loc_ind %in% ecowas_codes & 
                            hoh_roster_age %in% 18:40 &
                            hoh_roster_sex == "Male"),
           dum_noec_work = 1*(loc_ind %in% noecowas_codes & 
                              hoh_roster_age %in% 18:40 &
                              hoh_roster_sex == "Male"),
           dum_niger_work = 1*(loc_ind == 1 & 
                               hoh_roster_age %in% 18:40 &
                               hoh_roster_sex == "Male"))  |>
  ungroup() |>
  rowwise() |>
  mutate(dum_any = pmax(dum_ec, dum_noec, dum_niger),
         dum_any_work = pmax(dum_ec_work, dum_noec_work, dum_niger_work)) |>
  ungroup()
}

mig_df_fu3 <- hh_mig(hoh_fu3) |>
  mutate(survey_wave = "fu3")

mig_df <- hh_mig(hoh_fu4) |>
  mutate(survey_wave = "fu4") |>
  bind_rows(mig_df_fu3) |>
  group_by(hh_id, hoh_roster_name) |>
  summarize(dum_ec = max(dum_ec, na.rm = T),
            dum_noec = max(dum_noec, na.rm = T),
            dum_niger = max(dum_niger, na.rm = T),
            dum_any = max(dum_any, na.rm = T),
            dum_ec_work = max(dum_ec_work, na.rm = T),
            dum_noec_work = max(dum_noec_work, na.rm = T),
            dum_niger_work = max(dum_niger_work, na.rm = T),
            dum_any_work = max(dum_any_work, na.rm = T)) |>
  ungroup() |>
  arrange(hh_id, hoh_roster_name) |>
  group_by(hh_id) |>
  summarize(fu4_hh_border_cross_ecowas = max(dum_ec),
            fu4_hh_border_cross_nonec = max(dum_noec),
            fu4_hh_dom_mig = max(dum_niger),
            fu4_hh_mig_any = max(dum_any),
            fu4_hh_border_cross_ecowas_work = max(dum_ec_work),
            fu4_hh_border_cross_nonec_work = max(dum_noec_work),
            fu4_hh_dom_mig_work = max(dum_niger_work),
            fu4_hh_mig_any_work = max(dum_any_work),
            fu4_hh_border_cross_ecowas_num = sum(dum_ec),
            fu4_hh_border_cross_nonec_num = sum(dum_noec),
            fu4_hh_dom_mig_num = sum(dum_niger),
            fu4_hh_mig_any_num = sum(dum_any),
            fu4_hh_border_cross_ecowas_work_num = sum(dum_ec_work),
            fu4_hh_border_cross_nonec_work_num = sum(dum_noec_work),
            fu4_hh_dom_mig_work_num = sum(dum_niger_work),
            fu4_hh_mig_any_work_num = sum(dum_any_work)) |>
  ungroup() |>
  full_join(select(hoh_fu4, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu3, hh_id), by = "hh_id") |>
  mutate_at(vars(matches("fu4_hh_")),
            ~ifelse(is.na(.), 0, .))

```

```{r}
#| label: Summ-Mig-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(mig_df, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("fu4_hh_mig_any",
       "fu4_hh_dom_mig",
       "fu4_hh_border_cross_ecowas", 
       "fu4_hh_border_cross_nonec",
       "fu4_hh_mig_any_work",
       "fu4_hh_dom_mig_work",
       "fu4_hh_border_cross_ecowas_work", 
       "fu4_hh_border_cross_nonec_work",
       "fu4_hh_mig_any_num",
       "fu4_hh_dom_mig_num",
       "fu4_hh_border_cross_ecowas_num", 
       "fu4_hh_border_cross_nonec_num",
       "fu4_hh_mig_any_work_num",
       "fu4_hh_dom_mig_work_num",
       "fu4_hh_border_cross_ecowas_work_num", 
       "fu4_hh_border_cross_nonec_work_num"))
```



#### Failed Migration

```{r}
#| label: Gen-Failed-Mig-Outcomes-HH

ecowas_codes <- c(3, 6, 7, 9, 10, 13, 14, 15, 16, 17, 18, 19)
noecowas_codes <- c(setdiff(c(2:21), ecowas_codes), -777)

## Number of member failed migration (ECOWAS, non-ECOWAS, Domestically) ----

### Function to get 
hh_failed_mig <- function(df) {
  ## Getting PM names to remove from calculation ----
  pm_names <- df |>
    select(pm_name, hh_id) |>
    mutate(pm_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", pm_name)),
           dum_pm = 1) 
  
  ## MErging PM names to roster names, generating dummy for PM ----
  roster_names <- df |>
    select(hh_id, matches("hoh_roster_name_[0-9]")) |>
    pivot_longer(cols = matches("hoh_roster_name_[0-9]+"),
      names_to = c(".value", "mem_ind"),
      names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_roster_name = tolower(gsub("[^A-Za-zÀ-ÿ-]", "", hoh_roster_name))) |>
    left_join(pm_names, by = c("hh_id", "hoh_roster_name" = "pm_name")) |>
    mutate(dum_pm = ifelse(is.na(dum_pm), 0, 1))
  
  df |>
    select(hh_id, matches("hoh_failed_country_index_[0-9]+_[0-9]+")) |>
    pivot_longer(cols = matches("hoh_failed_country_index_[0-9]+"),
      names_to = c(".value", "mem_ind", "loc"),
      names_pattern = "(.+)_([0-9]+)_([0-9]+)") |>
    left_join(roster_names, by = c("hh_id", "mem_ind")) |>
    filter(dum_pm == 0 & hoh_failed_country_index != "") |>
    mutate(dum_failed_ec = 1*(hoh_failed_country_index %in% ecowas_codes),
           dum_failed_noec = 1*(hoh_failed_country_index %in% noecowas_codes),
           dum_failed_niger = 1*(hoh_failed_country_index == 1))  |>
  ungroup() |>
  rowwise() |>
  mutate(dum_failed_any = pmax(dum_failed_ec, dum_failed_noec, dum_failed_niger)) |>
  ungroup()
}

mig_df_fu3 <- hh_failed_mig(hoh_fu3) |>
  mutate(survey_wave = "fu3")

mig_df <- hh_failed_mig(hoh_fu4) |>
  mutate(survey_wave = "fu4") |>
  bind_rows(mig_df_fu3) |>
  group_by(hh_id, hoh_roster_name) |>
  summarize(dum_failed_ec = max(dum_failed_ec, na.rm = T),
            dum_failed_noec = max(dum_failed_noec, na.rm = T),
            dum_failed_niger = max(dum_failed_niger, na.rm = T),
            dum_failed_any = max(dum_failed_any, na.rm = T)) |>
  ungroup() |>
  arrange(hh_id, hoh_roster_name) |>
  group_by(hh_id) |>
  summarize(fu4_hh_failed_border_cross_ecowas = max(dum_failed_ec),
            fu4_hh_failed_border_cross_nonec = max(dum_failed_noec),
            fu4_hh_failed_dom_mig = max(dum_failed_niger),
            fu4_hh_failed_mig_any = max(dum_failed_any)) |>
  ungroup() |>
  full_join(select(hoh_fu4, hh_id), by = "hh_id") |>
  full_join(select(hoh_fu3, hh_id), by = "hh_id") |>
  mutate_at(vars(matches("fu4_hh_")),
            ~ifelse(is.na(.), 0, .)) |>
  arrange(hh_id) 

```

```{r}
#| label: Summ-Failed-Mig-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(mig_df, 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("fu4_hh_failed_mig_any",
       "fu4_hh_failed_dom_mig",
       "fu4_hh_failed_border_cross_ecowas", 
       "fu4_hh_failed_border_cross_nonec"))

```


#### Economic Well-Being

```{r}
#| label: Gen-Econ-Outcomes-HH

# Cleaning outcome components ----
hoh_fu4 <- hoh_fu4 |>
  mutate(hoh_remit_send_niger_amt = -hoh_remit_send_niger_amt,
         hoh_goods_send_niger_amt = -hoh_goods_send_niger_amt,
         hoh_livestock_expend = -hoh_livestock_expend,
         hoh_hire_livestock_total = -(hoh_hire_livestock_days*hoh_hire_livestock_wage),
         hoh_borrow_total = -hoh_borrow_total,
         hoh_adult_protein = case_when(hoh_adult_protein < 7 ~ 
                                         hoh_adult_protein,
                                   .default = 7),
         hoh_child_protein = case_when(hoh_child_protein < 7 ~ 
                                         hoh_child_protein,
                                   .default = 7),
         livestock_paid = hoh_paid_livestock_wage * 12 *
           hoh_paid_livestock_days,
         hoh_rent_land_amt = - hoh_rent_land_amt) |>
  mutate_at(vars(hoh_purchase_clothing, 
                 hoh_purchase_sheep, 
                 hoh_purchase_goat, 
                 hoh_purchase_poultry,
                 c(getVarnames(hoh_fu4, "emerg_sell_[1-9]"),
                   getVarnames(hoh_fu4, "emerg_borrow_[1-9]"),
                   getVarnames(hoh_fu4, "emerg_consume_[1-9]"),
                   getVarnames(hoh_fu4, "emerg_spend_[1-9]"))),
            ~case_when(. < 0 ~ NA,
                       .default = .)) |>
  mutate_at(vars(hoh_adults_skip_meal_num, 
                 hoh_adults_skip_days_num,
                 hoh_adult_protein,
                 hoh_child_skip_days_num,
                 hoh_child_skip_meals_num,
                 hoh_child_protein), ~./7) |>
  mutate(Y_1 = hoh_member_other_weeks_1 * hoh_member_other_amt_1,
         Y_2 = hoh_member_other_weeks_2 * hoh_member_other_amt_2,
         Y_3 = hoh_member_other_weeks_3 * hoh_member_other_amt_3,
         Y_4 = hoh_member_other_weeks_4 * hoh_member_other_amt_4,
         Y_5 = hoh_member_other_weeks_5 * hoh_member_other_amt_5,
         Y_6 = hoh_member_other_weeks_6 * hoh_member_other_amt_6,
         Y_7 = hoh_member_other_weeks_7 * hoh_member_other_amt_7,
         Y_8 = hoh_member_other_weeks_8 * hoh_member_other_amt_8,
         Y_9 = hoh_member_other_weeks_9 * hoh_member_other_amt_9,
         Y_10 = hoh_member_other_weeks_10 * hoh_member_other_amt_10,
         Y_11 = hoh_member_other_weeks_11 * hoh_member_other_amt_11,
         Y_12 = hoh_member_other_weeks_12 * hoh_member_other_amt_12,
         Y_13 = hoh_member_other_weeks_13 * hoh_member_other_amt_13,
         Y_14 = hoh_member_other_weeks_14 * hoh_member_other_amt_14,
         Y_15 = hoh_member_other_weeks_15 * hoh_member_other_amt_15,
         Y_16 = hoh_member_other_weeks_16 * hoh_member_other_amt_16,
         Y_17 = hoh_member_other_weeks_17 * hoh_member_other_amt_17,
         Y_18 = hoh_member_other_weeks_18 * hoh_member_other_amt_18,
         Y_19 = hoh_member_other_weeks_19 * hoh_member_other_amt_19,
         Y_20 = hoh_member_other_weeks_20 * hoh_member_other_amt_20,
         Y_21 = hoh_member_other_weeks_21 * hoh_member_other_amt_21,
         Y_22 = hoh_member_other_weeks_22 * hoh_member_other_amt_22,
         Y_23 = hoh_member_other_weeks_23 * hoh_member_other_amt_23,
         Y_24 = hoh_member_other_weeks_24 * hoh_member_other_amt_24) |>
  mutate(across(starts_with("hoh_crop_quantity_"), 
              ~ . * get(sub("crop_quantity", "price_sold", cur_column())), 
              .names = "A_{.col %>% str_extract('[0-9]+')}")) 


livestocks_price <- hoh_fu4 |>
  left_join(select(workfile, hh_id, com_id), by = "hh_id") |>
  select(hh_id, com_id, matches("hoh_livestock_name_"), 
         matches("hoh_livestock_own_"), 
         matches("hoh_livestock_value_")) |>
  pivot_longer(
    cols = matches("hoh_livestock_name_[0-9]+|hoh_livestock_own_|hoh_livestock_value_"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)")  |>
  filter(hoh_livestock_name != "") |>
  mutate(livestock_id =   case_when(
    hoh_livestock_name %in% c("Poultry", "Volaille", "Kaji") ~ 1,
    hoh_livestock_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
    hoh_livestock_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
    hoh_livestock_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
    hoh_livestock_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
    hoh_livestock_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
    hoh_livestock_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
    hoh_livestock_name %in% c("None", "Aucun", "Babu") ~ 0,
    TRUE ~ NA_real_  # In case of any unexpected value
  )) |>
  mutate(price = hoh_livestock_value/hoh_livestock_own) |>
  group_by(livestock_id) |>
  summarize(mean(hoh_livestock_value), median(hoh_livestock_value),
            mean(price), med_price = median(price)) |>
  arrange(livestock_id)

livestocks <- hoh_fu4 |>
  left_join(select(workfile, hh_id, com_id), by = "hh_id") |>
  select(hh_id, com_id, hhmembers,
         matches("hoh_livestock_act_name"), 
         matches("hoh_livestock_sold"), 
         matches("hoh_livestock_consumed")) |>
  pivot_longer(
    cols = matches("hoh_livestock_act_name_[0-9]+|hoh_livestock_sold_|hoh_livestock_consumed_"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)")  |>
  filter(hoh_livestock_act_name != "") |>
  mutate(livestock_id =   case_when(
    hoh_livestock_act_name %in% c("Poultry", "Volaille", "Kaji") ~ 1,
    hoh_livestock_act_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
    hoh_livestock_act_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
    hoh_livestock_act_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
    hoh_livestock_act_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
    hoh_livestock_act_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
    hoh_livestock_act_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
    hoh_livestock_act_name %in% c("None", "Aucun", "Babu") ~ 0,
    TRUE ~ NA_real_  # In case of any unexpected value
  ))

temp_livestock_df <- livestocks |>
  left_join(livestocks_price, 
            by = c("livestock_id")) |>
  mutate(X_sub = (hoh_livestock_sold)* med_price) |>
  group_by(hh_id) |>
  summarize(X = sum(X_sub))

## price sold is  conditional on selling crop, which is not always the case. Need the xwalk to calculate this.
#sum(crop_quantity * crops * price_sold) - sum(qty_sold * crops * price_sold) - sum(qty_consume * crops * price_sold) + sum(paid_ag * hire_ag_wage)
#getVarnames(hoh_fu4, "crop_quantity")

# hoh_fu4 |> 
#   left_join(select(bl_workfile, hh_id, com_id, loc_id), by = "hh_id") |>
#   select(hh_id, com_id, loc_id, matches("hoh_crop_name_"), 
#          matches("hoh_crop_unit_[0-9]+"), 
#          matches("hoh_price_sold")) |>
#   pivot_longer(cols = starts_with("hoh_"),  
#                names_to = c(".value", "index"), 
#                names_pattern = "hoh_(.*)_(\\d+)") %>% 
#   arrange(hh_id, index) |>
#   group_by(crop_name, crop_unit, loc_id) |>
#   summarize(loc_price = mean(price_sold, na.rm = T), n = n()) |>
#   filter(!is.na(loc_price)) 


temp_monthconscat_df <- hoh_fu4 |>
  select(hh_id, 
         matches("hoh_monthly_consumption_amt_[0-9]"),
         matches("hoh_item_[0-9]")) |>
  pivot_longer(
    cols = matches("hoh_monthly_consumption_amt_[0-9]|hoh_item_[0-9]"),
    names_to = c(".value", "item_number"),
    names_pattern = "(.+)_([0-9]+)") |>
    mutate(hoh_item = case_when(hoh_item %in% 
                            c("Education (children, excluding school fees)", 
                              "Education (enfants, hors frais de scolarité)",	
                              "Tarbiya (yara, ban da kuɗin makaranta)") ~ "fu4_hh_monthcons_edu_child",
                          hoh_item %in% 
                            c("Education (adults, including vocational training)",
                              "Éducation (adultes, y compris la formation professionnelle)",	
                              "Ilimi (manya, gami da koyar da sana'a") ~ "fu4_hh_monthcons_edu_adult",
                          hoh_item %in% 
                            c("Healthcare",	"Soins de santé", "Kiwon lafiya") ~ "fu4_hh_monthcons_health",
                          hoh_item %in% c("Ceremonies", "Cérémonies", "bukukuwa") ~ "fu4_hh_monthcons_ceremony",
                          hoh_item %in% c("Clothes + shoes", "Vêtements + chaussures", 
                                           "Tufafi + takalma") ~ "fu4_hh_monthcons_clothes",
                          .default = NA)) |>
  filter(hoh_item != "") |>
  select(-item_number) |>
  pivot_wider(names_from = "hoh_item", values_from = "hoh_monthly_consumption_amt") |>
  mutate_at(vars(matches("fu4_hh_monthcons")), ~case_when(is.na(.) ~ 0, .default = .))


temp_weekconscat_df <- hoh_fu4 |>
  select(hh_id, 
         matches("hoh_weekly_consumption_amt_[0-9]"),
         matches("hoh_item_week_[0-9]")) |>
  pivot_longer(
    cols = matches("hoh_weekly_consumption_amt_[0-9]|hoh_item_week_[0-9]"),
    names_to = c(".value", "item_number"),
    names_pattern = "(.+)_([0-9]+)") |>
  mutate(hoh_item_week = case_when(hoh_item_week %in% 
                            c("Food (for household members)",	
                              "Nourriture (pour les membres du ménage)",
                              "Abinci (ga mutanen gida)") ~ "fu4_hh_weekcons_food",
                          hoh_item_week %in% 
                            c("Mobile phone credit + charging", 
                              "Crédit mobile + recharge", 
                              "Kuɗin Kiran waya a waya/kiredi da caji") ~ "fu4_hh_weekcons_phone",
                          hoh_item_week %in% 
                            c("Fuel for home/ cooking (i.e. lighting, electricity, firewood)",
                              "Combustible pour la maison/la cuisine (c.-à-d. éclairage, électricité, bois de chauffe)",	
                              "Wutar dafa abinci da ta haske, wutar lantarki, itacen jin wuta)") ~ "fu4_hh_weekcons_homefuel",
                          hoh_item_week %in% c("Fuel for vehicles",
                                      "Carburant pour véhicules",
                                      "Mai ga ababen hawa") ~ "fu4_hh_weekcons_vehiclefuel",
                          hoh_item_week %in% c("Transportation fare (taxi, moto taxi)",
                                      "Frais de transport (taxi, moto taxi)",
                                      "Kudin sufuri kamar kabu kabu da kuɗin mota") ~ "fu4_hh_weekcons_transport",
                          hoh_item_week %in% c("Water (to drink)",
                                      "Eau (à boire)",
                                      "Ruwan sha") ~ "fu4_hh_weekcons_water",
                          .default = NA)) |>
  filter(hoh_item_week != "") |>
  select(-item_number) |>
  pivot_wider(names_from = "hoh_item_week", values_from = "hoh_weekly_consumption_amt") |>
  mutate_at(vars(matches("fu4_hh_weekcons")), ~case_when(is.na(.) ~ 0, .default = .))

# Livestock income (CFA) ----


temp_livestock_value_df <- hoh_fu4 |>
  select(hh_id, matches("hoh_livestock_value_")) |>
  pivot_longer(cols = matches("hoh_livestock_value_[0-9]"),
               names_to = c(".value", "livestock"),
               names_pattern = "(.+)_([0-9]+)") |>
  group_by(hh_id) |>
  summarize(C = sum(hoh_livestock_value, na.rm = T)) 

hoh_fu4 <- left_join(hoh_fu4, temp_livestock_df, by = "hh_id") |>
  left_join(temp_livestock_value_df, by = "hh_id") |>
  mutate(X = X) |>
  mutate_at(vars(c("livestock_paid",
           "X", "hoh_livestock_expend",
           "hoh_hire_livestock_total", "C")), ~ifelse(is.na(.), 0, .))


addIndex("hoh_fu4",
         c("livestock_paid", "C",
           "X", "hoh_livestock_expend",
           "hoh_hire_livestock_total"),
         "fu4_hh_livestock_inc")


# Other income (CFA) ----
addIndex("hoh_fu4",
         c(getVarnames(hoh_fu4, "^Y_[0-9]+$"), 
           "hoh_earn_rent",
           "hoh_income_gifts",
           "hoh_earn_interest"),
         "fu4_hh_other_inc")

# Business income (CFA) ----
hoh_fu4 <- hoh_fu4 |>
  mutate(fu4_hh_biz_inc = ifelse(hoh_own_biz == 1, hoh_biz_income, 0))


# Remittances (CFA) ---- 
## pm_names to identify PMs from roster 
pm_names <- hoh_bl |> 
  select(hh_id, pm_name) |>
  mutate(pm_name_str = stringi::stri_trans_general(tolower(gsub(" ", "", sub(" \\(age: [0-9]+\\)", "", pm_name))), "Latin-ASCII"))
  
#Amount contributed to HH common pot by PM
contribute_df <- hoh_fu4 |>
  select(hh_id, matches("hoh_member_contribute_[0-9]+|hoh_member_act_name_[0-9]+")) |>
  pivot_longer(cols = matches("hoh_member_contribute_[0-9]+|hoh_member_act_name_[0-9]+"),
               names_to = c(".value", "member"),
               names_pattern = "(.+)_([0-9]+)") |>
  select(hh_id, hoh_member_act_name, hoh_member_contribute) |>
  mutate(member_act_name_str = stringi::stri_trans_general(tolower(gsub(" ", "", sub(" \\(age: [0-9]+\\)", "", hoh_member_act_name))), "Latin-ASCII")) |>
  left_join(pm_names, by = c("hh_id", "member_act_name_str" = "pm_name_str")) |>
  filter(!is.na(pm_name)) |>
  distinct(hh_id, member_act_name_str, .keep_all = T) |>
  select(hh_id, 
         fu4_hh_pm_contribute = hoh_member_contribute)

addIndex("hoh_fu4",
         c("hoh_remit_rec_niger_amt",
           "hoh_goods_rec_niger_amt",
           "hoh_remit_send_niger_amt",
           "hoh_goods_send_niger_amt"),
         "fu4_hh_remit")

# Savings (CFA) ----
addIndex("hoh_fu4",
         c("hoh_savings_total",
           "hoh_borrow_total"),
         "fu4_hh_savings")



# Monthly expenditures (CFA) ----
addIndex("hoh_fu4",
         c("hoh_monthly_consumption_amt_1",
           "hoh_monthly_consumption_amt_2",
           "hoh_monthly_consumption_amt_3",
           "hoh_monthly_consumption_amt_4"),
         "fu4_hh_monthly_cons")

# Weekly expenditures (CFA) ----
addIndex("hoh_fu4",
         c("hoh_weekly_consumption_amt_1",
           "hoh_weekly_consumption_amt_2",
           "hoh_weekly_consumption_amt_3",
           "hoh_weekly_consumption_amt_4",
           "hoh_weekly_consumption_amt_5",
           "hoh_weekly_consumption_amt_6"),
         "fu4_hh_weekly_cons")

# Ramadan Expenditures (CFA) ----
addIndex("hoh_fu4",
         c("hoh_purchase_clothing", 
           "hoh_purchase_sheep", 
           "hoh_purchase_goat", 
           "hoh_purchase_poultry"),
         "fu4_hh_fest_cons")

# Adult food security (0-3) ----
addIndex("hoh_fu4",
         c("hoh_adults_skip_meal_num", 
           "hoh_adults_skip_days_num",
           "hoh_adult_protein"), 
         "fu4_hh_adult_foodsec")


# Child food security (0-3) ----
addIndex("hoh_fu4",
         c("hoh_child_skip_meals_num", 
           "hoh_child_skip_days_num",
           "hoh_child_protein"), 
         "fu4_hh_child_foodsec")

## Reversing so it is food security
hoh_fu4 <- hoh_fu4 |>
  mutate(fu4_hh_adult_foodsec = 3 - fu4_hh_adult_foodsec,
         fu4_hh_child_foodsec = 3 - fu4_hh_child_foodsec)


# Economic Precarity (events) ----
addIndex("hoh_fu4",
         c(getVarnames(hoh_fu4, "emerg_sell_[1-9]"),
           getVarnames(hoh_fu4, "emerg_borrow_[1-9]"),
           getVarnames(hoh_fu4, "emerg_consume_[1-9]"),
           getVarnames(hoh_fu4, "emerg_spend_[1-9]")),
         "fu4_hh_emerg_event")

# Economic Precarity (cost in CFA) ----
addIndex("hoh_fu4",
         c(getVarnames(hoh_fu4, "emerg_sell_amt_[1-9]"),
           getVarnames(hoh_fu4, "emerg_borrow_amt_[1-9]"),
           getVarnames(hoh_fu4, "emerg_spend_amt_[1-9]")),
         "fu4_hh_emerg_cost")
```


```{r}
#| label: Summ-Econ-Outcomes-HH
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(hoh_fu4, hh_id,
                   fu4_hh_livestock_inc,
                   fu4_hh_livestock_paid = livestock_paid,
                   fu4_hh_livestock_value = X, 
                   fu4_hh_livestock_expend = hoh_livestock_expend,
                   fu4_hh_hire_livestock_total = hoh_hire_livestock_total,
                   fu4_hh_livestock_holdings = C,
                   fu4_hh_other_inc,
                   fu4_hh_biz_inc,
                   fu4_hh_remit,
                   fu4_hh_savings,
                   fu4_hh_savings_total = hoh_savings_total,
                   fu4_hh_borrow_total = hoh_borrow_total,
                   fu4_hh_monthly_cons,
                   fu4_hh_weekly_cons,
                   fu4_hh_fest_cons,
                   fu4_hh_adult_foodsec,
                   fu4_hh_child_foodsec,
                   fu4_hh_emerg_event,
                   fu4_hh_emerg_cost), 
            by = "hh_id") |>
  left_join(temp_monthconscat_df, by = "hh_id") |>
  left_join(temp_weekconscat_df, by = "hh_id") |>
  mutate_at(vars(matches("fu4_hh_weekcons|fu4_hh_monthcons")), 
            ~case_when(fu4_hoh_comp == 1 & is.na(.) ~ 0,
                       .default = .))  |>
  left_join(contribute_df, by = "hh_id")


# Summarize outcomes generated ----
summ(c("fu4_hh_livestock_inc",
       "fu4_hh_other_inc", 
       "fu4_hh_biz_inc", 
       "fu4_hh_remit",
       "fu4_hh_pm_contribute",
       "fu4_hh_savings",
       "fu4_hh_monthly_cons",
       "fu4_hh_weekly_cons",
       "fu4_hh_fest_cons",
       "fu4_hh_adult_foodsec",
       "fu4_hh_child_foodsec",
       "fu4_hh_emerg_event",
       "fu4_hh_emerg_cost"))
```

#### Investments

```{r}
#| label: Gen-Inv-Outcomes-HH

# Cleaning outcome components ----


livestock_prices_df <- hoh_fu4 |>
  select(hh_id, 
         matches("hoh_livestock_name"), 
         matches("hoh_livestock_value"),
         matches("hoh_livestock_own")) |>
  pivot_longer(
    cols = matches("hoh_livestock_name_[0-9]+|hoh_livestock_value_|hoh_livestock_own_"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)")  |>
  filter(hoh_livestock_name != "") |>
  mutate(livestock_id =   case_when(
    hoh_livestock_name %in% c("Poultry", "Volaille", "Kaji") ~ 1,
    hoh_livestock_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
    hoh_livestock_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
    hoh_livestock_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
    hoh_livestock_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
    hoh_livestock_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
    hoh_livestock_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
    hoh_livestock_name %in% c("None", "Aucun", "Babu") ~ 0,
    TRUE ~ NA_real_  # In case of any unexpected value
  )) |>
  mutate(price = hoh_livestock_value/hoh_livestock_own) |>
  group_by(livestock_id) |>
  summarize(med_price = median(price, na.rm = T),
            mean_price = mean(price, na.rm = T))

livestock_bought_df <- hoh_fu4 |>
  select(hh_id, 
         matches("hoh_livestock_act_name"), 
         matches("hoh_livestock_bought")) |>
  pivot_longer(
    cols = matches("hoh_livestock_act_name_[0-9]+|hoh_livestock_bought_"),
    names_to = c(".value", "livestock_num"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(hoh_livestock_act_name != "") |>
  mutate(livestock_id =   case_when(
    hoh_livestock_act_name %in% c("Poultry", "Volaille", "Kaji") ~ 1,
    hoh_livestock_act_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
    hoh_livestock_act_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
    hoh_livestock_act_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
    hoh_livestock_act_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
    hoh_livestock_act_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
    hoh_livestock_act_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
    hoh_livestock_act_name %in% c("None", "Aucun", "Babu") ~ 0,
    TRUE ~ NA_real_  # In case of any unexpected value
  )) |>
  left_join(livestock_prices_df, by = "livestock_id") |>
  mutate(hoh_livestock_bought_amt = med_price * hoh_livestock_bought) |>
  group_by(hh_id) |>
  summarize(hoh_livestock_bought_amt = sum(hoh_livestock_bought_amt, na.rm = T))

# Num school age members and asset counts
temp_school_assets_df <- hoh_fu4 |>
  mutate_at(vars(matches("hoh_roster_age_[0-9]+")), 
            ~case_when(. %in% 4:27 ~ 1,
                       .default = 0)) |>
  select(hh_id, 
         matches("hoh_roster_age_[0-9]+"), 
         matches("hoh_durable_asset_[0-9]+"),
         matches("hoh_school_cost_[0-9]+")) |>
  pivot_longer(
    cols = matches("hoh_roster_age_[0-9]+|hoh_durable_asset_[0-9]+|hoh_school_cost_[0-9]+"),
    names_to = c(".value", "id"),
    names_pattern = "(.+)_([0-9]+)") |>
  group_by(hh_id) |>
  summarize(B = sum(hoh_durable_asset, na.rm = T),
            N_schoolage = sum(hoh_roster_age, na.rm = T))
  
# Select business assets. Merge in all data
temp_df <- hoh_fu4 |>
  left_join(livestock_bought_df, by = "hh_id") |>
  mutate(A = 1*(hoh_durable_asset_10 == 1) + 1*(hoh_durable_asset_11 == 1) + 
           1*(hoh_durable_asset_12 == 1),
         hoh_livestock_bought_amt = ifelse(is.na(hoh_livestock_bought_amt), 
                                           0, hoh_livestock_bought_amt)) |>
  left_join(temp_school_assets_df, by = "hh_id") |>
  mutate_at(vars(B, N_schoolage), ~ifelse(is.na(.), 0, .))
  

# Business investment (livestock purchase, business/land improvement) ----
## Getting BL values for normalization ----
# temp_livestock_price_df <-  hoh_livestock_bl |>
#   mutate(price = livestock_value/livestock_own) |>
#   mutate(livestock_id =   case_when(
#     livestock_name %in% c("Chickens", "Poulets", "Kaji") ~ 1,
#     livestock_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
#     livestock_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
#     livestock_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
#     livestock_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
#     livestock_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
#     livestock_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
#     livestock_name %in% c("None", "Aucun", "Babu") ~ 0,
#     TRUE ~ NA_real_  # In case of any unexpected value
#   )) |>
#   group_by(livestock_id) |>
#   summarize(med_price = median(price, na.rm = T))
# 
# temp_livestock_bought_df <- hoh_livestockact_bl |>
#   mutate(livestock_id =   case_when(
#     livestock_act_name %in% c("Chickens", "Poulets", "Kaji") ~ 1,
#     livestock_act_name %in% c("Goats", "Chèvres", "Awaki") ~ 2,
#     livestock_act_name %in% c("Sheep", "Mouton", "Tumaki") ~ 3,
#     livestock_act_name %in% c("Cattle", "Vaches", "Shanu") ~ 4,
#     livestock_act_name %in% c("Horses", "Les chevaux", "Dawaki") ~ 5,
#     livestock_act_name %in% c("Camels", "Chameaux", "Rakumma") ~ 6,
#     livestock_act_name %in% c("Donkey", "Âne", "Jaki") ~ 7,
#     livestock_act_name %in% c("None", "Aucun", "Babu") ~ 0,
#     TRUE ~ NA_real_  # In case of any unexpected value
#   )) |> 
#   left_join(temp_livestock_price_df, by = "livestock_id") |>
#   mutate(livestock_bought_amt = med_price*livestock_bought) |>
#   group_by(hh_id) |>
#   summarize(D = sum(livestock_bought_amt, na.rm = T)) |>
#   mutate(bl_hoh_livestock_bought_amt = as.numeric(D))
# 
# bl_data_temp <- hoh_bl |>
#   left_join(temp_livestock_bought_df, by = "hh_id") |>
#   mutate(A = 1*(durable_asset_10 == 1) + 1*(durable_asset_11 == 1) + 
#            1*(durable_asset_12 == 1),
#          bl_hoh_livestock_bought_amt = ifelse(is.na(bl_hoh_livestock_bought_amt), 0, bl_hoh_livestock_bought_amt),
#          land_purchased = ifelse(land_access_amt == 0, 0 , land_purchased),
#          improve_business = ifelse(own_biz == 0, 0, improve_business)) |>
#   select(c("bl_hoh_livestock_bought_amt",
#            "improve_business",
#            "improve_land"),
#          bl_hoh_land_purchased = land_purchased,
#          bl_A = A) |>
#   rename_at(vars(all_of(c("improve_business",
#                           "improve_land"))),
#             ~paste0("bl_hoh_",  .)) |>
#   trim("bl_hoh_livestock_bought_amt") |>
#   trim("bl_hoh_land_purchased") |>
#   select(-bl_hoh_land_purchased, 
#          -bl_hoh_livestock_bought_amt)
# 
# bl_means <- bl_data_temp |>
#   summarize_all(~mean(., na.rm = T)) |>
#   rename_all(~paste0(., "_mean"))
# 
# bl_sd <- bl_data_temp |>
#   summarize_all(~sd(., na.rm = T)) |>
#   rename_all(~paste0(., "_sd"))
# 
# bl_stats <- do.call("rbind", replicate(
#   nrow(hoh_fu4), bind_cols(bl_means, bl_sd), simplify = FALSE))
# 
# 
# # Normalized data by BL value
# norm_temp_inv_df <- temp_df |>
#   mutate(hoh_improve_business = ifelse(hoh_own_biz == 0, 0, hoh_improve_business),
#          hoh_land_purchased = ifelse(hoh_land_access_amt == 0, 0, hoh_land_purchased)) |>
#   trim("hoh_livestock_bought_amt") |>
#   trim("hoh_land_purchased") |>
#   select(hh_id, c("hoh_livestock_bought_amt_tr", "A", "hoh_improve_business", 
#                   "hoh_improve_land", "hoh_land_purchased_tr")) |>
#   cbind(bl_stats) |>
#   mutate(across(c("hoh_livestock_bought_amt_tr", "A", "hoh_improve_business", 
#                   "hoh_improve_land", "hoh_land_purchased_tr"),
#                 ~ (. - get(paste0("bl_", cur_column(), "_mean"))) / 
#                   get(paste0("bl_", cur_column(), "_sd")),
#     .names = "{.col}_std")) |>
#   filter(!is.na(hoh_livestock_bought_amt_tr) & 
#            !is.na(hoh_land_purchased_tr)) |>
#   select(hh_id, matches("_std"))
# 
# # Get PC1 loading
# std_vars_inv <- select(norm_temp_inv_df, ends_with("_std"))
# pca_result_inv <- prcomp(std_vars_inv, center = FALSE, scale. = FALSE)
# pc1_loadings_inv <- pca_result_inv$rotation[, 1]


# # Weight each standardized value by the PCA loadings and add for PC1 by observation
# pca_df_inv <- norm_temp_inv_df |>
#   mutate(fu4_hh_biz_inv = as.matrix(std_vars_inv) %*% pc1_loadings_inv) |>
#   select(hh_id, fu4_hh_biz_inv)

temp_inv_df <- temp_df |>
  mutate(hoh_improve_business = ifelse(hoh_own_biz == 0, 0, hoh_improve_business),
         hoh_land_purchased = ifelse(hoh_land_access_amt == 0, 0, hoh_land_purchased)) |>
  trim("hoh_livestock_bought_amt") |>
  trim("hoh_land_purchased")

stat_vars <- temp_inv_df |> 
  left_join(treat_df, by = "hh_id") |>
  filter(S == "mc" & Z == "c") |>
  summarize(mean_hoh_land_purchased_tr = mean(hoh_land_purchased_tr, na.rm = T),
            sd_hoh_land_purchased_tr = sd(hoh_land_purchased_tr, na.rm = T),
            mean_hoh_livestock_bought_amt_tr = mean(hoh_livestock_bought_amt_tr, na.rm = T),
            sd_hoh_livestock_bought_amt_tr = sd(hoh_livestock_bought_amt_tr, na.rm = T),
            mean_A = mean(A, na.rm = T),
            sd_A = sd(A, na.rm = T),
            mean_hoh_improve_land = mean(hoh_improve_land, na.rm = T),
            sd_hoh_improve_land = sd(hoh_improve_land, na.rm = T),
            mean_hoh_improve_business = mean(hoh_improve_business, na.rm = T),
            sd_hoh_improve_business = sd(hoh_improve_business, na.rm = T)) 

stat_vars <- do.call("rbind", replicate(nrow(temp_inv_df), 
                                      stat_vars, simplify = FALSE))

temp_inv_df <- temp_inv_df |>
  cbind(stat_vars)

std_vars_inv <- temp_inv_df |>
  mutate(across(c("hoh_land_purchased_tr", "A", "hoh_improve_business", 
                  "hoh_improve_land", "hoh_livestock_bought_amt_tr"),
                ~ (. - get(paste0("mean_", cur_column()))) / 
                  get(paste0("sd_", cur_column())),
    .names = "{.col}_std")) |>
  select(matches("_std"))


pca_result_inv <- prcomp(std_vars_inv, center = F, scale. = F)
temp_inv_df$fu4_hh_biz_inv <- pca_result_inv$x[, 1]

pca_df_inv <- temp_inv_df |>
  select(hh_id, fu4_hh_biz_inv)


# Education (number of children enrolled) ----
temp_enroll_df <- hoh_fu4 |> 
  select(hh_id, matches("hoh_attending_school")) |>
  pivot_longer(
    cols = matches("hoh_attending_school"),
    names_to = c(".value", "id"),
    names_pattern = "(.+)_([0-9]+)") |>
  filter(!is.na(hoh_attending_school)) |>
  group_by(hh_id) |>
  summarize(fu4_hh_enroll_num = sum(hoh_attending_school))

temp_df <- left_join(temp_df, temp_enroll_df, by = "hh_id") |>
  mutate(fu4_hh_enroll_num = ifelse(is.na(fu4_hh_enroll_num), 0, fu4_hh_enroll_num))

# Assets (durable goods, livestock, home, land) ----

# ## Getting BL values for normalization ----
# temp_livestock_assets <- hoh_livestock_bl |>
#   group_by(hh_id) |>
#   summarize(bl_C = sum(livestock_value, na.rm = T)) |>
#   right_join(select(hoh_bl, hh_id), by = "hh_id") |>
#   mutate(bl_C = ifelse(is.na(bl_C), 0, bl_C))
# 
# temp_durable_assets <- hoh_bl |>
#   select(hh_id, matches("durable_asset_[0-9]")) |>
#   pivot_longer(cols = matches("durable_asset_[0-9]"),
#                names_to = c(".value", "asset"),
#                names_pattern = "(.+)_([0-9]+)") |>
#   group_by(hh_id) |>
#   summarize(bl_B = sum(durable_asset, na.rm = T))
# 
# 
# bl_data_temp <- hoh_bl |> 
#   mutate(home_value = ifelse(own_home == 0, 0, home_value),
#          improve_home_amt = ifelse(improve_add_rooms == 0 &
#                                      improve_floors == 0 & 
#                                      improve_walls == 0& 
#                                      improve_roof == 0 &
#                                      improve_o == 0, 0, 
#                                    improve_home_amt)) |>
#   left_join(temp_livestock_assets, by = "hh_id") |>
#   left_join(temp_durable_assets, by = "hh_id") |>
#   trim("bl_C") |>
#   trim("home_value") |>
#   trim("improve_home_amt") |>
#   trim("own_hectares") |>
#   select(c("bl_B",
#            "bl_C_tr",
#            "improve_add_rooms",
#            "improve_floors",
#            "improve_walls",
#            "improve_roof",
#            "home_value_tr",
#            "improve_home_amt_tr",
#            "own_hectares_tr")) |>
#   rename_at(vars(all_of(c("improve_add_rooms",
#                         "improve_floors",
#                         "improve_walls",
#                         "improve_roof",
#                         "home_value_tr",
#                         "improve_home_amt_tr",
#                         "own_hectares_tr"))),
#             ~paste0("bl_hoh_",  .))
# 
# bl_means <- bl_data_temp |>
#   summarize_all(~mean(., na.rm = T)) |>
#   rename_all(~paste0(., "_mean"))
# 
# bl_sd <- bl_data_temp |>
#   summarize_all(~sd(., na.rm = T)) |>
#   rename_all(~paste0(., "_sd"))
# 
# bl_stats <- do.call("rbind", replicate(
#   nrow(hoh_fu4), bind_cols(bl_means, bl_sd), simplify = FALSE))
# 
# ## Normalizing, Calculating PCA of normalized values ----
# 
# # Normalized data by BL value
# norm_temp_df <- hoh_fu4 |>
#   left_join(select(temp_df, hh_id, B, C), by = "hh_id") |>
#   mutate(hoh_home_value = ifelse(hoh_own_home == 0 | is.na(hoh_own_home), 0, hoh_home_value),
#          hoh_home_value = ifelse(is.na(hoh_home_value), 0, hoh_home_value),
#          hoh_improve_home_amt = ifelse(hoh_improve_add_rooms == 0 &
#                                        hoh_improve_floors == 0 & 
#                                        hoh_improve_walls == 0& 
#                                        hoh_improve_roof == 0 &
#                                        hoh_improve_o == 0, 0, hoh_improve_home_amt)) |>
#   trim("C") |>
#   trim("hoh_home_value") |>
#   trim("hoh_improve_home_amt") |>
#   trim("hoh_own_hectares") |>
#   select(hh_id, c("B",
#            "C_tr",
#            "hoh_improve_add_rooms",
#            "hoh_improve_floors",
#            "hoh_improve_walls",
#            "hoh_improve_roof",
#            "hoh_home_value_tr",
#            "hoh_improve_home_amt_tr",
#            "hoh_own_hectares_tr")) |>
#   cbind(bl_stats) |>
#   mutate(across(c(B,
#                   C_tr,
#                   hoh_improve_add_rooms,
#                   hoh_improve_floors,
#                   hoh_improve_walls,
#                   hoh_improve_roof,
#                   hoh_home_value_tr,
#                   hoh_improve_home_amt_tr,
#                   hoh_own_hectares_tr),
#                 ~ (. - get(paste0("bl_", cur_column(), "_mean"))) / 
#                   get(paste0("bl_", cur_column(), "_sd")),
#     .names = "{.col}_std")) |>
#   filter(!is.na(C_tr) &
#            !is.na(hoh_home_value_tr) & 
#            !is.na(hoh_improve_home_amt_tr) & 
#            !is.na(hoh_own_hectares_tr)) |>
#   select(hh_id, matches("_std")) 
# 
# # Get PC1 loading
# std_vars <- select(norm_temp_df, ends_with("_std"))
# pca_result <- prcomp(std_vars, center = FALSE, scale. = FALSE)
# pc1_loadings <- pca_result$rotation[, 1]
# 
# # Weight each standardized value by the PCA loadings and add for PC1 by observation
# pca_df <- norm_temp_df |>
#   mutate(fu4_hh_assets = as.matrix(std_vars) %*% pc1_loadings) |>
#   select(hh_id, fu4_hh_assets)



norm_temp_df <- hoh_fu4 |>
  left_join(select(temp_df, hh_id, B, C), by = "hh_id") |>
  mutate(hoh_home_value = ifelse(hoh_own_home == 0 | is.na(hoh_own_home), 0, hoh_home_value),
         hoh_home_value = ifelse(is.na(hoh_home_value), 0, hoh_home_value),
         hoh_improve_home_amt = ifelse(hoh_improve_add_rooms == 0 &
                                       hoh_improve_floors == 0 & 
                                       hoh_improve_walls == 0& 
                                       hoh_improve_roof == 0 &
                                       hoh_improve_o == 0, 0, hoh_improve_home_amt)) |>
  trim("hoh_home_value") |>
  trim("hoh_improve_home_amt") |>
  trim("hoh_own_hectares")


stat_vars <- norm_temp_df |> 
  left_join(treat_df, by = "hh_id") |>
  filter(S == "mc" & Z == "c") |>
  summarize(mean_B = mean(B, na.rm = T),
            sd_B = sd(B, na.rm = T),
            mean_hoh_improve_add_rooms = mean(hoh_improve_add_rooms, na.rm = T),
            sd_hoh_improve_add_rooms = sd(hoh_improve_add_rooms, na.rm = T),
            mean_hoh_improve_floors = mean(hoh_improve_floors, na.rm = T),
            sd_hoh_improve_floors = sd(hoh_improve_floors, na.rm = T),
            mean_hoh_improve_walls = mean(hoh_improve_walls, na.rm = T),
            sd_hoh_improve_walls = sd(hoh_improve_walls, na.rm = T),
            mean_hoh_improve_roof = mean(hoh_improve_roof, na.rm = T),
            sd_hoh_improve_roof = sd(hoh_improve_roof, na.rm = T),
            mean_hoh_home_value_tr = mean(hoh_home_value_tr, na.rm = T),
            sd_hoh_home_value_tr = sd(hoh_home_value_tr, na.rm = T),
            mean_hoh_improve_home_amt_tr = mean(hoh_improve_home_amt_tr, na.rm = T),
            sd_hoh_improve_home_amt_tr = sd(hoh_improve_home_amt_tr, na.rm = T),
            mean_hoh_own_hectares_tr = mean(hoh_own_hectares_tr, na.rm = T),
            sd_hoh_own_hectares_tr = sd(hoh_own_hectares_tr, na.rm = T)) 


stat_vars <- do.call("rbind", replicate(nrow(norm_temp_df), 
                                      stat_vars, simplify = FALSE))

norm_temp_df <- norm_temp_df |>
  select(hh_id, c("B", 
                  "hoh_improve_add_rooms",
                  "hoh_improve_floors",
                  "hoh_improve_walls",
                  "hoh_improve_roof",
                  "hoh_home_value_tr",
                  "hoh_improve_home_amt_tr",
                  "hoh_own_hectares_tr")) |>
  cbind(stat_vars)
  
std_vars <- norm_temp_df |>
  mutate(across(c("B", 
                  "hoh_improve_add_rooms",
                  "hoh_improve_floors",
                  "hoh_improve_walls",
                  "hoh_improve_roof",
                  "hoh_home_value_tr",
                  "hoh_improve_home_amt_tr",
                  "hoh_own_hectares_tr"),
                ~ (. - get(paste0("mean_", cur_column()))) / 
                  get(paste0("sd_", cur_column())),
    .names = "{.col}_std")) |>
  select(matches("_std"))


pca_result <- prcomp(std_vars, center = F, scale. = F)
norm_temp_df$fu4_hh_assets <- pca_result$x[, 1]

pca_df <- norm_temp_df |>
  select(hh_id, fu4_hh_assets)

```


```{r}
#| label: Summ-Inv-Outcomes-HH
#| echo: False
workfile <- workfile |>
  left_join(select(temp_df, hh_id, 
                   fu4_hh_enroll_num), 
            by = "hh_id") |>
  left_join(pca_df, by = "hh_id") |>
  left_join(pca_df_inv, by = "hh_id") |>
  mutate_at(c("fu4_hh_assets", 
              "fu4_hh_biz_inv"), ~(scale(.) %>% as.vector))

# Summarize outcomes generated ----
summ(c("fu4_hh_biz_inv",
       "fu4_hh_enroll_num",
       "fu4_hh_assets"))

rm(temp_df)
```


## Secondary Outcomes

### PM

#### Family Structure

```{r}
#| label: Summ-Fam-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_marital_status = pm_married), 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("fu4_pm_marital_status"))
```

#### Investment

```{r}
#| label: Gen-Inv-Outcomes-PM

# Investments in training cost (CFA) ----
addIndex("pm_fu4",
         c("pm_lang_train_cost",
           "pm_voc_train_cost"),
         "fu4_pm_inv_cost")
```

```{r}
#| label: Summ-Inv-Outcomes-PM
#| echo: False
# Merge in outcomes to workfile ----
workfile <- workfile |>
  left_join(select(pm_fu4, hh_id,
                   fu4_pm_inv_cost), 
            by = "hh_id") 

# Summarize outcomes generated ----
summ(c("fu4_pm_inv_cost"))
```





# Saving Final Workfile

```{r}
workfile |>
  write.csv(here("data/out/fu4/workfile-final.csv"),
            na = '',
            row.names = F) 

```
